### 2015-08-30 paper/one/summary.tex
Added summary for first paper
I used LyX to generate the TeX code. Let me know if you're having
problems reading/viewing it.

%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}

\title{Paper One Summary}

\author{Matthew Neal, Joseph Sankar, and Sasha Sobran}

\maketitle

\section*{Reference}

Daryl Posnett, Vladimir Filkov, and Premkumar Devanbu. 2011. Ecological
Inference in Empirical Software Engineering. Proceedings of the 2011
26th IEEE/ACM International Conference on Automated Software Engineering.

\section*{Important Keywords}

\section*{Feature Extraction}

\section*{Possible Improvements}
\end{document}

### 2015-08-31 hw/code/2/think3.py
Fixed an issue with exercise 3.

@@ -21,11 +21,13 @@ repeat_lyrics()
 
 # 3.3
 def right_justify(s):
-    spaces_to_insert = 70 - len(s)
-    for i in range(0, spaces_to_insert):
-        print " ",
-        
-    print(s)
+    # For some reason the solution here before printed
+    # tabs instead of simple spaces printing to out.txt
+    # gives the last character of allen in the 70th column
+    print ' '*(70 - len(s)) + s
+    # for i in range(0, spaces_to_insert):
+    #     print " "
+    # print(s)
 
 right_justify('allen')
 
@@ -33,14 +35,14 @@ right_justify('allen')
 def do_twice(f, val):
     f(val)
     f(val)
-    
+
 def print_spam():
     print 'spam'
-    
+
 def print_twice(s):
     print s
     print s
-    
+
 def do_four(f, val):
     do_twice(f, val)
     do_twice(f, val)
@@ -54,7 +56,7 @@ def print_2x2_grid():
     print "+ - - - - + - - - - +"
     do_twice(print_twice, "|         |         |")
     print "+ - - - - + - - - - +"
-    
+
 def print_4x4_grid():
     print "+ - - - - + - - - - + - - - - + - - - - +"
     do_twice(print_twice, "|         |         |         |         |")
@@ -65,7 +67,7 @@ def print_4x4_grid():
     print "+ - - - - + - - - - + - - - - + - - - - +"
     do_twice(print_twice, "|         |         |         |         |")
     print "+ - - - - + - - - - + - - - - + - - - - +"
-    
+
 print
 print_2x2_grid()
 

### 2015-08-31 paper/one/summary.tex

@@
 \section*{Important Keywords}
+\begin{description}
+\item [{Ecological~inference}] The idea that an observation or finding
+at an aggregated level can apply at a disaggregated level. For example,
+the idea that a model of defects at the package level also applies
+at the file level
+\item [{Ecological~fallacy}] An incorrect application of ecological inference.
+For example, an instance where a model of defects at the product level
+is incorrectly used to model defects at the file level
+\end{description}
 
 \section*{Feature Extraction}
+\begin{description}
+\item [{1~-~Motivational~Statements}] Modern software applications are
+composed of many files. Thus, the files are usually organized into
+units, which may themselves be organized into broader units. While
+research could be focused at the most granular level, for example
+files, methods, even lines of code, research at these levels is costly
+and takes time, so research instead usually examines data at higher
+levels. Therefore, it would be useful to draw conclusions from higher
+levels that would apply to lower levels.
+\end{description}
 

### 2015-09-01 paper/one/summary.tex
added scala and zonation definition

@@
 at an aggregated level can apply at a disaggregated level. For example,
-the idea that a model of defects at the package level also applies
+the idea that a model of defects at the package level also applies.
 at the file level
-\item [{Ecological~fallacy}] An incorrect application of ecological inference.
+\item [{Ecological~fallacy}] An incorrect application of ecological inference. A discrepency between the findings at an aggregated level and disaggragated level.
 For example, an instance where a model of defects at the product level
-is incorrectly used to model defects at the file level
+is incorrectly used to model defects at the file level.
+\item [{Scale}] Size of an aggregated unit. THe larger the scale the bigger and fewer the aggregated units.
+\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering.
 \end{description}

### 2015-09-01 paper/one/summary.tex
extended definitions
added related work to paper summary

@@
 
-\author{Matthew Neal, Joseph Sankar, and Sasha Sobran}
+\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}
 
@@
 is incorrectly used to model defects at the file level.
-\item [{Scale}] Size of an aggregated unit. THe larger the scale the bigger and fewer the aggregated units.
-\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering.
+\item [{Scale}] Size of an aggregated unit. The larger the scale the bigger and fewer the aggregated units. This can effect affect the quality of statistical models built for defect prediction.
+\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering. This can create internal validity threats and lead to ecological fallacies.
 \end{description}
@@
 levels that would apply to lower levels.
+\item [{4~-~Related Work}] To improve model performance, Koru \textit{et al.} recommend aggregating.
+Their methods to acheive improved performance include summing method-level measures into class-level measures and combining these with metrics from class-level features.
+They conclude that this approach overcomes the issues of asymmetry in defect data sets.
+Schr\"{o}ter \textit{et al.} conclude that predicting at coarser granularities is less difficult in comparison to finer granularities but lead to worse results.
+Zimmerman \textit{et al.} find different results where package level correlations and model correlations are higher than file level correlations and model correlations.
+Ambrose \textit{et al.} argue against the use of aggregate level metrics, though without data, stating predictions are more cumbersome to investigate,classes are inherently self-contained, and information derived from the package-level cannot be applied to the class level.
 \end{description}

### 2015-09-02 paper/one/summary.tex
Added in some more feature extraction, keywords, and some places for improvement

@@
 \item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering. This can create internal validity threats and lead to ecological fallacies.
+\item [{Aggregate~Phenomena}] Certain phenomena may apply only at an aggregated level.
+The example given in the paper is that of inheritance.
+Inheritance only takes place at the class level and cannot be studied at a disaggregated level.
+\item [{Cost~Effectiveness}] A concept used within the paper to assess defect models.
+The baseline is that funds  are given to investigate {10\%} of a project for defects, in {10\%} of the lines of code taken at random {10\%} of the defects should be found.
+Models are compared against this baseline.
 \end{description}
@@
 \section*{Feature Extraction}
-\begin{description}
-\item [{1~-~Motivational~Statements}] Modern software applications are
+\begin{itemize}
+\item \textbf{Motivational Statements} Modern software applications are
 composed of many files. Thus, the files are usually organized into
@@
 levels that would apply to lower levels.
-\item [{4~-~Related Work}] To improve model performance, Koru \textit{et al.} recommend aggregating.
+\item \textbf{Related Work} To improve model performance, Koru \textit{et al.} recommend aggregating.
 Their methods to acheive improved performance include summing method-level measures into class-level measures and combining these with metrics from class-level features.
@@
 Ambrose \textit{et al.} argue against the use of aggregate level metrics, though without data, stating predictions are more cumbersome to investigate,classes are inherently self-contained, and information derived from the package-level cannot be applied to the class level.
-\end{description}
+\item \textbf{Motivational Statements}: The authors poses their motivation along with the central question of the paper "What is the right level of study?" (At an aggregated level or dis-aggregated level).
+They believe that this question has a central significance to whether or not a model that is built at a specific level of aggregation can hold at a lower level of aggregation as well as whether performance of the model as regards cost prediction is valid.
+\item \textbf{New Results}:  The authors grouped variables in the models based on loss of significance(LS) or gain of significance(GS).
+They explain that both LS and GS can cause Ecological Inferences issues as in a loss of significance situation when inferring between the aggregate level and the disaggregate level  or GS when inferring from the disaggregate to the aggregate.
+They found 28 instances of GS and 25 instances of LS out of 108 variables over 68 models.
+The authors draw the conclusion that models built at the aggregated level should be undertaken with the knowledge of the underlying risk of Ecological Inference and Ecological Fallacy.
+\item \textbf{Future Work}:The authors bring up three sources of Ecological Inference risk:  Zonation, Sample Size, and Class Imbalance.
+The authors believe that further study of the three sources is in order.
+To give a short background on how each applies:
+\begin{itemize}
+\item Zonation: Aggregation runs the risk of creating distortion by the way that the data is aggregated.  
+\item Sample Size:  As aggregation takes place inherently there is move to smaller and smaller sample sizes.
+As the move to those smaller sample sizes takes place there is a loss in Statistical power.
+\item Class Imbalance: A situation where a set of samples have a particular attribute and a large proportion of that set have a particular value with a very small number having another significant but underrepresented value.
+The example in the paper is a situation where there are a very high number of projects without defects and a very lower number with defects.
+\end{itemize}
+\item \textbf{Sampling Procedures}: Projects were taken from a set of 18 Apache Software Foundation Projects over 87 versions.
+The writers took JIRA issue reports and then mapped them to pull commits.
+Then, they took those commits and connected them to packages and files.
+They also pulled the number of lines of code as well as the number of developers per project.
+They were unable to look at past data sets due to their inability to correctly aggregate the data given that many data sets do not contain issue identifiers.
+
+\end{itemize}
 
 \section*{Possible Improvements}
+\begin{itemize}
+\item There are some particularly distracting typos in the paper.
+For example, on pages 367-368 the authors failed to correctly reference their table correctly leaving "Table ??" in the middle of their text twice.
+\end{itemize}
 \end{document}

### 2015-09-03 hw/code/3/employee.py
Added Employee class for Code3

@@ -1,0 +1,19 @@
+class Employee(object):
+    "Represents an employee in a company"
+    
+    def __init__(self, name, age):
+        self.name = name
+        self.age = age
+    
+    def __repr__(self):
+        return '%s, %s' % (self.name, self.age)
+        
+    def __lt__(self, other):
+        return self.age < other.age
+    
+john = Employee("John", 40)
+bob = Employee("Bob", 30)
+print john
+print bob
+print john < bob
+print bob < john

### 2015-09-03 hw/read/1/summary.tex
Added two possible improvements to paper one

--- 2015-09-02 paper/one/summary.tex
@@
 at the file level 
-\item [{Ecological~fallacy}] An incorrect application of ecological inference. A discrepency between the findings at an aggregated level and disaggragated level.
-For example, an instance where a model of defects at the product level
-is incorrectly used to model defects at the file level.
-\item [{Scale}] Size of an aggregated unit. The larger the scale the bigger and fewer the aggregated units. This can effect affect the quality of statistical models built for defect prediction.
-\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering. This can create internal validity threats and lead to ecological fallacies.
-\item [{Aggregate~Phenomena}] Certain phenomena may apply only at an aggregated level.
-The example given in the paper is that of inheritance.
-Inheritance only takes place at the class level and cannot be studied at a disaggregated level.
-\item [{Cost~Effectiveness}] A concept used within the paper to assess defect models.
-The baseline is that funds  are given to investigate {10\%} of a project for defects, in {10\%} of the lines of code taken at random {10\%} of the defects should be found.
-Models are compared against this baseline.
+\item [{Ecological~fallacy}] An incorrect application of ecological inference.
+A discrepency between the findings at an aggregated level and disaggragated
+level. For example, an instance where a model of defects at the product
+level is incorrectly used to model defects at the file level. 
+\item [{Scale}] Size of an aggregated unit. The larger the scale the bigger
+and fewer the aggregated units. This can effect affect the quality
+of statistical models built for defect prediction. 
+\item [{Zonation}] The manner in which aggregation is performed. For example,
+gerrymandering. This can create internal validity threats and lead
+to ecological fallacies. 
+\item [{Aggregate~Phenomena}] Certain phenomena may apply only at an aggregated
+level. The example given in the paper is that of inheritance. Inheritance
+only takes place at the class level and cannot be studied at a disaggregated
+level. 
+\item [{Cost~Effectiveness}] A concept used within the paper to assess
+defect models. The baseline is that funds are given to investigate
+{10\%} of a project for defects, in {10\%} of the lines of code
+taken at random {10\%} of the defects should be found. Models are
+compared against this baseline. 
 \end{description}
@@
 levels that would apply to lower levels. 
-\item \textbf{Related Work} To improve model performance, Koru \textit{et al.} recommend aggregating.
-Their methods to acheive improved performance include summing method-level measures into class-level measures and combining these with metrics from class-level features.
-They conclude that this approach overcomes the issues of asymmetry in defect data sets.
-Schr\"{o}ter \textit{et al.} conclude that predicting at coarser granularities is less difficult in comparison to finer granularities but lead to worse results.
-Zimmerman \textit{et al.} find different results where package level correlations and model correlations are higher than file level correlations and model correlations.
-Ambrose \textit{et al.} argue against the use of aggregate level metrics, though without data, stating predictions are more cumbersome to investigate,classes are inherently self-contained, and information derived from the package-level cannot be applied to the class level.
-\item \textbf{Motivational Statements}: The authors poses their motivation along with the central question of the paper "What is the right level of study?" (At an aggregated level or dis-aggregated level).
-They believe that this question has a central significance to whether or not a model that is built at a specific level of aggregation can hold at a lower level of aggregation as well as whether performance of the model as regards cost prediction is valid.
-\item \textbf{New Results}:  The authors grouped variables in the models based on loss of significance(LS) or gain of significance(GS).
-They explain that both LS and GS can cause Ecological Inferences issues as in a loss of significance situation when inferring between the aggregate level and the disaggregate level  or GS when inferring from the disaggregate to the aggregate.
-They found 28 instances of GS and 25 instances of LS out of 108 variables over 68 models.
-The authors draw the conclusion that models built at the aggregated level should be undertaken with the knowledge of the underlying risk of Ecological Inference and Ecological Fallacy.
-\item \textbf{Future Work}:The authors bring up three sources of Ecological Inference risk:  Zonation, Sample Size, and Class Imbalance.
-The authors believe that further study of the three sources is in order.
-To give a short background on how each applies:
+\item \textbf{Related Work} To improve model performance, Koru \textit{et
+al.} recommend aggregating. Their methods to acheive improved performance
+include summing method-level measures into class-level measures and
+combining these with metrics from class-level features. They conclude
+that this approach overcomes the issues of asymmetry in defect data
+sets. Schröter \textit{et al.} conclude that predicting at coarser
+granularities is less difficult in comparison to finer granularities
+but lead to worse results. Zimmerman \textit{et al.} find different
+results where package level correlations and model correlations are
+higher than file level correlations and model correlations. Ambrose
+\textit{et al.} argue against the use of aggregate level metrics,
+though without data, stating predictions are more cumbersome to investigate,classes
+are inherently self-contained, and information derived from the package-level
+cannot be applied to the class level. 
+\item \textbf{Motivational Statements}: The authors poses their motivation
+along with the central question of the paper \textquotedbl{}What is
+the right level of study?\textquotedbl{} (At an aggregated level or
+dis-aggregated level). They believe that this question has a central
+significance to whether or not a model that is built at a specific
+level of aggregation can hold at a lower level of aggregation as well
+as whether performance of the model as regards cost prediction is
+valid. 
+\item \textbf{New Results}: The authors grouped variables in the models
+based on loss of significance(LS) or gain of significance(GS). They
+explain that both LS and GS can cause Ecological Inferences issues
+as in a loss of significance situation when inferring between the
+aggregate level and the disaggregate level or GS when inferring from
+the disaggregate to the aggregate. They found 28 instances of GS and
+25 instances of LS out of 108 variables over 68 models. The authors
+draw the conclusion that models built at the aggregated level should
+be undertaken with the knowledge of the underlying risk of Ecological
+Inference and Ecological Fallacy. 
+\item \textbf{Future Work}:The authors bring up three sources of Ecological
+Inference risk: Zonation, Sample Size, and Class Imbalance. The authors
+believe that further study of the three sources is in order. To give
+a short background on how each applies:
+
 \begin{itemize}
-\item Zonation: Aggregation runs the risk of creating distortion by the way that the data is aggregated.  
-\item Sample Size:  As aggregation takes place inherently there is move to smaller and smaller sample sizes.
-As the move to those smaller sample sizes takes place there is a loss in Statistical power.
-\item Class Imbalance: A situation where a set of samples have a particular attribute and a large proportion of that set have a particular value with a very small number having another significant but underrepresented value.
-The example in the paper is a situation where there are a very high number of projects without defects and a very lower number with defects.
+\item Zonation: Aggregation runs the risk of creating distortion by the
+way that the data is aggregated. 
+\item Sample Size: As aggregation takes place inherently there is move to
+smaller and smaller sample sizes. As the move to those smaller sample
+sizes takes place there is a loss in Statistical power. 
+\item Class Imbalance: A situation where a set of samples have a particular
+attribute and a large proportion of that set have a particular value
+with a very small number having another significant but underrepresented
+value. The example in the paper is a situation where there are a very
+high number of projects without defects and a very lower number with
+defects. 
 \end{itemize}
-\item \textbf{Sampling Procedures}: Projects were taken from a set of 18 Apache Software Foundation Projects over 87 versions.
-The writers took JIRA issue reports and then mapped them to pull commits.
-Then, they took those commits and connected them to packages and files.
-They also pulled the number of lines of code as well as the number of developers per project.
-They were unable to look at past data sets due to their inability to correctly aggregate the data given that many data sets do not contain issue identifiers.
-
+\item \textbf{Sampling Procedures}: Projects were taken from a set of 18
+Apache Software Foundation Projects over 87 versions. The writers
+took JIRA issue reports and then mapped them to pull commits. Then,
+they took those commits and connected them to packages and files.
+They also pulled the number of lines of code as well as the number
+of developers per project. They were unable to look at past data sets
+due to their inability to correctly aggregate the data given that
+many data sets do not contain issue identifiers.
 \end{itemize}
@@
 \begin{itemize}
-\item There are some particularly distracting typos in the paper.
-For example, on pages 367-368 the authors failed to correctly reference their table correctly leaving "Table ??" in the middle of their text twice.
-\end{itemize}
+\item There are some particularly distracting typos in the paper. For example,
+on pages 367-368 the authors failed to correctly reference their table
+correctly leaving \textquotedbl{}Table ??\textquotedbl{} in the middle
+of their text twice. 
+\item The authors could have provided a better explanation of AUCROC and
+AUCCE and the meaning of their results with respect to those measures.
+The authors did a good job of comparing file and package measures,
+but did not explain why file AUCCE was lower than file AUCROC. Is
+this just the nature of AUCCE since it is including cost effectiveness?
+Why was there more variance in the AUCCE measures than AUCROC?
+\item At the end of the paper, the authors provide a brief note about threats
+to the external validity of the results. The authors only examined
+projects from one source: the Apache Software Foundation. Analyzing
+projects from other sources which employ different software engineering
+principles or which organize their projects differently would bolster
+their results and conclusions.\end{itemize}
+
 \end{document}

### 2015-09-03 hw/read/1/summary.tex
Merged motivational statement, expanded on results, fixed typos

@@
 research could be focused at the most granular level, for example
-files, methods, even lines of code, research at these levels is costly
-and takes time, so research instead usually examines data at higher
-levels. Therefore, it would be useful to draw conclusions from higher
-levels that would apply to lower levels. 
+files, methods, even lines of code, modeling at these levels is costly
+and takes time.
+The authors motivation is determine if statistical models built at an aggregated level are valid at the dis-aggregated level.
+A second motivation is to asses the cost-effectiveness of predication models at varying aggregated levels.
 \item \textbf{Related Work} To improve model performance, Koru \textit{et
@@
 cannot be applied to the class level. 
-\item \textbf{Motivational Statements}: The authors poses their motivation
-along with the central question of the paper \textquotedbl{}What is
-the right level of study?\textquotedbl{} (At an aggregated level or
-dis-aggregated level). They believe that this question has a central
-significance to whether or not a model that is built at a specific
-level of aggregation can hold at a lower level of aggregation as well
-as whether performance of the model as regards cost prediction is
-valid. 
-\item \textbf{New Results}: The authors grouped variables in the models
-based on loss of significance(LS) or gain of significance(GS). They
-explain that both LS and GS can cause Ecological Inferences issues
-as in a loss of significance situation when inferring between the
-aggregate level and the disaggregate level or GS when inferring from
-the disaggregate to the aggregate. They found 28 instances of GS and
-25 instances of LS out of 108 variables over 68 models. The authors
+\item \textbf{New Results}: The authors grouped features in the models
+based on loss of significance(LS) or gain of significance(GS). Both of these can result in Ecological Fallacy. 
+LS is a loss of significance when inferring from the
+aggregate level to the disaggregate level. GS is a gain of significance from the aggregate level to the file level. They found 28 instances of GS and
+25 instances of LS out of 108 features over 68 models. The authors
 draw the conclusion that models built at the aggregated level should
@@
 Inference and Ecological Fallacy.
+The author's also provided data showing the advantages of AUCCE over AUCROC when comparing models at different levels of aggregation.
+These results lead to two final conclusions: aggregated prediction models can evaluate better than actual when applied to aggregated data and as a consequence models build at an aggregated level may not be applicable to the dis-aggregated level.
 \item \textbf{Future Work}:The authors bring up three sources of Ecological
@@
 principles or which organize their projects differently would bolster
-their results and conclusions.\end{itemize}
+their results and conclusions.
+\end{itemize}
 

### 2015-09-03 hw/code/3/think10.py
word on code 3

@@ -1,4 +1,6 @@
 
+import random
+
 #Exercise 8.1
 def has_duplicates(x):
 	for i in x:
@@ -7,4 +9,14 @@ def has_duplicates(x):
 
 	return False
 
+
+def populateBirthdays(number):
+	return map(lambda _: random.randrange(1, 365, 1), range(number))
+
+def generateBirthdayStats(iterations):
+	x = filter(lambda x: x == True , map(lambda _: has_duplicates(populateBirthdays(23)), range(iterations)) ).__len__() / iterations
+	return x
+
+
+print generateBirthdayStats(100000)
 

### 2015-09-04 hw/code/3/Card.py
Added initial methods in poker for Code3

@@ -1,0 +1,136 @@
+"""This module contains code from
+Think Python by Allen B. Downey
+http://thinkpython.com
+
+Copyright 2012 Allen B. Downey
+License: GNU GPLv3 http://www.gnu.org/licenses/gpl.html
+
+"""
+
+import random
+
+
+class Card(object):
+    """Represents a standard playing card.
+    
+    Attributes:
+      suit: integer 0-3
+      rank: integer 1-13
+    """
+
+    suit_names = ["Clubs", "Diamonds", "Hearts", "Spades"]
+    rank_names = [None, "Ace", "2", "3", "4", "5", "6", "7", 
+              "8", "9", "10", "Jack", "Queen", "King"]
+
+    def __init__(self, suit=0, rank=2):
+        self.suit = suit
+        self.rank = rank
+
+    def __str__(self):
+        """Returns a human-readable string representation."""
+        return '%s of %s' % (Card.rank_names[self.rank],
+                             Card.suit_names[self.suit])
+
+    def __cmp__(self, other):
+        """Compares this card to other, first by suit, then rank.
+
+        Returns a positive number if this > other; negative if other > this;
+        and 0 if they are equivalent.
+        """
+        t1 = self.suit, self.rank
+        t2 = other.suit, other.rank
+        return cmp(t1, t2)
+
+
+class Deck(object):
+    """Represents a deck of cards.
+
+    Attributes:
+      cards: list of Card objects.
+    """
+    
+    def __init__(self):
+        self.cards = []
+        for suit in range(4):
+            for rank in range(1, 14):
+                card = Card(suit, rank)
+                self.cards.append(card)
+
+    def __str__(self):
+        res = []
+        for card in self.cards:
+            res.append(str(card))
+        return '\n'.join(res)
+
+    def add_card(self, card):
+        """Adds a card to the deck."""
+        self.cards.append(card)
+
+    def remove_card(self, card):
+        """Removes a card from the deck."""
+        self.cards.remove(card)
+
+    def pop_card(self, i=-1):
+        """Removes and returns a card from the deck.
+
+        i: index of the card to pop; by default, pops the last card.
+        """
+        return self.cards.pop(i)
+
+    def shuffle(self):
+        """Shuffles the cards in this deck."""
+        random.shuffle(self.cards)
+
+    def sort(self):
+        """Sorts the cards in ascending order."""
+        self.cards.sort()
+
+    def move_cards(self, hand, num):
+        """Moves the given number of cards from the deck into the Hand.
+
[…]

### 2015-09-04 hw/code/3/PokerHand.py

@@ -1,0 +1,146 @@
+"""This module contains code from
+Think Python by Allen B. Downey
+http://thinkpython.com
+
+Copyright 2012 Allen B. Downey
+License: GNU GPLv3 http://www.gnu.org/licenses/gpl.html
+
+"""
+
+from Card import *
+
+
+class PokerHand(Hand):
+
+    def suit_hist(self):
+        """Builds a histogram of the suits that appear in the hand.
+
+        Stores the result in attribute suits.
+        """
+        self.suits = {}
+        for card in self.cards:
+            self.suits[card.suit] = self.suits.get(card.suit, 0) + 1
+            
+    def rank_hist(self):
+        self.ranks = {}
+        for card in self.cards:
+            self.ranks[card.rank] = self.ranks.get(card.rank, 0) + 1
+        
+    def has_pair(self):
+        self.rank_hist()
+        for val in self.ranks.values():
+            if (val >= 2):
+                return True
+        return False
+        
+    def has_two_pair(self):
+        self.rank_hist()
+        num_pairs = 0
+        for val in self.ranks.values():
+            if (val >= 2):
+                num_pairs += 1
+        if (num_pairs >= 2):
+            return True
+        else:
+            return False
+            
+    def has_three_of_a_kind(self):
+        self.rank_hist()
+        for val in self.ranks.values():
+            if (val >= 3):
+                return True
+        return False
+        
+    def has_straight(self):
+        self.rank_hist()
+        consecutive_ranks = 0
+        max_consecutive_ranks = 0
+        for i in range(1,14):
+            val = self.ranks.get(i, 0)
+            
+            if (val > 0):
+                consecutive_ranks += 1
+            else:
+                if (consecutive_ranks > max_consecutive_ranks):
+                    max_consecutive_ranks = consecutive_ranks
+                consecutive_ranks = 0
+                
+        if (self.ranks.get(1, 0) > 0):
+            consecutive_ranks += 1
+        
+        if (consecutive_ranks > max_consecutive_ranks):
+            max_consecutive_ranks = consecutive_ranks
+                
+        return max_consecutive_ranks >= 5
+        
+    def has_flush(self):
+        """Returns True if the hand has a flush, False otherwise.
+      
+        Note that this works correctly for hands with more than 5 cards.
+        """
+        self.suit_hist()
+        for val in self.suits.values():
+            if val >= 5:
+                return True
+        return False
+        
+    def has_full_house(self):
+        self.rank_hist()
+        
+        three_of_a_kind = False
[…]

### 2015-09-07 hw/code/3/PokerHand.py
testing proved within a fairly reasonable margin of theoretical probability

@@ -166,7 +166,7 @@ if __name__ == '__main__':
     prob_dict = {'high_card': 0, 'one_pair': 0, 'two_pair': 0, 'three_of_a_kind': 0, \
                     'straight': 0, 'flush': 0, 'full_house': 0, 'four_of_a_kind': 0,\
                     'straight_flush': 0}
-    num_decks = 100000
+    num_decks = 10000000
     # Originally had this set to 7 and when
     # comparing to probabilities on wikipedia
     # with seven cards probabilities don't line

### 2015-09-07 hw/read/2/summary.tex
Initialized second paper summary and added definitions

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}

\title{Paper Two Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Erik Arisholm, Lionel C. Briand, and Eivind B. Johannessen. 2010. A systematic and comprehensive investigation of methods to build and evaluate fault prediction models. J. Syst. Softw. 83, 1 (January 2010), 2-17. DOI=10.1016/j.jss.2009.06.055 http://dx.doi.org/10.1016/j.jss.2009.06.055

\section*{Important Keywords}
\begin{description}
\item [{Fault-proneness}] The number of defects detected in a software-component. A measurement of the likelihood of software or software component error.
\item [{Object-oriented~(OO)~code~measures}] Measurement of the structural properties of the source code.
\item [{Delta~measures}] Measurement of the amount of change (churn) in a file between two successive releases.
\item [{Process~measures}] Measures from a configuration management system. Includes developer experience, the number of developers that have edited a file, the number of faults in the previous releases, the number of line added, the number of lines removed.

\end{description}

\end{document}

### 2015-09-08 hw/read/2/summary.tex
Added some feature extraction items and a possible improvement to paper 2

@@
 
-Erik Arisholm, Lionel C.
-Briand, and Eivind B.
-Johannessen.
-2010.
-A systematic and comprehensive investigation of methods to build and evaluate fault prediction models.
-J.
-Syst.
-Softw.
-83, 1 (January 2010), 2-17.
-DOI=10.1016/j.jss.2009.06.055 http://dx.doi.org/10.1016/j.jss.2009.06.055
+Erik Arisholm, Lionel C. Briand, and Eivind B. Johannessen. 2010.
+A systematic and comprehensive investigation of methods to build and
+evaluate fault prediction models. J. Syst. Softw. 83, 1 (January 2010),
+2-17. DOI=10.1016/j.jss.2009.06.055 http://dx.doi.org/10.1016/j.jss.2009.06.055
 
@@
 \begin{description}
-\item [{Fault-proneness}] The number of defects detected in a software-component. A measurement of the likelihood of software or software component error.
-\item [{Object-oriented~(OO)~code~measures}] Measurement of the structural properties of the source code.
-\item [{Delta~measures}] Measurement of the amount of change (churn) in a file between two successive releases.
+\item [{Fault-proneness}] The number of defects detected in a software-component.
+A measurement of the likelihood of software or software component
+error. 
+\item [{Object-oriented~(OO)~code~measures}] Measurement of the structural
+properties of the source code. 
+\item [{Delta~measures}] Measurement of the amount of change (churn) in
+a file between two successive releases. 
 \item [{Process~measures}] Measures from a configuration management system.
-Includes developer experience, the number of developers that have edited a file, the number of faults in the previous releases, the number of line added, the number of lines removed.
-
+Includes developer experience, the number of developers that have
+edited a file, the number of faults in the previous releases, the
+number of line added, the number of lines removed.
 \end{description}
 
+\section*{Feature Extraction}
+\begin{description}
+\item [{Motivational~statements}] The authors mentioned that most previous
+studies only examined the structure of the code when constructing
+fault-proneness prediction models. In the few studies that did, they
+did not systematically measure the cost-effectiveness of the models
+with factors with different data collection costs. Very few studies
+have looked at the methods and criteria for evaluating the models.
+Finally, it is very difficult to draw general conclusions using confusion
+matrices since they do not provide any insight into determining the
+cost-effectiveness of the models under test.
+\item [{Future~Work}] The authors used the default parameters for the
+statistical techniques they employed in the study. They have stated
+that they hope to tweak the parameters and observe the results to
+see if there are optimizations that can be made while at the same
+time try to avoid overfitting. The authors also stated they are going
+to work on a large-scale evaluation of the costs and benefits of various
+prediction models in the COS project.
+\end{description}
+
+\section*{Possible Improvements}
+\begin{itemize}
+\item In the Introduction section, the authors reference a paper published
+in 1989 to cite a percentage of effort spent on testing. Is there
+a more recent paper the authors could have chosen to cite? If not,
+why quote a figure that is 26 years old and quite possibly outdated?\end{itemize}
+
 \end{document}

### 2015-09-08 hw/read/2/summary.tex
added reference section features, commentary, and connection section

@@
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
 \usepackage{babel}
@@
 
-Erik Arisholm, Lionel C. Briand, and Eivind B. Johannessen. 2010.
-A systematic and comprehensive investigation of methods to build and
-evaluate fault prediction models. J. Syst. Softw. 83, 1 (January 2010),
-2-17. DOI=10.1016/j.jss.2009.06.055 http://dx.doi.org/10.1016/j.jss.2009.06.055
+Arisholm et al \cite{arisholm10} listed below.
 
@@
 cost-effectiveness of the models under test.
+
+\item[{Motivational Statements}]  The motivation was to provide a systematic methodology for comparing modeling techniques.
+The authors state that little to no effort was put forth to prior to this paper in that area.
+
+\item[{Patterns}]  The authors provide an overview of a number of different techniques and different metric sets in an attempt to prove which provides the best results across comparison techniques.
+The results seem to show that the ROC curve combined with cost effectiveness comparisons provide a good deal of insight into the performance of techniques and matrices as compared to using the confusion matrix approach.
+
 \item [{Future~Work}] The authors used the default parameters for the
@@
 see if there are optimizations that can be made while at the same
-time try to avoid overfitting. The authors also stated they are going
+time preventing overfitting. The authors also stated they are going
 to work on a large-scale evaluation of the costs and benefits of various
 prediction models in the COS project.
+
+\item[{Informative Visualizations}]  Figure four on page 12 of the paper provides a really interesting visualization of the distribution of cost efficiency of prediction models using Process and Object Oriented metrics.
+The figure provides two lines, one for OO and one for Process metrics, but they also provide clouds around those lines that demarcate the 25th and 75th percentiles.
+The authors use this figure to show the fact that the performance of OO metrics based models is poor compared with Process.
+The baseline for this study was a line such that $y=x$ so as is shown in the figure, OO has very close to the baseline performance while OO outperforms the baseline by a significant margin.
 \end{description}
@@
 a more recent paper the authors could have chosen to cite? If not,
-why quote a figure that is 26 years old and quite possibly outdated?\end{itemize}
+why quote a figure that is 26 years old and quite possibly outdated?
+
+\item While the way that the authors combined data in an attempt to consolidate it to a smaller number of tables was very clever, it produces tables that are very difficult to interpret.
+They have split the data into a standard set of stats (mean, median, Q1, Q3) on half of the table and then created a diagonal split on the other half of the table into two sets of data, one for effect size and the other for the Wilcoxon test data.
+It seems that they had so much data to report that it would have been impossible to report it in the space they had available without this type of table, but perhaps some further graphical representation would have been preferable with an appendix of the tables and data sets split out into more easily decipherable tables.
+
+\end{itemize}
+
+\section*{Connection to Other Papers}
+Posnett et al \cite{posnett11} cited this paper as well as Menzies et al \cite{menzies10} as evidence that prediction models designed for the aggregated level have poor performance at the disaggregated level.
+But moreover the Posnett paper uses this paper as a methodological foundation for the way that they went about using the ROC curve and Cost Effectiveness analysis that they used in their study.
+
+\bibliography{references}{}
+\bibliographystyle{plain}
 

### 2015-09-08 hw/read/2/summary.tex
Clarified first motivational statement and fixed encoding error

@@
 \usepackage[T1]{fontenc}
+\usepackage[latin9]{inputenc}
 \usepackage{babel}
@@
 studies only examined the structure of the code when constructing
-fault-proneness prediction models. In the few studies that did, they
-did not systematically measure the cost-effectiveness of the models
-with factors with different data collection costs. Very few studies
-have looked at the methods and criteria for evaluating the models.
-Finally, it is very difficult to draw general conclusions using confusion
-matrices since they do not provide any insight into determining the
-cost-effectiveness of the models under test.
-
-\item[{Motivational Statements}]  The motivation was to provide a systematic methodology for comparing modeling techniques.
-The authors state that little to no effort was put forth to prior to this paper in that area.
-
-\item[{Patterns}]  The authors provide an overview of a number of different techniques and different metric sets in an attempt to prove which provides the best results across comparison techniques.
-The results seem to show that the ROC curve combined with cost effectiveness comparisons provide a good deal of insight into the performance of techniques and matrices as compared to using the confusion matrix approach.
-
+fault-proneness prediction models. In the few studies that did not,
+they failed to systematically measure the cost-effectiveness of the
+models with factors with different data collection costs. Very few
+studies have looked at the methods and criteria for evaluating the
+models. Finally, it is very difficult to draw specific conclusions
+using confusion matrices since they do not provide any insight into
+determining the cost-effectiveness of the models under test.
+\item [{Motivational Statements}] The motivation was to provide a systematic
+methodology for comparing modeling techniques. The authors state that
+little to no effort was put forth to prior to this paper in that area.
+\item [{Patterns}] The authors provide an overview of a number of different
+techniques and different metric sets in an attempt to prove which
+provides the best results across comparison techniques. The results
+seem to show that the ROC curve combined with cost effectiveness comparisons
+provide a good deal of insight into the performance of techniques
+and matrices as compared to using the confusion matrix approach.
 \item [{Future~Work}] The authors used the default parameters for the
@@
 prediction models in the COS project.
-
-\item[{Informative Visualizations}]  Figure four on page 12 of the paper provides a really interesting visualization of the distribution of cost efficiency of prediction models using Process and Object Oriented metrics.
-The figure provides two lines, one for OO and one for Process metrics, but they also provide clouds around those lines that demarcate the 25th and 75th percentiles.
-The authors use this figure to show the fact that the performance of OO metrics based models is poor compared with Process.
-The baseline for this study was a line such that $y=x$ so as is shown in the figure, OO has very close to the baseline performance while OO outperforms the baseline by a significant margin.
+\item [{Informative Visualizations}] Figure four on page 12 of the paper
+provides a really interesting visualization of the distribution of
+cost efficiency of prediction models using Process and Object Oriented
+metrics. The figure provides two lines, one for OO and one for Process
+metrics, but they also provide clouds around those lines that demarcate
+the 25th and 75th percentiles. The authors use this figure to show
+the fact that the performance of OO metrics based models is poor compared
+with Process. The baseline for this study was a line such that $y=x$
+so as is shown in the figure, OO has very close to the baseline performance
+while OO outperforms the baseline by a significant margin. 
 \end{description}
@@
 why quote a figure that is 26 years old and quite possibly outdated?
-
-\item While the way that the authors combined data in an attempt to consolidate it to a smaller number of tables was very clever, it produces tables that are very difficult to interpret.
-They have split the data into a standard set of stats (mean, median, Q1, Q3) on half of the table and then created a diagonal split on the other half of the table into two sets of data, one for effect size and the other for the Wilcoxon test data.
-It seems that they had so much data to report that it would have been impossible to report it in the space they had available without this type of table, but perhaps some further graphical representation would have been preferable with an appendix of the tables and data sets split out into more easily decipherable tables.
-
+\item While the way that the authors combined data in an attempt to consolidate
+it to a smaller number of tables was very clever, it produces tables
+that are very difficult to interpret. They have split the data into
+a standard set of stats (mean, median, Q1, Q3) on half of the table
+and then created a diagonal split on the other half of the table into
+two sets of data, one for effect size and the other for the Wilcoxon
+test data. It seems that they had so much data to report that it would
+have been impossible to report it in the space they had available
+without this type of table, but perhaps some further graphical representation
+would have been preferable with an appendix of the tables and data
+sets split out into more easily decipherable tables.
 \end{itemize}
@@
 \section*{Connection to Other Papers}
-Posnett et al \cite{posnett11} cited this paper as well as Menzies et al \cite{menzies10} as evidence that prediction models designed for the aggregated level have poor performance at the disaggregated level.
-But moreover the Posnett paper uses this paper as a methodological foundation for the way that they went about using the ROC curve and Cost Effectiveness analysis that they used in their study.
 
-\bibliography{references}{}
+Posnett et al \cite{posnett11} cited this paper as well as Menzies
+et al \cite{menzies10} as evidence that prediction models designed
+for the aggregated level have poor performance at the disaggregated
+level. But moreover the Posnett paper uses this paper as a methodological
+foundation for the way that they went about using the ROC curve and
+Cost Effectiveness analysis that they used in their study.
+
 \bibliographystyle{plain}
-
+\bibliography{references}
+{} \bibliographystyle{plain}
 \end{document}

### 2015-09-09 hw/read/2/summary.tex
Added another possible improvement to paper 2

@@
 sets split out into more easily decipherable tables. 
+\item The authors mentioned that one threat to the validity of the study
+was that the cost of making the measures available and collecting
+them was not accounted for. It seems that such calcuations should
+be taken into account. Additionally, they note that the Process metric
+set has a high cost of data reporting and collection but was found
+to be the most cost-effective. It is hard to say if Process is indeed
+the most cost-effective, since all cost measures were not taken into
+consideration. A future study should include as many cost factors
+as possible when determining the cost-effectiveness of a particular
+method or metric.
 \end{itemize}

### 2015-09-12 hw/code/4/SimAnnealing.py
setup baseline study for shaffer

@@ -1,0 +1,44 @@
+import random
+
+def shaffer(f1, f2):
+  f1 = f1*f1
+  f2 = (f2 - 2) * (f2 - 2)
+  return f1 + f2
+
+def normalization(f1, f2):
+  return ((f1+f2) - 0) / (1 - 0)
+
+def base_runner():
+  # list of minimum observations for 100 iterations
+  # of the model being run 100 times each
+  min_obs = []
+  # list of max observations for 100 iterations
+  # of the model being run 100 times each
+  max_obs = []
+
+  # Run the baseline model test 100 times
+  for i in range(100):
+    # observations for each run
+    obs = []
+    # Run the model 100 times
+    for j in range(100):
+      f1 = random.random()
+      f2 = random.random()
+      obs.append((f1,f2, shaffer(f1,f2)))
+
+    # Sort by the shaffer value
+    obs = sorted(obs, key=lambda ob: ob[2])
+
+    # Add the min and max of this run
+    min_obs.append(obs[0])
+    max_obs.append(obs[-1])
+
+  min_obs = sorted(min_obs, key=lambda ob: ob[2])
+  max_obs = sorted(max_obs, key=lambda ob: ob[2])
+
+  print 'median min observation: ' + str(min_obs[49][0]) + '\t' + str(min_obs[49][1]) + '\t' + str(min_obs[49][2])
+  print 'median max observation: ' + str(max_obs[49][0]) + '\t' + str(max_obs[49][1]) + '\t' + str(max_obs[49][2])
+  print 'abs min observation: ' + str(min_obs[0][0]) + '\t' + str(min_obs[0][1]) + '\t' + str(min_obs[0][2])
+  print 'abs max observation: ' + str(max_obs[-1][0]) + '\t' + str(max_obs[-1][1]) + '\t' + str(max_obs[-1][2])
+
+base_runner()

### 2015-09-12 hw/read/2/summary.tex

@@
 \item [{Object-oriented~(OO)~code~measures}] Measurement of the structural
-properties of the source code. 
+properties of the source code. For example cyclomatic complexity and LOC.
 \item [{Delta~measures}] Measurement of the amount of change (churn) in
@@
 \begin{description}
-\item [{Motivational~statements}] The authors mentioned that most previous
-studies only examined the structure of the code when constructing
-fault-proneness prediction models. In the few studies that did not,
-they failed to systematically measure the cost-effectiveness of the
-models with factors with different data collection costs. Very few
-studies have looked at the methods and criteria for evaluating the
-models. Finally, it is very difficult to draw specific conclusions
-using confusion matrices since they do not provide any insight into
-determining the cost-effectiveness of the models under test. 
-\item [{Motivational Statements}] The motivation was to provide a systematic
-methodology for comparing modeling techniques. The authors state that
-little to no effort was put forth to prior to this paper in that area. 
+\item [{Motivational~statements}] The motivation of this study was to compare multiple feature sets, machine learning techniques, and evaluation criteria to determine the most useful combination at predicting fault-proneness in a continually changing codebase.
+The authors leverage both structural measurements inherent to the code and process measurements derived from configuration management systems.
+Due to the lack of evidence for the economic viability of fault-proneness detection, the authors introduce a novel evaluation criteria, cost-effectiveness (CE) measure, which incorporates the verification costs of detected faults.
 \item [{Patterns}] The authors provide an overview of a number of different
@@
 seem to show that the ROC curve combined with cost effectiveness comparisons
-provide a good deal of insight into the performance of techniques
+provide more insight into the performance of techniques
 and matrices as compared to using the confusion matrix approach. 
@@
 why quote a figure that is 26 years old and quite possibly outdated? 
-\item While the way that the authors combined data in an attempt to consolidate
+\item While the way the authors combined data in an attempt to consolidate
 it to a smaller number of tables was very clever, it produces tables
@@
 was that the cost of making the measures available and collecting
-them was not accounted for. It seems that such calcuations should
-be taken into account. Additionally, they note that the Process metric
+them was not accounted for. It seems that such calculations should
+be taken into account. Additionally, they note the Process metric
 set has a high cost of data reporting and collection but was found

### 2015-09-17 hw/code/4/SimAnnealing.py
added some print lines to check out a few things

@@ -31,7 +31,15 @@ def energy(f1_norm, f2_norm):
     s = schaffer(x)
     x = f1_norm(s[0])
     y = f2_norm(s[1])
+    # print '\n'
+    # print 'x is ' + str(x)
+    # print 'f1 is ' + str(s[0])
+    # print 'f2 is ' + str(s[1])
+    # print 'f1 normlized is ' + str(x)
+    # print 'f2 normalized is ' + str(y)
     dist_from_hell = ((1 - x)**2 + (1 - y)**2)**0.5
+    # print 'dist from hell ' + str(dist_from_hell)
+
     return dist_from_hell
   return e
 
@@ -42,7 +50,7 @@ def base_runner():
   obs = []
 
   # Run the baseline model test 100 times
-  for j in range(100):
+  for j in range(1000):
     x = random.random()
     y_tup = schaffer(x)
 
@@ -53,6 +61,11 @@ def base_runner():
     # Sort by f2 values
     f2_obs = sorted(obs, key=lambda ob: ob[1])
 
+  # print 'f1 max ' +  str(f1_obs[-1][0])
+  # print 'f1 min ' + str(f1_obs[0][0])
+  # print 'f2 max ' + str(f2_obs[-1][1])
+  # print 'f2 min ' + str(f2_obs[0][1])
+
   # Returns normalization function for f1
   norm_f1 = normalize(f1_obs[0][0], f1_obs[-1][0])
 
@@ -62,6 +75,7 @@ def base_runner():
   # This is all just a sanity check.  To make sure that
   # everything works as expected.  Check it out if you want.
   #
+
   # norm_f1_obs = [norm_f1(f1) for f1,f2 in f1_obs]
   # norm_f2_obs = [norm_f2(f2) for f1,f2 in f2_obs]
 
@@ -131,7 +145,7 @@ def sim_anneal(energy):
       e = en
       say("?")
 
-    say(".")
+    #say(".")
     k += 1.0
 
     if k % 50 == 0:
@@ -144,19 +158,3 @@ if __name__ == "__main__":
   norm_tup = base_runner()
   e = energy(norm_tup[0], norm_tup[1])
   sim_anneal(e)
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-

### 2015-09-17 hw/code/4/SimAnnealing.py
Added wrapping, removed -1.0 factor from prob to deal with maximization, code still doesn't cool correctly

@@ -96,12 +96,19 @@ def base_runner():
   return (norm_f1, norm_f2)
 
 def neighbor(x):
-  epsilon = 0.01
+  epsilon = 0.001
   add = bool(random.getrandbits(1))
   if add:
     x += epsilon
   else:
     x -= epsilon
+
+  if x < 0.0:
+    x = x + 1.0
+
+  if x > 1.0:
+    x = x - 1.0
+     
   return x
 
 def say(x):
@@ -109,7 +116,9 @@ def say(x):
 
 # Something isn't right here.
 def prob(old, new, k):
-  return math.exp( -1.0 * ((new - old) / k))
+  x = math.exp(((new - old) / k))
+  #say(x)
+  return x
 
 global kmax
 global emax
@@ -140,15 +149,15 @@ def sim_anneal(energy):
       e = en
       say("+")
 
-    elif prob(e, en, k / kmax) > random.random():
+    elif prob(e, en, (kmax - k) / kmax) > random.random():
       s = sn
       e = en
       say("?")
 
     #say(".")
-    k += 1.0
+    k += 1.00
 
-    if k % 50 == 0:
+    if math.floor(k) % 50 == 0:
       say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(sb))
 
   print '\n \nbest solution ' + str(sb)

### 2015-09-17 hw/code/4/SimAnnealing.py
fixed some experimental changes

@@ -96,7 +96,7 @@ def base_runner():
   return (norm_f1, norm_f2)
 
 def neighbor(x):
-  epsilon = 0.001
+  epsilon = 0.01
   add = bool(random.getrandbits(1))
   if add:
     x += epsilon
@@ -157,7 +157,7 @@ def sim_anneal(energy):
     #say(".")
     k += 1.00
 
-    if math.floor(k) % 50 == 0:
+    if k % 50 == 0:
       say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(sb))
 
   print '\n \nbest solution ' + str(sb)

### 2015-09-17 hw/code/4/SimAnnealing.py
Improved probability in SA

@@ -114,10 +114,8 @@ def neighbor(x):
 def say(x):
   sys.stdout.write(str(x)); sys.stdout.flush()
 
-# Something isn't right here.
 def prob(old, new, k):
   x = math.exp(((new - old) / k))
-  #say(x)
   return x
 
 global kmax
@@ -126,12 +124,15 @@ kmax = 10000.0
 emax = (2)**0.5
 
 def sim_anneal(energy):
-  s0 = 0.0
+  s0 = 0.5
   s = s0
   e = energy(s)
+  print "Initial energy", e
   sb = s
   eb = e
   k = 1.0
+  
+  say('(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
 
   while k < kmax and e < emax:
     sn = neighbor(s)
@@ -149,16 +150,16 @@ def sim_anneal(energy):
       e = en
       say("+")
 
-    elif prob(e, en, (kmax - k) / kmax) > random.random():
+    elif prob(e, en, k / kmax) < random.random():
       s = sn
       e = en
       say("?")
 
-    #say(".")
+    say(".")
     k += 1.00
 
     if k % 50 == 0:
-      say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(sb))
+      say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
 
   print '\n \nbest solution ' + str(sb)
   print 'energy of best solution ' + str(energy(sb))

### 2015-09-17 hw/read/3/summary.tex
Began summary for Paper 3

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}

\title{Paper Three Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Bird et al \cite{bird09} listed below.

\section*{Important Keywords}
\begin{description}
\item [{Global development}] Development that is globally distributed but takes place within one company. The authors contrast this to \emph{outsourcing}, in which development takes place among multiple companies and \emph{collocated development}, where development takes place in one location. 
\item [{Coordination breakdown}] A difficulty usually encountered in distributed development where employees in one location are not appropriately aware or responsive to the work of employees in another location.
\item [{Binary distribution}] Different levels of classifications for where binaries are developed. The authors give \emph{building, cafeteria, campus, locality, continent, } and \emph{world} as different ways to classify binary distribution.
\item [{Organizational integration}] An organizational structure that spans geographical locations at low levels.
\end{description}

\section*{Feature Extraction}

\section*{Possible Improvements}

\section*{Connection to Other Papers}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-09-17 notes/notes09172015.py
Notes for 09172015

@@ -1,0 +1,80 @@
+#not sure if this compiles it's from the chalkboard
+#fib closures
+def memo(f):		
+	cache = {}
+	def wrappedfunction(*args, **d):	#list of args, list of keyword arguments, generic call for any python function 
+		if n in cache:
+			return cache[n]
+		else:
+			tmp = f(*args, **d)
+			cache[n] = tmp
+			return tmp
+	return wrappedfunction
+
+@memo
+def fib(n):
+	if n < 2:
+		return 1
+	else:
+		return f(n-2) + f(n-1)
+
+
+#first class object functions
+@memo
+def lt(x,y):
+	return x < y
+
+def gt(x,y):
+	return x > y
+
+def check(x, y, better=lt):
+	return 	better(x, y)
+
+# SA
+# candidate solutions: 1. decisions 2. objectives 3. aggregates(optional)
+# candidate = decisions + objectives + aggregates(optional)
+# Schaffer has 1 decision = x, 2 objectives = f1, f2, aggregate = from_hell_measure
+# Quantile chart from notes:
+# 	each line is an era
+# 	each line is a summary of the f1 scores from each line above
+
+# Relax video
+# Multi-objective overtime planning paper
+# 	vector with work packages, n tasks with each task having a certain amount overtime
+# 	each candidate is a set of decisions with a certain amount of overtime
+# 	took NSGAII and made simple change
+# 	2 point crossover apply max and min
+# 	changes to a model are big changes, putting domain knowledge into models is very powerful
+
+
+# Goals
+# 	Goal-based modeling summary 
+# 	Traceability: map to summary(requirements document), does the code satisfy the requirements, 10^7 LOC train!, smart!
+# 	Runtime Verification:	10^6 LOC, train!!, smart!!
+# 	Model Checking: return crash or no, if I can find a pathway to an error 10^4 LOC, train!!!, smart!!!
+# 	Theorem Proving: will crash if it runs our of memory 10^3, train!!!!, smart!!!!
+
+# Requirements engineering people
+# 	user requirements are comical 
+# 	Myopoulous, Fickas, Lamsweerde are researches who analyse human wims
+# 	We can explore conflicting human ideals
+
+# MaxWalkSat
+# 	small change to SE
+# 	by code 6 we should be able to pass any model into our optimizers, don't be clever for code 4 or code 5
+# 	Sampling the landscape of the local region, peaks at the curve
+# 	Jumps anywhere at random half the time
[…]

### 2015-09-18 hw/code/4/SimAnnealing.py
Added temp dependent neighbors

@@ -95,8 +95,8 @@ def base_runner():
 
   return (norm_f1, norm_f2)
 
-def neighbor(x):
-  epsilon = 0.01
+def neighbor(x, temp):
+  epsilon = temp * random.random()
   add = bool(random.getrandbits(1))
   if add:
     x += epsilon
@@ -135,7 +135,7 @@ def sim_anneal(energy):
   say('(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
 
   while k < kmax and e < emax:
-    sn = neighbor(s)
+    sn = neighbor(s, (kmax - k)/kmax)
     en = energy(sn)
 
     # Is this a best overall?

### 2015-09-22 hw/code/5/MaxWalkSat.py
transferred same framework at code4 added osyczka2

@@ -1,0 +1,172 @@
+import random, math, sys
+
+# Calculates f1 and f2 and then
+# returns the values in a tuple
+# f1,f2
+def osyczka2(x1, x2, x3, x4, x5, x6):
+  f1 = -(25*(x1-2)**2 + (x2 - 2)**2 + (x3 - 1)**2 * (x4-4)**2 + (x5 - 1)**2)
+  f2 = x1**2 + x2**2 + x3**2 + x4**2 + x5**2 + x6**2
+  return (f1, f2)
+
+# This returns the normalization function
+# for one of the two observation functions (f1, f2)
+# b1 is the minimum, b2 is the maximum
+def normalize(b1, b2):
+  def n(x):
+    return (x - b1) / (b2 - b1)
+  return n
+
+# This returns the energy function for x
+# basically it takes the two normalization
+# functions as parameters and then treats those
+# normalization functions return values as the
+# x and y values in the x,y plane.  F1 returns x,
+# f2 returns y.  We know for schaffer that hell
+# is at (1,1) in this graph.  We calculate distance
+# to hell from our x,y point and return it as our
+# energy value.  For this simplified environment
+# emax is sqrt(2).
+
+def energy(f1_norm, f2_norm):
+  def e(x):
+    s = osyczka2(x)
+    x = f1_norm(s[0])
+    y = f2_norm(s[1])
+    # print '\n'
+    # print 'x is ' + str(x)
+    # print 'f1 is ' + str(s[0])
+    # print 'f2 is ' + str(s[1])
+    # print 'f1 normlized is ' + str(x)
+    # print 'f2 normalized is ' + str(y)
+    dist_from_hell = ((1 - x)**2 + (1 - y)**2)**0.5
+    # print 'dist from hell ' + str(dist_from_hell)
+
+    return dist_from_hell
+  return e
+
+
+#TODO: adapt for oszyzcka2 constraints
+def base_runner():
+  f1_obs = []
+  f2_obs = []
+  obs = []
+
+  # Run the baseline model test 100 times
+  for j in range(1000):
+    x = random.random()
+    y_tup = schaffer(x)
+
+    obs.append(y_tup)
+
+    # Sort by f1 values
+    f1_obs = sorted(obs, key=lambda ob: ob[0])
+    # Sort by f2 values
[…]

### 2015-09-22 hw/read/3/summary.tex
Added some more stuff to paper 3's summary

@@
 \section*{Feature Extraction}
+\begin{description}
+\item[Hypotheses] The authors list two hypotheses \cite{bird09}: 
+\begin{quote}
+\emph{H1: Binaries that are developed by teams of engineers that are distributed will have more post-release failures than those developed by collocated engineers.}
+\end{quote}
+\begin{quote}
+\emph{H2: Binaries that are distributed will be less complex, experience less code churn, and have fewer dependencies than collocated binaries.}
+\end{quote}
+\item[Future Work] The authors note that there haven't been any causal relationshisp established between development practices and effective distributed development.
+They suggest studies to examine the effects of various development practices on distributed development.
+\end{description}
 
@@
 \section*{Connection to Other Papers}
+	Our first paper \cite{posnett11} cited geographical issues as a difficulty in interpreting aggregated results.
+They ask how the work should be divided among multiple locations to maximize quality and productivity, initially suggesting that development should not be split over different locations.
+They note that this study found different results, that geographical distribution had little to no effect on software quality.
+
+The authors also mentioned that this study examined software on the binary level (an aggregated level), which supports their claim that aggregation is very common in defect modeling research.
 

### 2015-09-22 notes/notes09222015.py
09222015 notes

@@ -1,0 +1,91 @@
+Re pushes back
+Prior to Toronto group (Myopolis et al) requirements weren't considered in SE, people like Djikstra said requirements weren't part of SE
+Local search: surf the turf (moto of maxwalksat -> sample the search space around the current solutions because water runs down hill)
+maxwalksat does two things either sample around current space or jump to new space
+maxwalksat is an example of local search
+SA can mutate any number of decisions while maxwalksat only mutates one
+
+Schaffer min(f1 + f2) at x = 1
+Fun with Fonseca
+
+
+gadgetgetsok.txt -> coded SA by Menzies (line 248)
+contextmanager called Study -> prints time, prints all the magic constants, epsilon 
+tiles -> prints quantile distribution
+prints f1 scores -> after SA values have gone down
+prints f2 scores -> medians ahve gone down after SA
+Fonsica has problem -> issue with the model, it's basically flat: talke to user, can also use elite sampling where the values can influence your next choice (a king of heuristic search)
+ZDT1 -> SA is kicking butt and taking names
+you have to reflect as much on the models as the optimizers
+
+fromHell-> hell: 1,1 heaven: 0,0 : we can express as distance from heaven or distance from hell
+normalize with sqrt(2) 
+from heaven is a smaller space(exploring smaller space)
+from hell is larger (exploring a larger space), preferrable because we are about options, we want to present users with range of options, possibly solutions they never thought of
+
+Model project -> how to build a model
+business user who is knowlegable and wants to build a model
+
+Doman-Specific Languages 101: https://github.com/txt/mase/blob/master/src/dsl101.md
+Compartmental modeling: stocks and flows, tubes carry stuff to tubs
+linked book has compartmental model ("Software Process Dynamics" - Raymond J.Madachy)
+Does you language pass the elbow test -> do business users elbow you out of the way to change something wrong on the screen
+can you abstract the business knowledge, allow busines users do the coding, if business users cannot elbow you out the way you've lost something
+All the little languages 
+Read Godel, Esher, Bach
+From 1967 -> needed programming languages that are as natural as possible
+DSL is a high level language that user can learn in less than a day
+Ideoms: Methods imposed by programmers to handle common forms
+External DSLs are hard (compilers) string is manipulated and evaluated
+Internal DSLs are easier
+Python decorators: @ok
+Decorators run from top to bottom
+Logger and timer are tiny examples of an idiom, wrapping up common processes\
+Watch implementing domain specific languages in python
+
[…]

### 2015-09-23 hw/code/5/MaxWalkSat.py
added constraint checker

@@ -8,6 +8,18 @@ def osyczka2(x1, x2, x3, x4, x5, x6):
   f2 = x1**2 + x2**2 + x3**2 + x4**2 + x5**2 + x6**2
   return (f1, f2)
 
+#osyczka2 constraints: checks all costraints, returns true is all constraints met
+#new mutation should be done if this returns false
+def constraints(x1, x2, x3, x4, x5, x6):
+  if(x1 + x2 - 2 < 0): return False
+  if(6 - x1 - x2 < 0): return False
+  if(2 - x2 + x1 < 0): return False
+  if(4 - (x3 - 3)**2 - x4 < 0): return False
+  if((x5 - 3)**3 + x6 - 4 < 0): return False
+
+  return True
+
+
 # This returns the normalization function
 # for one of the two observation functions (f1, f2)
 # b1 is the minimum, b2 is the maximum
@@ -51,10 +63,17 @@ def base_runner():
   f2_obs = []
   obs = []
 
-  # Run the baseline model test 100 times
+  # Run the baseline model test 1000 times
+  # bounds:
+  # x1 >= 0
+  # x2 <= 10
+  # x3 >= 1
+  # x5 <= 5
+  # 0 <= x4 <= 6
+  # 0 <= x6 <= 10
   for j in range(1000):
     x = random.random()
-    y_tup = schaffer(x)
+    y_tup = oszyzcka2(x)
 
     obs.append(y_tup)
 

### 2015-09-23 notes/notes09222015.py

@@ -1,70 +1,70 @@
-Re pushes back
-Prior to Toronto group (Myopolis et al) requirements weren't considered in SE, people like Djikstra said requirements weren't part of SE
-Local search: surf the turf (moto of maxwalksat -> sample the search space around the current solutions because water runs down hill)
-maxwalksat does two things either sample around current space or jump to new space
-maxwalksat is an example of local search
-SA can mutate any number of decisions while maxwalksat only mutates one
+# Re pushes back
+# Prior to Toronto group (Myopolis et al) requirements weren't considered in SE, people like Djikstra said requirements weren't part of SE
+# Local search: surf the turf (moto of maxwalksat -> sample the search space around the current solutions because water runs down hill)
+# maxwalksat does two things either sample around current space or jump to new space
+# maxwalksat is an example of local search
+# SA can mutate any number of decisions while maxwalksat only mutates one
 
-Schaffer min(f1 + f2) at x = 1
-Fun with Fonseca
+# Schaffer min(f1 + f2) at x = 1
+# Fun with Fonseca
 
 
-gadgetgetsok.txt -> coded SA by Menzies (line 248)
-contextmanager called Study -> prints time, prints all the magic constants, epsilon 
-tiles -> prints quantile distribution
-prints f1 scores -> after SA values have gone down
-prints f2 scores -> medians ahve gone down after SA
-Fonsica has problem -> issue with the model, it's basically flat: talke to user, can also use elite sampling where the values can influence your next choice (a king of heuristic search)
-ZDT1 -> SA is kicking butt and taking names
-you have to reflect as much on the models as the optimizers
+# gadgetgetsok.txt -> coded SA by Menzies (line 248)
+# contextmanager called Study -> prints time, prints all the magic constants, epsilon 
+# tiles -> prints quantile distribution
+# prints f1 scores -> after SA values have gone down
+# prints f2 scores -> medians ahve gone down after SA
+# Fonsica has problem -> issue with the model, it's basically flat: talke to user, can also use elite sampling where the values can influence your next choice (a king of heuristic search)
+# ZDT1 -> SA is kicking butt and taking names
+# you have to reflect as much on the models as the optimizers
 
-fromHell-> hell: 1,1 heaven: 0,0 : we can express as distance from heaven or distance from hell
-normalize with sqrt(2) 
-from heaven is a smaller space(exploring smaller space)
-from hell is larger (exploring a larger space), preferrable because we are about options, we want to present users with range of options, possibly solutions they never thought of
[…]

### 2015-09-23 hw/read/3/summary.tex
added motivational statement

@@
 \section*{Feature Extraction}
+\item [{Motivational~statements}] The motivation of this study was to compare the post release failures of Windows Vista components developed in a distributed fashion to those developed in a collocated teams as to attain insight into the affect of distributed team developement against collocated team development.
 \begin{description}

### 2015-09-23 hw/read/3/summary.tex
formatting

--- 2015-09-22 hw/read/3/summary.tex
@@
 \begin{description}
+\item [{Motivational~statements}] The motivation of this study was to compare the post release failures of Windows Vista components developed in a distributed fashion to those developed by collocated teams as to attain insight into the affect of distributed team development against collocated team development.
 \item[Hypotheses] The authors list two hypotheses \cite{bird09}: 

### 2015-09-23 hw/read/3/summary.tex
added more to the motivational statement
added informative visualizations, possible improvements, edits

@@
 \item [{Motivational~statements}] The motivation of this study was to compare the post release failures of Windows Vista components developed in a distributed fashion to those developed by collocated teams as to attain insight into the affect of distributed team development against collocated team development.
+Additionally, they aim to study whether the projects assigned to distributed teams were less complex.
+The idea there is that post release failures are expected in distributed teams to some degree, so are managers making attempts to prevent those failures by assigning simpler projects to those teams.
 \item[Hypotheses] The authors list two hypotheses \cite{bird09}: 
@@
 \end{quote}
-\item[Future Work] The authors note that there haven't been any causal relationshisp established between development practices and effective distributed development.
+\item[Future Work] The authors note that there haven't been any causal relationships established between development practices and effective distributed development.
 They suggest studies to examine the effects of various development practices on distributed development.
+\item[Informative Visualizations] The visualizations on page 523 of the paper are particularly useful.
+Figure 2 shows a breakdown of where people working on a specific dll are working geographically to give an idea of the level of distribution Microsoft was dealing with.
+The other vissualization on the same page, a Venn diagram showing concentric circles of the percentages of binaries at each distribution level, is very useful in understanding how distributed the project was overall.
 \end{description}
@@
 \section*{Possible Improvements}
+This paper was incredibly well written and makes its argument in a fairly air tight manner.
+I think as it is, it would be difficult to improve upon it.
+That said, perhaps some data on outsourced projects within Microsoft for comparison or distributed projects within companies recently acquired by Microsoft would make that piece of their argument more solid, but could quickly turn into a book rather than an article.
+The project detailed was so specific and the organizations so specific that it would be difficult generalize to any other company.
+For example, the authors mention the fact that Microsoft sent a number of developers that had worked at Microsoft for over ten years, but were from the same cultural group to work with a distributed team in India.
+Not many companies would have either the staff or resources to do the same.
 
@@
 The authors also mentioned that this study examined software on the binary level (an aggregated level), which supports their claim that aggregation is very common in defect modeling research.
+This paper was not mentioned in paper two \cite{arisholm10}.
 

### 2015-09-24 hw/read/4/summary.tex
initialize paper four

--- 2015-09-08 hw/read/2/summary.tex
@@
 
-\title{Paper Two Summary}
+\title{Paper Four Summary}
 
@@
 
-Arisholm et al \cite{arisholm10} listed below.
+Vandecruys et al \cite{Vandecruys08} listed below.
 
@@
 \begin{description}
-\item [{Fault-proneness}] The number of defects detected in a software-component.
-A measurement of the likelihood of software or software component
-error. 
-\item [{Object-oriented~(OO)~code~measures}] Measurement of the structural
-properties of the source code. 
-\item [{Delta~measures}] Measurement of the amount of change (churn) in
-a file between two successive releases. 
-\item [{Process~measures}] Measures from a configuration management system.
-Includes developer experience, the number of developers that have
-edited a file, the number of faults in the previous releases, the
-number of line added, the number of lines removed. 
+\item [{Ant Colony Based Optimization}] 
 \end{description}
@@
 \begin{description}
-\item [{Motivational~statements}] The authors mentioned that most previous
-studies only examined the structure of the code when constructing
-fault-proneness prediction models. In the few studies that did not,
-they failed to systematically measure the cost-effectiveness of the
-models with factors with different data collection costs. Very few
-studies have looked at the methods and criteria for evaluating the
-models. Finally, it is very difficult to draw specific conclusions
-using confusion matrices since they do not provide any insight into
-determining the cost-effectiveness of the models under test.
-\item [{Motivational Statements}] The motivation was to provide a systematic
-methodology for comparing modeling techniques. The authors state that
-little to no effort was put forth to prior to this paper in that area.
-\item [{Patterns}] The authors provide an overview of a number of different
-techniques and different metric sets in an attempt to prove which
-provides the best results across comparison techniques. The results
-seem to show that the ROC curve combined with cost effectiveness comparisons
-provide a good deal of insight into the performance of techniques
-and matrices as compared to using the confusion matrix approach.
-\item [{Future~Work}] The authors used the default parameters for the
-statistical techniques they employed in the study. They have stated
-that they hope to tweak the parameters and observe the results to
-see if there are optimizations that can be made while at the same
-time preventing overfitting. The authors also stated they are going
-to work on a large-scale evaluation of the costs and benefits of various
-prediction models in the COS project.
-\item [{Informative Visualizations}] Figure four on page 12 of the paper
-provides a really interesting visualization of the distribution of
-cost efficiency of prediction models using Process and Object Oriented
-metrics. The figure provides two lines, one for OO and one for Process
-metrics, but they also provide clouds around those lines that demarcate
-the 25th and 75th percentiles. The authors use this figure to show
-the fact that the performance of OO metrics based models is poor compared
-with Process. The baseline for this study was a line such that $y=x$
-so as is shown in the figure, OO has very close to the baseline performance
-while OO outperforms the baseline by a significant margin. 
+\item [{Motivational~statements}]
 \end{description}
@@
 \section*{Possible Improvements}
-\begin{itemize}
-\item In the Introduction section, the authors reference a paper published
-in 1989 to cite a percentage of effort spent on testing. Is there
-a more recent paper the authors could have chosen to cite? If not,
-why quote a figure that is 26 years old and quite possibly outdated?
-\item While the way that the authors combined data in an attempt to consolidate
-it to a smaller number of tables was very clever, it produces tables
-that are very difficult to interpret. They have split the data into
-a standard set of stats (mean, median, Q1, Q3) on half of the table
-and then created a diagonal split on the other half of the table into
-two sets of data, one for effect size and the other for the Wilcoxon
-test data. It seems that they had so much data to report that it would
-have been impossible to report it in the space they had available
-without this type of table, but perhaps some further graphical representation
-would have been preferable with an appendix of the tables and data
-sets split out into more easily decipherable tables.
-\end{itemize}
 
@@
 
-Posnett et al \cite{posnett11} cited this paper as well as Menzies
-et al \cite{menzies10} as evidence that prediction models designed
-for the aggregated level have poor performance at the disaggregated
-level. But moreover the Posnett paper uses this paper as a methodological
-foundation for the way that they went about using the ROC curve and
-Cost Effectiveness analysis that they used in their study.
-
 \bibliographystyle{plain}
 \bibliography{references}
-{} \bibliographystyle{plain}
 \end{document}

### 2015-09-24 hw/read/4/summary.tex
added motivational statement

@@
 \begin{description}
-\item [{Motivational~statements}]
+\item [{Motivational~statements}] The motivation of this paper is to apply AntMiner+, a rule-based Ant Colony Optimization classification technique to public repositories and assess it's prediction and inference capabilities against other previously successful classification techniques in the domain of software quality.
 \end{description}

### 2015-09-24 hw/read/4/summary.tex
added ant colony optimization definition and motivational statement

@@
 \begin{description}
-\item [{Ant Colony Based Optimization}] 
+\item [{Ant Colony Optimization (ACO)}] A metaheuristic inspired by the ant behavior of determining shortest path by concentration of pheromone present on the path.
+Ants returning faster to the colony leave a greater concentration of pheromone by doubling over on their path which is used as an indicator of the shortest path for other ants.
+ACO's artificial ants iteratively and stochastically construct solutions and add pheromones to these solutions.
+The pheromone is defined as the number of ants recently choosing a solution.
+When a new artificial ant encounters a decision it is more likely to choose path with a greater concentration of pheromone.
+The concentration is adjusted based on the evaluation of the solution.
+An evaporation constant causes the pheromones to evaporate and lowers concentration for each path.
 \end{description}

### 2015-09-24 hw/read/4/summary.tex
Added two keywords to paper four's summary

@@
 An evaporation constant causes the pheromones to evaporate and lowers concentration for each path.
+\item [{Software mining}] The use of data mining to support and improve the development of software.
+The paper found three areas of interest covered by recent papers on this field: Fault prediction, the use of change histories to detect incomplete changes, and effort prediction.
+\item[{COCOMO II}] A well-known example of a structural model designed to optimize the allocation of resources for planning and developing software projects.
+The authors note that the constants in COCOMO II are determined from trial and error and the scaling factors and effort multiplicators are discrete, limiting the feasibility and accuracy of the model.
 \end{description}

### 2015-09-24 hw/code/5/MaxWalkSat.py
added bounds

@@ -20,6 +20,12 @@ def constraints(x1, x2, x3, x4, x5, x6):
   return True
 
 
+#returns bounds function that takes a random and returns a value within in the bounds
+def bounds(min, max):
+  def f(rand):
+    return ((max-min) * rand) + min
+  return f
+
 # This returns the normalization function
 # for one of the two observation functions (f1, f2)
 # b1 is the minimum, b2 is the maximum
@@ -39,6 +45,7 @@ def normalize(b1, b2):
 # energy value.  For this simplified environment
 # emax is sqrt(2).
 
+
 def energy(f1_norm, f2_norm):
   def e(x):
     s = osyczka2(x)
@@ -56,6 +63,13 @@ def energy(f1_norm, f2_norm):
     return dist_from_hell
   return e
 
+GLOBAL_BOUND_MAX = 100000
+x1bound = bounds(0 , GLOBAL_BOUND_MAX)
+x2bound = bounds(-GLOBAL_BOUND_MAX, 10)
+x3bound = bounds(1, GLOBAL_BOUND_MAX)
+x4bound = bounds(0, 6)
+x5bound = bounds(-GLOBAL_BOUND_MAX, 5)
+x6bound = bounds(0, 10)
 
 #TODO: adapt for oszyzcka2 constraints
 def base_runner():

### 2015-09-24 hw/code/5/MaxWalkSat.py
base runner working

@@ -3,20 +3,25 @@ import random, math, sys
 # Calculates f1 and f2 and then
 # returns the values in a tuple
 # f1,f2
-def osyczka2(x1, x2, x3, x4, x5, x6):
-  f1 = -(25*(x1-2)**2 + (x2 - 2)**2 + (x3 - 1)**2 * (x4-4)**2 + (x5 - 1)**2)
-  f2 = x1**2 + x2**2 + x3**2 + x4**2 + x5**2 + x6**2
+def osyczka2(x):
+  f1 = -(25*(x[0]-2)**2 + (x[1] - 2)**2 + (x[2] - 1)**2 * (x[3]-4)**2 + (x[4] - 1)**2)
+  f2 = x[0]**2 + x[1]**2 + x[2]**2 + x[3]**2 + x[4]**2 + x[5]**2
   return (f1, f2)
 
 #osyczka2 constraints: checks all costraints, returns true is all constraints met
 #new mutation should be done if this returns false
-def constraints(x1, x2, x3, x4, x5, x6):
+def constraints12(x1, x2):
   if(x1 + x2 - 2 < 0): return False
   if(6 - x1 - x2 < 0): return False
   if(2 - x2 + x1 < 0): return False
-  if(4 - (x3 - 3)**2 - x4 < 0): return False
-  if((x5 - 3)**3 + x6 - 4 < 0): return False
+  return True
 
+def constraints34(x3, x4):
+  if(4 - (x3 - 3)**2 - x4 < 0): return False
+  return True
+
+def constraints56(x5, x6):
+  if((x5 - 3)**3 + x6 - 4 < 0): return False
   return True
 
 
@@ -71,6 +76,31 @@ x4bound = bounds(0, 6)
 x5bound = bounds(-GLOBAL_BOUND_MAX, 5)
 x6bound = bounds(0, 10)
 
+def generateValidValues():
+  x1temp = x1bound(random.random())
+  x2temp = x2bound(random.random())
+  x3temp = x3bound(random.random())
+  x4temp = x4bound(random.random())
+  x5temp = x5bound(random.random())
+  x6temp = x6bound(random.random())
+
+  while(not constraints12(x1temp, x2temp)):
+    x1temp = x1bound(random.random())
+    x2temp = x2bound(random.random())
+  
+
+  while(not constraints34(x3temp, x4temp)):
+    x3temp = x3bound(random.random())
+    x4temp = x4bound(random.random())
+  
+
[…]

### 2015-09-24 notes/notes09222015.py
notes

@@ -65,7 +65,7 @@
 # keys sorts state 
 
 # Even though domain specific languages is general models, it's an exmaple of making python business user readable
-
+#elite sampling
 
 
 #python below here about 

### 2015-09-24 notes/notes09242015.py

@@ -1,0 +1,48 @@
+# Differential evolution -> better than maxwalksat and SA, 90s idea, this is where it's at, Code7
+
+# Compartmental models are visual ways to express first order linear equations, can tell if they will converge or diverge
+# Copy over the items in payload that weren't updated
+# Keep background knowledge of the constraints on all the payloads
+# step updates the payload
+# have is once before the model starts running and step is once for each step in the model
+# state is the background knowledge
+
+# Support Utilities:
+# dots sumbolize a repeat of the same values
+# zip runs every column as one row, pulls out each column for formatting
+# ditto is the dot printer
+# enumerate = zipWithIndex
+
+# Debugging Compartmental Models:
+# never underestimate the effort associated with commissioning a model
+# stay away from globals and have hierarchical modeling
+# team up with domain experts
+
+# Writing Compartmental Models:
+# feedback loop from verbal cues
+# Business users typically repeat a small number of cliches, submodules are useful(ex. for accounts receivable)
+# 2 papers about linguistic clues
+
+# Causal Model Refinement:
+# Different business experts fixate on different parts of the process
+# Can translate diagrams into models, pathway from scrolling on the whiteboard and then getting somethign that runs
+# Process of Classic Activism, forces that resist change and forces that favor change are affected by the same variables
+# UML is not business user friendly
+
+# Drop subgraphs in submodels to analyze them
+
+# Hans Gosling - Social theorist with WHO
+
+
+# When you write a model, you spend a good proportion of your time debugging your model because if something unexpected happends you need to ensure it's the result of a valid model
+# Should break models into submodels and verify microexpectations
+
+# Brooks effect/law, adding programmers to a project delays release but there are also circumstances where it doesn't make it quicker just more exppensive
+
+
+# Hofstadter, french poem translatation
+
+# One way to build a domain specific language is to look at what pepople use and talk to them. Define domain idioms.
+
+# @staticmethod is unique to class(1000 instances, 1 class)
+

### 2015-09-25 hw/code/5/MaxWalkSat.py
Added jump all around and sanity check

@@ -160,77 +160,65 @@ def base_runner():
 
   return (norm_f1, norm_f2)
 
-# def neighbor(x, temp):
-#   epsilon = temp * random.random()
-#   add = bool(random.getrandbits(1))
-#   if add:
-#     x += epsilon
-#   else:
-#     x -= epsilon
+def say(x):
+  sys.stdout.write(str(x)); sys.stdout.flush()
 
-#   if x < 0.0:
-#     x = x + 1.0
+def prob(old, new, k):
+  x = math.exp(((new - old) / k))
+  return x
 
-#   if x > 1.0:
-#     x = x - 1.0
-     
-#   return x
+global kmax
+global emax
+kmax = 1000.0
+emax = (2)**0.5
 
-# def say(x):
-#   sys.stdout.write(str(x)); sys.stdout.flush()
-
-# def prob(old, new, k):
-#   x = math.exp(((new - old) / k))
-#   return x
-
-# global kmax
-# global emax
-# kmax = 10000.0
-# emax = (2)**0.5
-
-# def sim_anneal(energy):
-#   s0 = 0.5
-#   s = s0
-#   e = energy(s)
-#   print "Initial energy", e
-#   sb = s
-#   eb = e
-#   k = 1.0
+def maxWalkSat(energy):
+  s0 = generateValidValues()
+  s = s0
+  e = energy(s)
+  print "Initial energy", e
+  sb = s
+  eb = e
+  k = 1.0
   
-#   say('(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
+  #say('(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
+ 
+  #shitty print function
+  say('K:' + str(k) + " vector: " + str(sb[0]) + " " + str(sb[1]) + " " + str(sb[2]) + " " + str(sb[3]) + " " + str(sb[4]) + " " + str(sb[5]))
 
-#   while k < kmax and e < emax:
-#     sn = neighbor(s, (kmax - k)/kmax)
-#     en = energy(sn)
+  while k < kmax and e < emax:
+    sn = generateValidValues()
+    en = energy(sn)
 
-#     # Is this a best overall?
-#     if en > eb:
-#       sb = sn
-#       eb = en
-#       say("!")
+    # Is this a best overall?
+    if en > eb:
+      sb = sn
+      eb = en
+      say("!")
 
-#     # Is this better than where we were last?
-#     if en > e:
-#       s = sn
[…]

### 2015-09-26 hw/code/5/MaxWalkSat.py
merged sashas code with mine and made changes until working correctly

@@ -24,20 +24,11 @@ def constraints56(x5, x6):
   if((x5 - 3)**3 + x6 - 4 < 0): return False
   return True
 
-def constraints_all(s):
-  x1 = s[0]
-  x2 = s[1]
-  x3 = s[2]
-  x4 = s[3]
-  x5 = s[4]
-  x6 = s[5]
-  if(x1 + x2 - 2 < 0): return False
-  if(6 - x1 - x2 < 0): return False
-  if(2 - x2 + x1 < 0): return False
-  if(4 - (x3 - 3)**2 - x4 < 0): return False
-  if((x5 - 3)**3 + x6 - 4 < 0): return False
-  return True
-
+#constraint stack, makes dealing with the step function easier
+constraintsStack = []
+constraintsStack.append(constraints12)
+constraintsStack.append(constraints34)
+constraintsStack.append(constraints56)
 
 #returns bounds function that takes a random and returns a value within in the bounds
 def bounds(min, max):
@@ -62,9 +53,7 @@ def normalize(b1, b2):
 # is at (1,1) in this graph.  We calculate distance
 # to hell from our x,y point and return it as our
 # energy value.  For this simplified environment
-# emax is sqrt(2).
-
-
+# emax is sqrt(2)
 def energy(f1_norm, f2_norm):
   def e(x):
     s = osyczka2(x)
@@ -78,7 +67,6 @@ def energy(f1_norm, f2_norm):
     # print 'f2 normalized is ' + str(y)
     dist_from_hell = ((1 - x)**2 + (1 - y)**2)**0.5
     # print 'dist from hell ' + str(dist_from_hell)
-
     return dist_from_hell
   return e
 
@@ -89,34 +77,43 @@ def energy(f1_norm, f2_norm):
 # 0 <= x4 <= 6
 # 1 <= x5 <= 5
 # 0 <= x6 <= 10
-x1bound = bounds(0, 10)
-x2bound = bounds(0, 10)
-x3bound = bounds(1, 5)
-x4bound = bounds(0, 6)
-x5bound = bounds(1, 5)
-x6bound = bounds(0, 10)
+
+#bound list, makes dealing with steps easier
+xbounds = []
+xbounds.append(bounds(0, 10))
+xbounds.append(bounds(0, 10))
+xbounds.append(bounds(1, 5))
+xbounds.append(bounds(0, 6))
+xbounds.append(bounds(1, 5))
+xbounds.append(bounds(0, 10))
+
[…]

### 2015-09-27 hw/read/4/summary.tex
Added a keyword and feature extractions to reading 5

@@
 The authors note that the constants in COCOMO II are determined from trial and error and the scaling factors and effort multiplicators are discrete, limiting the feasibility and accuracy of the model.
+\item[{Classification}] A type of data mining where a data point is assigned to a group according to some set of its characteristics.
+The authors used classification to assign software modules to either an "erroneous" or "correct" class depending on characteristics such as LOC (lines of code) metrics, cyclomatic complexity, and the number of unique operands.
 \end{description}
@@
 \item [{Motivational~statements}] The motivation of this paper is to apply AntMiner+, a rule-based Ant Colony Optimization classification technique to public repositories and assess it's prediction and inference capabilities against other previously successful classification techniques in the domain of software quality.
+\item[{Patterns}] Different types of preprocessing were applied on the data.
+First, the authors had to discretize all the input variables since AntMiner+ only accepts discrete variables.
+Second, they had to narrow the selection of which input variables to consider to the ones with the highest predictive power.
+Last, they oversampled the training observations that contained erroneous software modules in order to eliminate a bias toward correct software modules.
+\item[{Sampling procedures}] The authors note that in about half of the papers they summarized, datasets that are not publicly accessible were used.
+They recommend using public datasets as it allows other researchers to replicate the results and to better compare different data mining techniques.
+These are the reasons why, they state, that they have chosen the most commonly used state-of-the-art classification techniques and apply them to publicly available datasets, namely three from NASA: PC1, PC4, and KC1.
+\item[{Scripts}] The pseudocode of the AntMiner+ algorithm is provided.
+The algorithm builds a graph representing the state space (see Fig.
+3 in the paper), then simulates running ants between the Start and Stop vertices, constructing a rule along the way.
+Better rules will contain more pheromone along them as more ants traverse the same path.
+Due to some evaporation that occurs over time, there will eventually be a very high amount of pheromone on the best path and very low amounts on the other paths.
+Once this occurs, the rule corresponding to the path with the high amount of pheromone is added to the rule set, and the process continues until rules are discovered to account for all the data in the training set.
 \end{description}

### 2015-10-05 hw/read/4/summary.tex

@@
 \begin{document}
-
 \title{Paper Four Summary}
@@
 
-Vandecruys et al \cite{Vandecruys08} listed below.
+Vandecruys et al. \cite{Vandecruys08} listed below.
 
@@
 \section*{Possible Improvements}
+\begin{itemize}
+\item Table 6 \cite[p.
+835]{Vandecruys08} is rotated 90 degrees in order to fit on the page.
+On a computer screen, it is difficult to read without rotating the entire page 90 degrees, and then the page has to be rotated back to read the rest of the paper.
+Since the table is split into three sections for each of the three datasets, the large table could have been divided into tables for each dataset, which could have easily been placed vertically to fit on a page.
+\item The conclusion of the paper was very short, consisting of only about a quarter of a column.
+In this section, the authors reiterated their goals of reducing faults in software programs by helping software managers to better understand which modules might contain faults.
+They note that AntMiner+ will help to achieve these goals.
+But that is all they say.
+They did not explicitly state any plans or ideas for future work or threats to validity, which were present in previous papers we summarized.
+The authors should have fleshed out their conclusion a bit more to suggest some practical next steps.
+\end{itemize}
 
 \section*{Connection to Other Papers}
+This paper was cited by Arisholm et al.
+\cite{arisholm10} as part of a literature review.
+They cited this paper's analysis of various classification techniques and the results that there were no large differences in accuracy, sensitivity, or specificity.
+The paper uses these findings as well as similar findings in other papers to claim that, "the differences between modeling techniques are relatively small" \cite[p.
+4]{arisholm10}.
+The study also notes that most of the studies it cited (including this one) only looked at structural measures to predict fault proneness and not more expensive factors like process measures.
+Finally, the study examined the cost-effectiveness of various modeling techniques, while this one did not.
 

### 2015-10-15 hw/code/6/MaxWalkSat.py
models running MWS, imported SA but just getting started

@@ -37,9 +37,6 @@ def tweak(c, sn, m):
     # returning in a 1 based range on line 53
     # to make it simpler to get the id
     sn_temp[c - 1] = getattr(m.decs, id)(random.random())
-    # we try ten times to make this work, if we fail then
-    # we just leave sn alone and return it as it was
-    # count = 0
     while not m.check_con(sn, id):
       sn_temp[c - 1] = getattr(m.decs, id)(random.random())
       # count += 1
@@ -69,9 +66,9 @@ def run(m):
         print 'e was greater than e max'
         print 'e: ', e
         print 's: ', s
-        print 'constraint 1 ', m.check_con(s, 'x' + str(1))
-        print 'constraint 2 ', m.check_con(s, 'x' + str(3))
-        print 'constraint 3 ', m.check_con(s, 'x' + str(5))
+        # print 'constraint 1 ', m.check_con(s, 'x' + str(1))
+        # print 'constraint 2 ', m.check_con(s, 'x' + str(3))
+        # print 'constraint 3 ', m.check_con(s, 'x' + str(5))
         return s,e
       #pick the x to mutate
       num_decs = len(m.decs)

### 2015-10-15 hw/code/6/SimAnnealing.py

@@ -1,0 +1,70 @@
+import random, math, sys
+
+def neighbor(x, temp):
+  epsilon = temp * random.random()
+  add = bool(random.getrandbits(1))
+  if add:
+    x += epsilon
+  else:
+    x -= epsilon
+
+  # Clipping
+  if x < 0.0:
+    x = x + 1.0
+  if x > 1.0:
+    x = x - 1.0
+
+  return x
+
+def say(x):
+  sys.stdout.write(str(x)); sys.stdout.flush()
+
+def prob(old, new, k):
+  x = math.exp(((new - old) / k))
+  return x
+
+def sim_anneal(m):
+  kmax = 10000.0
+  emax = (2)**0.5
+
+  # Not sure why we start with 1/2, but whatever
+  s0 = 0.5
+  s = s0
+  e = m.energy(s)
+
+  print "Initial energy", e
+  sb = s
+  eb = e
+  k = 1.0
+
+  say('(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
+
+  while k < kmax and e < emax:
+    sn = neighbor(s, (kmax - k)/kmax)
+    en = m.energy(sn)
+
+    # Is this a best overall?
+    if en > eb:
+      sb = sn
+      eb = en
+      say("!")
+
+    # Is this better than where we were last?
+    if en > e:
+      s = sn
+      e = en
+      say("+")
+
+    elif prob(e, en, k / kmax) < random.random():
+      s = sn
+      e = en
+      say("?")
+
+    say(".")
+    k += 1.00
+
+    if k % 50 == 0:
+      say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(sb) + '\t')
+
+  print '\n \nbest solution ' + str(sb)
+  print 'energy of best solution ' + str(m.energy(sb))

### 2015-10-15 hw/code/6/model.py

@@ -42,6 +42,8 @@ class model(object):
   # is only involved in one set of constraints.
   # If that isn't true we need to make changes here.
   def check_con(self, vector, id):
+    if not self.constraints:
+      return True
     for c in self.constraints:
       # print c
       # print c.ids
@@ -57,7 +59,7 @@ class model(object):
     # we don't need to do anything
     # other than regen a new vector
     if self.constraints == None:
-      vector = self.gen_clean()
+      return self.gen_clean()
 
     if not vector:
       vector = self.gen_clean()
@@ -69,7 +71,7 @@ class model(object):
 
   def eval_objs(self, vector):
     eval_list = []
-    #print self.objs
+    # print self.objs
     for f in self.objs:
       # print f
       if(self.bound):

### 2015-10-15 hw/code/6/schaffer.py

@@ -1,0 +1,43 @@
+import collections, model, base, MaxWalkSat
+
+def bounds(min, max):
+  def f(rand):
+    return ((max-min) * rand) + min
+  return f
+
+def normalize(b1, b2):
+  def n(x):
+    return (x - b1) / (b2 - b1)
+  return n
+
+def schaffer():
+  def f1(*args):
+    args = args[0]
+    return args[0] * args[0]
+    return f1
+  def f2(*args):
+    args = args[0]
+    return (args[0] - 2)**2
+  return (f1, f2)
+
+
+payload = collections.namedtuple('payload', ['decs', 'objs', 'cons', 'bound', 'energy'])
+objectives = collections.namedtuple('objs', ['f1', 'f2'])
+objective = collections.namedtuple('obj', ['func', 'norm'])
+decs = collections.namedtuple('decs', ['x1'])
+constraint = collections.namedtuple('constraint', ['ids', 'state'])
+cons = None
+
+funcs = schaffer()
+obj1 = objective(funcs[0], normalize(0, 10000000000))
+obj2 = objective(funcs[1], normalize(0, 9999600004))
+objs = objectives(obj1, obj2)
+
+decs = decs(bounds(-10**(5),10**(5)))
+
+
+payload = payload(decs, objs, cons, True, 'from_hell')
+
+m = model.model(payload)
+
+fin = MaxWalkSat.run(m)

### 2015-10-15 hw/code/6/schaffer_base.py

@@ -1,4 +1,4 @@
-import collections, model, base, math
+import collections, model, base, random
 
 def bounds(min, max):
   def f(rand):
@@ -10,37 +10,28 @@ def normalize(b1, b2):
     return (x - b1) / (b2 - b1)
   return n
 
-def kursawe(a, b):
-  a_param = a
-  b_param = b
+def schaffer():
   def f1(*args):
     args = args[0]
-    sum = 0
-    sum += -10 * math.exp(-0.2*math.sqrt(args[0]**2 + args[1]**2))
-    sum += -10 * math.exp(-0.2*math.sqrt(args[1]**2 + args[2]**2))
-    return sum
+    return args[0] * args[0]
     return f1
   def f2(*args):
     args = args[0]
-    sum = 0
-    sum += abs(args[0])**a_param + 5 * math.sin(args[0])**b_param
-    sum += abs(args[1])**a_param + 5 * math.sin(args[1])**b_param
-    sum += abs(args[2])**a_param + 5 * math.sin(args[2])**b_param
-    return sum
+    return (args[0] - 2)**2
   return (f1, f2)
 
 
 payload = collections.namedtuple('payload', ['decs', 'objs', 'cons', 'bound', 'energy'])
 objectives = collections.namedtuple('objs', ['f1', 'f2'])
 objective = collections.namedtuple('obj', ['func', 'norm'])
-decs = collections.namedtuple('decs', ['x1', 'x2', 'x3'])
+decs = collections.namedtuple('decs', ['x1'])
 constraint = collections.namedtuple('constraint', ['ids', 'state'])
 cons = None
 
-funcs = kursawe(1,1)
+funcs = schaffer()
 objs = objectives(funcs[0], funcs[1])
 
-decs = decs(bounds(-5,5), bounds(-5,5), bounds(-5,5))
+decs = decs(bounds(-10**(5),10**(5)))
 
 payload = payload(decs, objs, cons, False, 'from_hell')
 

### 2015-10-15 hw/code/6/test.py

@@ -1,94 +1,0 @@
-import collections, model
-
-def bounds(min, max):
-  def f(rand):
-    return ((max-min) * rand) + min
-  return f
-
-def normalize(b1, b2):
-  def n(x):
-    return (x - b1) / (b2 - b1)
-  return n
-
-def constraints():
-  def c1(*args):
-    args = args[0]
-    if(args[0] + args[1] - 2 < 0): return False
-    if(6 - args[0] - args[1] < 0): return False
-    if(2 - args[1] + args[0] < 0): return False
-    return True
-  def c2(*args):
-    args = args[0]
-    if(4 - (args[2] - 3)**2 - args[3] < 0): return False
-    return True
-  def c3(*args):
-    args = args[0]
-    if((args[4] - 3)**3 + args[5] - 4 < 0): return False
-    return True
-  return (c1,c2,c3)
-
-def osyczka2():
-  def f1(*args):
-    args = args[0]
-    return -(25*(args[0]-2)**2 + (args[1] - 2)**2 + (args[2] - 1)**2 * (args[3]-4)**2 + (args[4] - 1)**2)
-  def f2(*args):
-    args = args[0]
-    return args[0]**2 + args[1]**2 + args[2]**2 + args[3]**2 + args[4]**2 + args[5]**2
-  return (f1, f2)
-
-
-payload = collections.namedtuple('payload', ['decs', 'objs', 'cons', 'bound'])
-objectives = collections.namedtuple('objs', ['f1', 'f2'])
-objective = collections.namedtuple('obj', ['func', 'norm'])
-
-decs = collections.namedtuple('decs', ['x1', 'x2', 'x3', 'x4', 'x5', 'x6'])
-
-constraint = collections.namedtuple('constraint', ['ids', 'state'])
-cons = collections.namedtuple('cons', ['c1', 'c2', 'c3'])
-
-funcs = osyczka2()
-obj1 = objective(funcs[0], normalize(-608.378316019, -0.423436047808))
-obj2 = objective(funcs[1], normalize(26.1019387811, 175.967589423))
-objs = objectives(obj1, obj2)
-
-decs = decs(bounds(0,10), bounds(0,10), bounds(1,5), bounds(0,6), bounds(1,5), bounds(0,10))
-
-funcs = constraints()
-c1 = constraint(('x1','x2'), funcs[0])
[…]

### 2015-10-15 hw/read/5/summary.tex
Started Reading 5 summary

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}
\title{Paper Five Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Nagappan et al. \cite{Nagappan} listed below.

\section*{Important Keywords}
\begin{description}
\item [{Organizational metrics}] Metrics designed to give a balanced view of organizational complexity with respect to software development. The authors argue that these metrics, as a measure of organizational structure, greatly affect product quality.
\item[{Failure-proneness}] The probability that a particular piece of software will fail in production. The authors hope to reduce this by incorporating organizational metrics into models.
\end{description}

\section*{Feature Extraction}
\begin{description}
\item[{Future Work}] The authors hope to replicate the study with other Microsoft projects as well as organizations outside of Microsoft. They have mentioned that they are already begun collaborating with the Fraunhofer research institute (pg. 10) for this purpose. The authors also hope to research open source teams and their "virtual organizations", global software development, and even the social and cognitive aspects of the engineers themselves.
\end{description}

\section*{Possible Improvements}
\begin{itemize}
\item The phrasing in particular sections is grammatically incorrect. Here are a couple examples: "The deeper in the tree is the ownership the more focused the activities, communication, and responsibility" (pg. 4) and "The lower level is the ownership the better is the quality" (pg. 5). More editing should have been done to fix these errors.
\end{itemize}

\section*{Connection to Other Papers}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-10-15 hw/read/5/summary.tex
added three features and one keyword to paper 5

@@
 \item[{Failure-proneness}] The probability that a particular piece of software will fail in production. The authors hope to reduce this by incorporating organizational metrics into models.
+\item[{Software Metrics}]  The authors define them as things like code churn, code complexity, code coverage, and code dependencies.  These metrics have been used to determine fault proneness.
 \end{description}
@@
 \begin{description}
+\item[{Motivational Statements}]  The authors perspective is that software metrics have been used to a great degree to predict fault proneness in software, but that organizational metrics have not been used to try to predict failure proneness.
+Their main motivation is determining whether organizational metrics have a comparable efficacy in predicting failure proneness and also whether it is possible to accurately define and measure organizational metrics.
+
 \item[{Future Work}] The authors hope to replicate the study with other Microsoft projects as well as organizations outside of Microsoft.
@@
 The authors also hope to research open source teams and their "virtual organizations", global software development, and even the social and cognitive aspects of the engineers themselves.
+
+\item[{Baseline Results}]  The authors present strong baseline results when compared with software metrics in the area of fault predictions.
+The main comparison metrics used in the paper are precision and recall.
+The authors found that models using organizational metrics (specifically organizational structure) outperformed all software metric based prediction models.
+The closest competitor for precision was code coverage at $83.8\%$ vs organizational structure at $86.2\%$, while for recall the closest competitor was code churn at $79.9\%$ vs organizational structure at $84.0\%$.
+
+\item[{Statistical Tests}]  The authors use Spearman's rank correlation, which is an assessment of how correlated two specific variables are.
+They wanted to prove that the predicted faults and the actual faults of Windows Vista were highly correlated to show the sensitivity of their method.
+They found, as shown in Figure 4 in the paper that there was a statistically significant high correlation between predicted and actual failures with $99\%$ confidence.
+
 \end{description}

### 2015-10-18 hw/code/6/model.py
working setup with output

@@ -4,6 +4,9 @@ class model(object):
     self.payload = payload(decs, cons, objs, norm_objs, wrap, name)
     # print self.payload.decs
 
+  def get_bound(self, id):
+    return self.payload.decs[id]
+
   def get_name(self):
     return self.payload.name
 

### 2015-10-18 hw/code/6/models.py

@@ -61,6 +61,7 @@ obs_list = (f0, (-19.8575351929, -4.98880272393)), (f1, (-10.587243916, 29.43482
 
 kursawe = model.model(decs_list, constraint_list, obs_list, True, True, "Kursawe")
 
+
 model_list = [osyczka, schaffer, kursawe]
 for m in model_list:
   for optimizer in [sa,mws]:

### 2015-10-18 hw/code/6/sa.py

@@ -1,7 +1,31 @@
 import random, math, sys
 
-def neighbor(m, id, vect, temp):
-  epsilon = temp * random.random()
+def neighbor(m, id, s, temp):
+  vect = list(s)
+  bound = m.get_bound(id)
+  decay = math.exp(-temp)
+  # temp is decreasing so the possibility
+  # of a completely random position also is
+  # decreasing.  If we miss this then we calculate
+  # some epsilon based on the magnitude of the
+  # difference between the max and min for the dec
+  # and then add or subtract it
+  if( random.random() < decay):
+    # print 'vect id before ', vect[id]
+    vect[id] = random.uniform(*bound)
+    # print 'vect id after ', vect[id]
+    # print 'm.check_con ', m.check_con(vect, id)
+    if m.check_con(vect, id):
+      return vect
+    else:
+      vect = list(s)
+  mag = bound[1] - bound[0]
+  # print 'bound', bound
+  # print 'mag', mag
+  # print 'temp', temp
+  epsilon = decay * abs(mag)
+  # print 'epsilon', epsilon
+
   add = bool(random.getrandbits(1))
   if add:
     m.add_epsilon(id, vect, epsilon)
@@ -33,11 +57,13 @@ def from_hell(m, vect):
   dist_from_hell = ((1 - resp[0])**2 + (1 - resp[1])**2)**0.5
   return dist_from_hell / (2**(0.5))
 
-def run(m, e, retries, kmax):
-  print "RUN DATA: "
+def run(m, e, retries, kmax, goal = 0.01, pat = 10):
+  print "\nRUN DATA "
+  print "-------------------------"
   print "Model: ", m.get_name()
   print "Optimizer: Simulated Annealing"
-
+  print 'Goal epsilon ', goal
+  emax = 1
   if e == 'from_hell':
     energy = from_hell
   else:
@@ -50,28 +76,47 @@ def run(m, e, retries, kmax):
     e = energy(m, s)
     sb = s
     eb = e
+    eblast = e
     k = 1.0
+    patience = kmax/pat
     say("\n" + '(K:' + str(k) + ', SB:' + ''.join(["({0:.3f}) ".format(val) for val in sb]) + ', EB:(' + str(eb) + ')\t')
-    while k < kmax and e < 1:
+    while k < kmax and e < emax:
+      if emax - eb < goal:
+        print '\n\nQuitting early, close enough.'
+        print 'SB: ', sb
+        print 'EB: ', eb
+        print 'K: ', k
+        return
[…]

### 2015-10-18 hw/code/6/MWS.py
MWS finished and all models run

@@ -1,44 +1,85 @@
 from Models import *
 from random import *
+import sys
 
 def say(x):
  	sys.stdout.write(str(x)); sys.stdout.flush()
 
 
+
+
 def MWS(model):
-	max_changes = 100
+	max_changes = 1000
 	max_retries = 100
 	emin = 0
 	s = model.retry()
 
-	model.initiateObjectiveMinMax(s)
-	[model.updateObjectiveMaxMin(model.retry()) for i in range(100)] #prime the maxs and mins with second values, avoids divide by 0
+	model.initializeObjectiveMaxMin(s)
+	[model.updateObjectiveMaxMin(model.retry()) for i in range(100)] #prime the maxs and mins with values, avoids divide by 0
 
-	e = energy(s)
-	sb = list[s]
-  	sbo = list[s]
+	e = model.energy(s)
+	sb = list(s)
+  	sbo = list(s)
   	eb = e
   	ebo = e
-  	sn = list[sb]
+  	sn = list(sb)
 
   	for i in range(max_retries):
   		print '\nT:', i
   		for j in range(max_changes):
   			if e <= emin:
-        		return s,e
-        	c = random.randint(1, model.numOfVars + 1)
-        	if(random.random() >= 0.5):
-        		sn = model.singleRetry(s, c)
-      		else:
-      			#change to sn later
-        		for i in range(1, 10):
-					vector[index] = (model.bounds[i][1] - model.bounds[i][0]) * (i/10.0)
-						if(model.checkConstraints(vector)):
-							if(model.updateObjectiveMaxMin(vector))	
-								e = energy(s)	#update all energies if new normal
-								eb = energy(sb)
-								ebo = energy(sbo)
-							if(model.energy(vector) < e):
-								s = list[vector]
-								e = energy(s)
+  				sbo = list(s)
+  				ebo = e
+  				break
+  			c = randint(1, model.numOfVars)
+  			if(random() >= 0.5):
+  				sn = model.singleRetry(s, c)
+  			else:
+  				tempS = list(sn)
+  				tempE = model.energy(sn)
+  				for index in range(1, 10):
+  					tempS[c] = (model.bounds[c][1] - model.bounds[c][0]) * (index/10.0)
+  					if(model.checkConstraints(tempS)):
+  						if(model.updateObjectiveMaxMin(tempS)):
+  							e = model.energy(s)	#update all energies if new normal
[…]

### 2015-10-18 hw/code/6/model.py

@@ -69,7 +69,11 @@ class Model(object):
 		else:
 			return False
 
-	def checkConstraints(self, vector): reduce(lambda a, b: True & a & b, [f(vector) for f in self.constraints])
+	def checkConstraints(self, vector): 
+		if(len(self.constraints) > 0):
+			return reduce(lambda a, b: True & a & b, [f(vector) for f in self.constraints])
+		else:
+			return True
 
 
 	def energy(self,v):

### 2015-10-18 hw/code/6/test.py

@@ -1,4 +1,7 @@
 from Models import *
 from SA import *
+from MWS import *
 
-SA(Kursawe)
+for m in [Schaffer, Osyczka2, Kursawe]:
+	for o in [SA, MWS]:
+		o(m)

### 2015-10-18 hw/code/6/Models.py
Added Kursawe parameters

@@ -23,7 +23,7 @@ Schaffer = (Model(1)
 			)
 
 
-Ka = 2	#exponent values in kursawe
+Ka = 0.8	#exponent values in kursawe
 Kb = 3
 Kn = 3	#n values for kursawe, default to 3
 Kursawe = (Model(Kn)

### 2015-10-18 hw/read/5/summary.tex
Added conway's law
Conway's law
Connection to other papers

@@
 \item[{Software Metrics}]  The authors define them as things like code churn, code complexity, code coverage, and code dependencies.  These metrics have been used to determine fault proneness.
+\item[{Conway's Law}] Organizations that design systems are constrained to produce the systems which are copies of the communication structures of these organizations.
+
 \end{description}
@@
 
+In \cite{bird09}, this paper was referenced by the authors as previous research.
+The organizational metrics described in this paper were used as a set of features in \cite{bird09}.
+It was also used in that paper to reinforce the conclusion that organizationally distributed development affects the number of post-release defects.
+
 \bibliographystyle{plain}

### 2015-10-20 hw/code/6/MWS.py
Added Matt's suggestion

@@ -3,82 +3,83 @@ from random import *
 import sys
 
 def say(x):
- 	sys.stdout.write(str(x)); sys.stdout.flush()
-
-
-
+  sys.stdout.write(str(x)); sys.stdout.flush()
 
 def MWS(model):
-	max_changes = 1000
-	max_retries = 100
-	emin = 0
-	s = model.retry()
+  max_changes = 1000
+  max_retries = 100
+  emin = 0
+  s = model.retry()
+  model.initializeObjectiveMaxMin(s)
+	# prime the maxs and mins with values, avoids divide by 0
+  for i in xrange(1000):
+    model.updateObjectiveMaxMin(model.retry())
+  
+  e = model.energy(s)
+  sb = list(s)
+  sbo = list(s)
+  eb = e
+  ebo = e
+  sn = list(sb)
 
-	model.initializeObjectiveMaxMin(s)
-	[model.updateObjectiveMaxMin(model.retry()) for i in range(100)] #prime the maxs and mins with values, avoids divide by 0
+  for i in range(max_retries):
+    print '\nT:', i
+    for j in range(max_changes):
+      if e <= emin:
+        sbo = list(s)
+        ebo = e
+        break
+      c = randint(0, model.numOfVars - 1)
 
-	e = model.energy(s)
-	sb = list(s)
-  	sbo = list(s)
-  	eb = e
-  	ebo = e
-  	sn = list(sb)
+      if(random() >= 0.5):
+        sn = model.mutate(s, c)
+        if(model.updateObjectiveMaxMin(sn)):
+          e = model.energy(s)  # update all energies if new normal
+          eb = model.energy(sb)
+          ebo = model.energy(sbo)
+      else:
+				tempS = list(sn)
+				tempE = model.energy(sn)
+				for index in range(1, 10):
+					tempS[c] = (model.bounds[c][1] - model.bounds[c][0]) * (index / 10.0)
+					if(model.checkConstraints(tempS)):
+						if(model.updateObjectiveMaxMin(tempS)):
+							e = model.energy(s)  # update all energies if new normal
+							eb = model.energy(sb)
+							ebo = model.energy(sbo)
+							en = model.energy(sn)
+							tempE = model.energy(tempS)
+						if(model.energy(tempS) < tempE):
+							sn = list(tempS)
+							tempE = model.energy(tempS)
+      en = model.energy(sn)
+      if en < eb:
+				sb = list(sn)
+				eb = en
[…]

### 2015-10-20 hw/code/6/Models.py

@@ -2,24 +2,24 @@ from model import *
 import math
 
 Osyczka2 = (Model(6)
-				.addBound([1,2], 0, 10)		#usage: list of decision indices, min, max
-				.addBound([3,5], 1, 5)
-				.addBound([4], 0, 6)
-				.addBound([6], 0, 10)
-				.addConstraint([1,2], lambda x: (x[1] + x[2] - 2) >= 0)	#usage: list of decision indices, function
-				.addConstraint([1,2], lambda x: (6 - x[1] - x[2]) >= 0)
-				.addConstraint([1,2], lambda x: (2 + x[1] - x[2]) >= 0)
-				.addConstraint([1,2], lambda x: (2 - x[1] + 3 * x[2]) >= 0)
-				.addConstraint([3,4], lambda x: (4 - (x[3] - 3)**2 - x[4]) >= 0)
-				.addConstraint([5,6], lambda x: ((x[5] - 3)**3 + x[6] - 4) >= 0)
-				.addObjective(lambda x: -(25 * (x[1] - 2)**2 + (x[2] - 2)**2) + (x[3] - 1)**2 * (x[4] - 4)**2 + (x[5] - 1)**2)
-				.addObjective(lambda x: x[1]**2 + x[2]**2 + x[3]**2 + x[4]**2 + x[5]**2 + x[6]**2)
+				.addBound([0,1], 0, 10)		#usage: list of decision indices, min, max
+				.addBound([2,4], 1, 5)
+				.addBound([3], 0, 6)
+				.addBound([5], 0, 10)
+				.addConstraint([0,1], lambda x: (x[0] + x[1] - 2) >= 0)	#usage: list of decision indices, function
+				.addConstraint([0,1], lambda x: (6 - x[0] - x[1]) >= 0)
+				.addConstraint([0,1], lambda x: (2 + x[0] - x[1]) >= 0)
+				.addConstraint([0,1], lambda x: (2 - x[0] + 3 * x[1]) >= 0)
+				.addConstraint([2,3], lambda x: (4 - (x[2] - 3)**2 - x[3]) >= 0)
+				.addConstraint([4,5], lambda x: ((x[4] - 3)**3 + x[5] - 4) >= 0)
+				.addObjective(lambda x: -(25 * (x[0] - 2)**2 + (x[1] - 2)**2) + (x[2] - 1)**2 * (x[3] - 4)**2 + (x[4] - 1)**2)
[…]

### 2015-10-20 hw/code/6/SA.py

@@ -20,16 +20,18 @@ def SA(model):
 	
 	model.initializeObjectiveMaxMin(s)
 
-	[model.updateObjectiveMaxMin(model.retry()) for i in range(100)] #prime the maxs and mins with second values, avoids divide by 0
+	for i in xrange(1000):
+		model.updateObjectiveMaxMin(model.retry())	 #prime the maxs and mins with second values, avoids divide by 0
 
 	e = model.energy(s)
 	eb = e
-
-	def prob(old, new, t): return(math.exp(((old - new) / t)))
+	def prob(old, new, t): 
+		return(math.exp(((old - new) / t)))
+		
 		
 	def neighbor(vector, t):
 		
-		for i in range(1, len(vector)):
+		for i in range(0, len(vector)):
 			epsilon = t * random()
 			if bool(getrandbits(1)): 		#not sure if we should random on each value
 				vector[i] += epsilon		#or the whole vector
@@ -37,7 +39,7 @@ def SA(model):
 				vector[i] -= epsilon
 
 		vector = model.wrap(vector)			#wrap
-		for i in range(1, len(vector)):		#check all constraints for each vector
+		for i in range(0, len(vector)):		#check all constraints for each vector
 			vector = model.singleRetry(vector, i)	#will change value if constraints aren't met
 											#could implement this differently
 		return(vector)
@@ -45,6 +47,7 @@ def SA(model):
 	say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(eb) + '\t')
 	while((k < kmax) & (e > emin)):
 		sn = neighbor(s, (kmax - k)/kmax)
+		#sn = model.mutate(s, 1)
 		
 		if(model.updateObjectiveMaxMin(sn)):	#check if new objective bounds
 			e = model.energy(s)						#adjust accordingly 
@@ -54,25 +57,23 @@ def SA(model):
 
 		if(en < eb):
 			say( "!")
-			sb = sn
+			sb = list(sn)
 			eb = en
 
 		if((en < e)):
 			say("+")
-			s = sn
+			s = list(sn)
 			e = en
-
-		if(prob(e, en, (kmax - k)/kmax) > random()):
+		elif(prob(e, en, (kmax - k)/kmax) > random()):
 			say("?")
-			s = sn
+			s = list(sn)
 			e = en
 
 		say(".")
 		k += 1.00
[…]

### 2015-10-20 hw/code/6/model.py

@@ -2,80 +2,86 @@ from random import *
 
 class Model(object):
 
-	def __init__(self, x):
-		self.numOfVars = x
-		self.constraints = []	#list of constraints
-		self.constraintsTrack = {}	#dict mapping decision index to constraint index in self.constraints
-		[self.constraintsTrack.update({i:[]}) for i in xrange(x + 1)]	#initialising constraint tracker
-		self.bounds = {}	#dict of bounds in the form of {index:[min, max]}
-		self.objectives = []	#list of objectives
+	def __init__(s, x):
+		s.numOfVars = x
+		s.constraints = []	#list of constraints
+		s.constraintsTrack = {}	#dict mapping decision index to constraint index in s.constraints
+		[s.constraintsTrack.update({i:[]}) for i in xrange(x + 1)]	#initialising constraint tracker
+		s.bounds = {}	#dict of bounds in the form of {index:[min, max]}
+		s.objectives = []	#list of objectives
 
-	def addConstraint(self, indices, f):		#adds constraints
-		constraintLocation = len(self.constraints)
-		self.constraints.append(f)
-		[self.constraintsTrack[i].append(constraintLocation) for i in indices]
-		return self
+	def addConstraint(s, indices, f):		#adds constraints
+		constraintLocation = len(s.constraints)
+		s.constraints.append(f)
+		[s.constraintsTrack[i].append(constraintLocation) for i in indices]
+		return s
 
-	def addBound(self, indices, min, max): 	#adds bounds
-		[self.bounds.update({x: [min,max]}) for x in indices]
-		return self
+	def addBound(s, indices, min, max): 	#adds bounds
+		[s.bounds.update({x: [min,max]}) for x in indices]
+		return s
 
-	def addObjective(self, f):	#adds objective 
-		self.objectives.append(f)
-		return self
+	def addObjective(s, f):	#adds objective 
+		s.objectives.append(f)
+		return s
 
-	def boundy(self, index):	# generates new single random decision within bounds
-		return (self.bounds[index][1] - self.bounds[index][0]) * random() + self.bounds[index][0]
+	def boundy(s, index):	# generates new single random decision within bounds
+		return (s.bounds[index][1] - s.bounds[index][0]) * random() + s.bounds[index][0]
 
-	def retry(self, *args):	#generates new random vector
[…]

### 2015-10-20 hw/code/6/test.py

@@ -5,3 +5,4 @@ from MWS import *
 for m in [Schaffer, Osyczka2, Kursawe]:
 	for o in [SA, MWS]:
 		o(m)
+

### 2015-10-20 hw/read/5/summary.tex
Added two more improvements

@@
 More editing should have been done to fix these errors.
+\item The authors don't address how the size of a binary affects the probability measure of software defects.
+It can be logically deduced that larger binaries inherently have a greater number of defects.
+\item The authors address the validity of their features using step-wise regression and PCA but it would also be beneficial if the authors presented this data and gave a ranking of the affect of the features on predicting variance.
 \end{itemize}

### 2015-10-20 hw/code/6/model.py
Delete commented out transpose

@@ -47,11 +47,6 @@ class Model(object):
 		vector = s.singleRetry(vector, index)
 		return(vector)
 
-	# def transpose(s, vector): #transposes vector so first index is 1 instead of 0
-	# 	temp = range(1)
-	# 	temp.extend(vector)
-	# 	return temp
-
 	def wrap(s, vector):	#wrap all values in vector
 		return [(vector[i] % (s.bounds[i][1] - s.bounds[i][0])) + s.bounds[i][0] for i in range(0, len(vector))]
 	

### 2015-10-20 hw/code/6/model.py
Changed zombie lists

@@ -6,18 +6,21 @@ class Model(object):
 		s.numOfVars = x
 		s.constraints = []	#list of constraints
 		s.constraintsTrack = {}	#dict mapping decision index to constraint index in s.constraints
-		[s.constraintsTrack.update({i:[]}) for i in xrange(x + 1)]	#initialising constraint tracker
+		for i in xrange(x):
+			s.constraintsTrack.update({i:[]})	#initialising constraint tracker
 		s.bounds = {}	#dict of bounds in the form of {index:[min, max]}
 		s.objectives = []	#list of objectives
 
 	def addConstraint(s, indices, f):		#adds constraints
 		constraintLocation = len(s.constraints)
 		s.constraints.append(f)
-		[s.constraintsTrack[i].append(constraintLocation) for i in indices]
+		for i in indices:
+			s.constraintsTrack[i].append(constraintLocation)
 		return s
 
 	def addBound(s, indices, min, max): 	#adds bounds
-		[s.bounds.update({x: [min,max]}) for x in indices]
+		for x in indices:
+			s.bounds.update({x: [min,max]})
 		return s
 
 	def addObjective(s, f):	#adds objective 

### 2015-10-20 hw/code/6/MWS.py
Remove zombie lists & apply autoformatter

@@ -2,85 +2,86 @@ from Models import *
 from random import *
 import sys
 
+
 def say(x):
-  sys.stdout.write(str(x)); sys.stdout.flush()
+    sys.stdout.write(str(x))
+    sys.stdout.flush()
+
 
 def MWS(model):
-  max_changes = 1000
-  max_retries = 100
-  emin = 0
-  s = model.retry()
-  model.initializeObjectiveMaxMin(s)
-	# prime the maxs and mins with values, avoids divide by 0
-  for i in xrange(1000):
-    model.updateObjectiveMaxMin(model.retry())
-  
-  e = model.energy(s)
-  sb = list(s)
-  sbo = list(s)
-  eb = e
-  ebo = e
-  sn = list(sb)
-
-  for i in range(max_retries):
-    print '\nT:', i
-    for j in range(max_changes):
-      if e <= emin:
-        sbo = list(s)
-        ebo = e
-        break
-      c = randint(0, model.numOfVars - 1)
-
-      if(random() >= 0.5):
-        sn = model.mutate(s, c)
-        if(model.updateObjectiveMaxMin(sn)):
-          e = model.energy(s)  # update all energies if new normal
-          eb = model.energy(sb)
-          ebo = model.energy(sbo)
-      else:
-				tempS = list(sn)
-				tempE = model.energy(sn)
-				for index in range(1, 10):
-					tempS[c] = (model.bounds[c][1] - model.bounds[c][0]) * (index / 10.0)
-					if(model.checkConstraints(tempS)):
-						if(model.updateObjectiveMaxMin(tempS)):
-							e = model.energy(s)  # update all energies if new normal
-							eb = model.energy(sb)
-							ebo = model.energy(sbo)
-							en = model.energy(sn)
-							tempE = model.energy(tempS)
-						if(model.energy(tempS) < tempE):
-							sn = list(tempS)
-							tempE = model.energy(tempS)
-      en = model.energy(sn)
-      if en < eb:
-				sb = list(sn)
-				eb = en
-				say("!")
-      if en < e:
-	  		say("+")
-      else:
-	  		say(".")
-      s = list(sn)
-      e = en
-    print '\nEB:', eb
-    print 'SB:', sb
-	    # First check if the sb for that set of changes was better
-	    # Than any of our other retries
-    if(eb < ebo):
-  		sbo = list(sb)
-  		ebo = eb
-  	# Then retry with a brand new set of values
+    max_changes = 1000
[…]

### 2015-10-20 hw/code/6/Models.py

@@ -2,36 +2,38 @@ from model import *
 import math
 
 Osyczka2 = (Model(6)
-				.addBound([0,1], 0, 10)		#usage: list of decision indices, min, max
-				.addBound([2,4], 1, 5)
-				.addBound([3], 0, 6)
-				.addBound([5], 0, 10)
-				.addConstraint([0,1], lambda x: (x[0] + x[1] - 2) >= 0)	#usage: list of decision indices, function
-				.addConstraint([0,1], lambda x: (6 - x[0] - x[1]) >= 0)
-				.addConstraint([0,1], lambda x: (2 + x[0] - x[1]) >= 0)
-				.addConstraint([0,1], lambda x: (2 - x[0] + 3 * x[1]) >= 0)
-				.addConstraint([2,3], lambda x: (4 - (x[2] - 3)**2 - x[3]) >= 0)
-				.addConstraint([4,5], lambda x: ((x[4] - 3)**3 + x[5] - 4) >= 0)
-				.addObjective(lambda x: -(25 * (x[0] - 2)**2 + (x[1] - 2)**2) + (x[2] - 1)**2 * (x[3] - 4)**2 + (x[4] - 1)**2)
-				.addObjective(lambda x: x[0]**2 + x[1]**2 + x[2]**2 + x[3]**2 + x[4]**2 + x[5]**2)
-			)
+            # usage: list of decision indices, min, max
+            .addBound([0, 1], 0, 10)
+            .addBound([2, 4], 1, 5)
+            .addBound([3], 0, 6)
+            .addBound([5], 0, 10)
+            # usage: list of decision indices, function
+            .addConstraint([0, 1], lambda x: (x[0] + x[1] - 2) >= 0)
+            .addConstraint([0, 1], lambda x: (6 - x[0] - x[1]) >= 0)
+            .addConstraint([0, 1], lambda x: (2 + x[0] - x[1]) >= 0)
+            .addConstraint([0, 1], lambda x: (2 - x[0] + 3 * x[1]) >= 0)
+            .addConstraint([2, 3], lambda x: (4 - (x[2] - 3)**2 - x[3]) >= 0)
+            .addConstraint([4, 5], lambda x: ((x[4] - 3)**3 + x[5] - 4) >= 0)
+            .addObjective(lambda x: -(25 * (x[0] - 2)**2 + (x[1] - 2)**2) + (x[2] - 1)**2 * (x[3] - 4)**2 + (x[4] - 1)**2)
[…]

### 2015-10-20 hw/code/6/SA.py

@@ -1,4 +1,4 @@
-#Notes for var names:
+# Notes for var names:
 # f = some anonymous function
 # x = some value
 # i = some index
@@ -6,80 +6,78 @@ from random import *
 import math
 import sys
 
+
 def say(x):
-  sys.stdout.write(str(x)); sys.stdout.flush()
+    sys.stdout.write(str(x))
+    sys.stdout.flush()
+
 
 def SA(model):
 
-	emin = 0
-	kmax = 10000.0
-	k = 1
+    emin = 0
+    kmax = 10000.0
+    k = 1
 
-	s = model.retry()
-	sb = s
-	
-	model.initializeObjectiveMaxMin(s)
+    s = model.retry()
+    sb = s
 
-	for i in xrange(1000):
-		model.updateObjectiveMaxMin(model.retry())	 #prime the maxs and mins with second values, avoids divide by 0
+    model.initializeObjectiveMaxMin(s)
 
-	e = model.energy(s)
-	eb = e
-	def prob(old, new, t): 
-		return(math.exp(((old - new) / t)))
-		
-		
-	def neighbor(vector, t):
-		
-		for i in range(0, len(vector)):
-			epsilon = t * random()
-			if bool(getrandbits(1)): 		#not sure if we should random on each value
-				vector[i] += epsilon		#or the whole vector
-			else:
-				vector[i] -= epsilon
+    for i in xrange(1000):
+        # prime the maxs and mins with second values, avoids divide by 0
+        model.updateObjectiveMaxMin(model.retry())
 
-		vector = model.wrap(vector)			#wrap
-		for i in range(0, len(vector)):		#check all constraints for each vector
-			vector = model.singleRetry(vector, i)	#will change value if constraints aren't met
-											#could implement this differently
-		return(vector)
+    e = model.energy(s)
+    eb = e
 
-	say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(eb) + '\t')
-	while((k < kmax) & (e > emin)):
-		sn = neighbor(s, (kmax - k)/kmax)
-		#sn = model.mutate(s, 1)
-		
-		if(model.updateObjectiveMaxMin(sn)):	#check if new objective bounds
-			e = model.energy(s)						#adjust accordingly 
-			eb = model.energy(sb)
-		
-		en = model.energy(sn)
+    def prob(old, new, t):
+        return(math.exp(((old - new) / t)))
 
-		if(en < eb):
[…]

### 2015-10-20 hw/code/6/model.py

@@ -1,85 +1,93 @@
 from random import *
 
+
 class Model(object):
 
-	def __init__(s, x):
-		s.numOfVars = x
-		s.constraints = []	#list of constraints
-		s.constraintsTrack = {}	#dict mapping decision index to constraint index in s.constraints
-		for i in xrange(x):
-			s.constraintsTrack.update({i:[]})	#initialising constraint tracker
-		s.bounds = {}	#dict of bounds in the form of {index:[min, max]}
-		s.objectives = []	#list of objectives
+    def __init__(s, x):
+        s.numOfVars = x
+        s.constraints = []  # list of constraints
+        # dict mapping decision index to constraint index in s.constraints
+        s.constraintsTrack = {}
+        for i in xrange(x):
+            # initialising constraint tracker
+            s.constraintsTrack.update({i: []})
+        s.bounds = {}  # dict of bounds in the form of {index:[min, max]}
+        s.objectives = []  # list of objectives
 
-	def addConstraint(s, indices, f):		#adds constraints
-		constraintLocation = len(s.constraints)
-		s.constraints.append(f)
-		for i in indices:
-			s.constraintsTrack[i].append(constraintLocation)
-		return s
+    def addConstraint(s, indices, f):  # adds constraints
+        constraintLocation = len(s.constraints)
+        s.constraints.append(f)
+        for i in indices:
+            s.constraintsTrack[i].append(constraintLocation)
+        return s
 
-	def addBound(s, indices, min, max): 	#adds bounds
-		for x in indices:
-			s.bounds.update({x: [min,max]})
-		return s
+    def addBound(s, indices, min, max):  # adds bounds
+        for x in indices:
+            s.bounds.update({x: [min, max]})
+        return s
 
-	def addObjective(s, f):	#adds objective 
-		s.objectives.append(f)
-		return s
+    def addObjective(s, f):  # adds objective
+        s.objectives.append(f)
+        return s
 
-	def boundy(s, index):	# generates new single random decision within bounds
-		return (s.bounds[index][1] - s.bounds[index][0]) * random() + s.bounds[index][0]
+    def boundy(s, index):  # generates new single random decision within bounds
+        return (s.bounds[index][1] - s.bounds[index][0]) * random() + s.bounds[index][0]
 
-	def retry(s, *args):	#generates new random vector
-		vector = [s.boundy(x) for x in range(0, s.numOfVars)]
[…]

### 2015-10-20 hw/code/6/test.py

@@ -3,6 +3,5 @@ from SA import *
 from MWS import *
 
 for m in [Schaffer, Osyczka2, Kursawe]:
-	for o in [SA, MWS]:
-		o(m)
-
+    for o in [SA, MWS]:
+        o(m)

### 2015-10-20 hw/code/6/model.py
prepare for merge

@@ -1,217 +1,0 @@
-import random, math, sys, collections, mws
-class model(object):
-  def __init__(self, decs, cons, objs, norm_objs, wrap, name):
-    self.payload = payload(decs, cons, objs, norm_objs, wrap, name)
-    # print self.payload.decs
-
-  def get_bound(self, id):
-    return self.payload.decs[id]
-
-  def get_name(self):
-    return self.payload.name
-
-  def num_decs(self):
-    return len(self.payload.decs)
-
-  def gen_clean(self):
-    return [self.gen_dec(dec) for dec in self.payload.decs]
-
-  def gen_con(self, vect=None):
-    # If we don't have any constraints
-    # we don't need to do anything
-    # other than regen a new vector
-    if self.payload.cons == None:
-      return self.gen_clean()
-    # If we're calling for the first time
-    # generate a blank vector
-    if not vect:
-      vect = self.gen_clean()
-    # This is set up to try three things
-    # each time there is a problem with a constraint
-    # it first tries to generate either dec in
-    # the constraint, then both.  If that fails
-    # it loops back and tries again.
-    for c in self.payload.cons:
-      while not c.state(vect):
-        # print('c is', c)
-        t1 = self.gen_spec(vect, c.ids[0])
-        t2 = self.gen_spec(vect, c.ids[1])
-        t3 = self.gen_spec(vect, c.ids)
-        if c.state(t1):
-          vect = t1
-        if c.state(t2):
-          vect = t2
-        if c.state(t3):
-          vect = t3
-    return vect
-
-  def gen_spec(self, vect, ids):
-    # We don't really need to deal with multiple ids
-    # yet, since if we call with one id 0,1 or 2,3
-    # we can just index based on the first id.
-    if isinstance(ids, tuple):
-      for id in ids:
-        vect[id] = self.gen_dec(self.payload.decs[id])
-    else:
-      vect[ids] = self.gen_dec(self.payload.decs[ids])
-    return vect
-
-  def gen_dec(self, dec):
-    min = dec[0]
-    max = dec[1]
-    return ((max-min) * random.random()) + min
-
-  def get_min(self, id):
-    return self.payload.decs[id][0]
-
-  def get_max(self, id):
-    return self.payload.decs[id][1]
-
[…]

### 2015-10-20 hw/code/6/models.py

@@ -1,68 +1,0 @@
-import model, mws, sa, math
-# OSYCKZYA STARTS HERE
-def c0(args):
-  # print 'args in c0 are ', args
-  if(args[0] + args[1] - 2 < 0): return False
-  if(6 - args[0] - args[1] < 0): return False
-  if(2 - args[1] + args[0] < 0): return False
-  return True
-def c1(args):
-  # print 'args in c1 are ', args
-  if(4 - (args[2] - 3)**2 - args[3] < 0): return False
-  return True
-def c2(args):
-  # print 'args in c2 are ', args
-  if((args[4] - 3)**3 + args[5] - 4 < 0): return False
-  return True
-
-def f0(args):
-  return -(25*(args[0]-2)**2 + (args[1] - 2)**2 + (args[2] - 1)**2 * (args[3]-4)**2 + (args[4] - 1)**2)
-def f1(args):
-  return args[0]**2 + args[1]**2 + args[2]**2 + args[3]**2 + args[4]**2 + args[5]**2
-
-decs_list = (0,10), (0,10), (1,5), (0,6), (1,5), (0,10)
-constraint_list = ((0,1),c0), ((2,3),c1), ((4,5),c2)
-obs_list = (f0, (-640.908072277, -0.423436047808)), (f1, (25.4899157903, 176.005656027))
-
-osyczka = model.model(decs_list, constraint_list, obs_list, True, True, "Osyczka2")
-
-#SCHAFFER STARTS HERE
-def f0(args):
-  return args[0] * args[0]
-def f1(args):
-  return (args[0] - 2)**2
-
-decs_list = ((-10**(5), 10**(5)),)
-constraint_list = None
-obs_list = (f0, (0, 10000000000)), (f1, (0, 9999600004))
-
-schaffer = model.model(decs_list, constraint_list, obs_list, True, True, "Schaffer")
-
-#KURSAWE STARTS HERE
-# these are parameters used for a and b in the second objective
-a_param = 1
-b_param = 1
-def f0(args):
-  sum = 0
-  sum += -10 * math.exp(-0.2*math.sqrt(args[0]**2 + args[1]**2))
-  sum += -10 * math.exp(-0.2*math.sqrt(args[1]**2 + args[2]**2))
-  return sum
-
-def f1(args):
-  sum = 0
-  sum += abs(args[0])**a_param + 5 * math.sin(args[0])**b_param
[…]

### 2015-10-20 hw/code/6/MWSold.py
printing stuff in MWSold

@@ -7,8 +7,13 @@ def say(x):
     sys.stdout.write(str(x))
     sys.stdout.flush()
 
+# Logger to avoid adding tons of separate print statements
+# dynamically chooses what to print
+def log_state(T, sbo, ebo):
+    print "Ended on try: %s\n SBO: %s\nEBO: %s\n" % (T, ebo, sbo)
 
-def MWS(model):
+def MWS(model, retries, changes):
+    print "Model %s\nNum Retries %s\nNum Changes%s" % (model.name, retries, changes)
     max_changes = 1000
     max_retries = 100
     emin = 0
@@ -24,14 +29,18 @@ def MWS(model):
     eb = e
     ebo = e
     sn = list(sb)
-
     for i in range(max_retries):
-        print '\nT:', i
+        print "T: %d\n Initial Values: S: %s\n E: %s\n" % (i,e,s)
         for j in range(max_changes):
             if e <= emin:
                 sbo = list(s)
                 ebo = e
-                break
+                # This shouldn't be a break
+                # We're at that best possible
+                # overall value here
+                # just print out and stop.
+                log_state(i, sbo, ebo)
+                return
             c = randint(0, model.numOfVars - 1)
 
             if(random() >= 0.5):
@@ -66,10 +75,10 @@ def MWS(model):
                 say("+")
             else:
                 say(".")
+            # Always promote the last solution
             s = list(sn)
             e = en
-        print '\nEB:', eb
-        print 'SB:', sb
+        print "SB: %s\nEB: %s\n" % (sb, eb)
         # First check if the sb for that set of changes was better
         # Than any of our other retries
         if(eb < ebo):
@@ -83,5 +92,4 @@ def MWS(model):
         sb = list(sn)
         eb = en
 
-    print '\nEBO:', ebo
-    print 'SBO:', sbo
+    log_state(max_retries, ebo, sbo)

### 2015-10-21 hw/code/6/MWSold.py
completed and working rig

@@ -1,95 +1,0 @@
-from Models import *
-from random import *
-import sys
-
-
-def say(x):
-    sys.stdout.write(str(x))
-    sys.stdout.flush()
-
-# Logger to avoid adding tons of separate print statements
-# dynamically chooses what to print
-def log_state(T, sbo, ebo):
-    print "Ended on try: %s\n SBO: %s\nEBO: %s\n" % (T, ebo, sbo)
-
-def MWS(model, retries, changes):
-    print "Model %s\nNum Retries %s\nNum Changes%s" % (model.name, retries, changes)
-    max_changes = 1000
-    max_retries = 100
-    emin = 0
-    s = model.retry()
-    model.initializeObjectiveMaxMin(s)
-    # prime the maxs and mins with values, avoids divide by 0
-    for i in xrange(1000):
-        model.updateObjectiveMaxMin(model.retry())
-
-    e = model.energy(s)
-    sb = list(s)
-    sbo = list(s)
-    eb = e
-    ebo = e
-    sn = list(sb)
-    for i in range(max_retries):
-        print "T: %d\n Initial Values: S: %s\n E: %s\n" % (i,e,s)
-        for j in range(max_changes):
-            if e <= emin:
-                sbo = list(s)
-                ebo = e
-                # This shouldn't be a break
-                # We're at that best possible
-                # overall value here
-                # just print out and stop.
-                log_state(i, sbo, ebo)
-                return
-            c = randint(0, model.numOfVars - 1)
-
-            if(random() >= 0.5):
-                sn = model.mutate(s, c)
-                if(model.updateObjectiveMaxMin(sn)):
-                    e = model.energy(s)  # update all energies if new normal
-                    eb = model.energy(sb)
-                    ebo = model.energy(sbo)
-            else:
-                tempS = list(sn)
-                tempE = model.energy(sn)
-                for index in range(1, 10):
-                    tempS[c] = (model.bounds[c][1] -
-                                model.bounds[c][0]) * (index / 10.0)
-                    if(model.checkConstraints(tempS)):
-                        if(model.updateObjectiveMaxMin(tempS)):
-                            # update all energies if new normal
-                            e = model.energy(s)
-                            eb = model.energy(sb)
-                            ebo = model.energy(sbo)
-                            en = model.energy(sn)
-                            tempE = model.energy(tempS)
-                        if(model.energy(tempS) < tempE):
-                            sn = list(tempS)
-                            tempE = model.energy(tempS)
[…]

### 2015-10-21 hw/code/6/Models.py

@@ -16,12 +16,14 @@ Osyczka2 = (Model(6)
             .addConstraint([4, 5], lambda x: ((x[4] - 3)**3 + x[5] - 4) >= 0)
             .addObjective(lambda x: -(25 * (x[0] - 2)**2 + (x[1] - 2)**2) + (x[2] - 1)**2 * (x[3] - 4)**2 + (x[4] - 1)**2)
             .addObjective(lambda x: x[0]**2 + x[1]**2 + x[2]**2 + x[3]**2 + x[4]**2 + x[5]**2)
+            .addName("Osyczka2")
             )
 
 Schaffer = (Model(1)
             .addBound([0], -10**5, 10**5)
             .addObjective(lambda x: x[0]**2)
             .addObjective(lambda x: (x[0] - 2)**2)
+            .addName("Schaffer")
             )
 
 
@@ -36,4 +38,5 @@ Kursawe = (Model(Kn)
            .addObjective(lambda x: reduce(lambda a, b: a + b,
                                           [abs(x[i])**Ka + 5 * math.sin(x[i])**Kb
                                            for i in range(0, len(x) - 1)]))
+           .addName("Kursawe")
            )

### 2015-10-21 hw/code/6/SAold.py

@@ -1,83 +1,0 @@
-# Notes for var names:
-# f = some anonymous function
-# x = some value
-# i = some index
-from random import *
-import math
-import sys
-
-
-def say(x):
-    sys.stdout.write(str(x))
-    sys.stdout.flush()
-
-
-def SA(model):
-
-    emin = 0
-    kmax = 10000.0
-    k = 1
-
-    s = model.retry()
-    sb = s
-
-    model.initializeObjectiveMaxMin(s)
-
-    for i in xrange(1000):
-        # prime the maxs and mins with second values, avoids divide by 0
-        model.updateObjectiveMaxMin(model.retry())
-
-    e = model.energy(s)
-    eb = e
-
-    def prob(old, new, t):
-        return(math.exp(((old - new) / t)))
-
-    def neighbor(vector, t):
-
-        for i in range(0, len(vector)):
-            epsilon = t * random()
-            if bool(getrandbits(1)):  # not sure if we should random on each value
-                vector[i] += epsilon  # or the whole vector
-            else:
-                vector[i] -= epsilon
-
-        vector = model.wrap(vector)  # wrap
-        for i in range(0, len(vector)):  # check all constraints for each vector
-            # will change value if constraints aren't met
-            vector = model.singleRetry(vector, i)
-            # could implement this differently
-        return(vector)
-
-    say("\n" + '(K:' + str(k) + ", SB:({0:.3f}) ".format(eb) + '\t')
-    while((k < kmax) & (e > emin)):
-        sn = neighbor(s, (kmax - k) / kmax)
-        #sn = model.mutate(s, 1)
-
-        if(model.updateObjectiveMaxMin(sn)):  # check if new objective bounds
-            e = model.energy(s)  # adjust accordingly
-            eb = model.energy(sb)
-
-        en = model.energy(sn)
-
-        if(en < eb):
-            say("!")
-            sb = list(sn)
-            eb = en
-
-        if((en < e)):
-            say("+")
-            s = list(sn)
-            e = en
-        elif(prob(e, en, (kmax - k) / kmax) > random()):
-            say("?")
-            s = list(sn)
-            e = en
-
-        say(".")
-        k += 1.00
-        if k % 50 == 0:
-            say("\n" + '(K:' + str(k) + ", EB:({0:.9f}) ".format(eb) + '\t')
-
-    print(sb)
-    print(eb)

### 2015-10-21 hw/code/6/model.py

@@ -13,6 +13,11 @@ class Model(object):
             s.constraintsTrack.update({i: []})
         s.bounds = {}  # dict of bounds in the form of {index:[min, max]}
         s.objectives = []  # list of objectives
+        s.name = ''
+
+    def addName(s, name):
+        s.name = name
+        return s
 
     def addConstraint(s, indices, f):  # adds constraints
         constraintLocation = len(s.constraints)
@@ -49,6 +54,8 @@ class Model(object):
                 for i in xrange(0, s.numOfVars):
                     if(len([x for x in s.constraintsTrack[i] if x in vectorConstraints]) > 0):
                         vector[i] = s.boundy(i)
+        else:
+            vector[index] = s.boundy(index)
         return vector
 
     def mutate(s, vector, index):

### 2015-10-21 hw/code/6/mws.py

@@ -1,116 +1,109 @@
-import model, random, sys
+from Models import *
+from random import *
+from state import *
+import sys
+
 
 def say(x):
-  sys.stdout.write(str(x)); sys.stdout.flush()
+    sys.stdout.write(str(x))
+    sys.stdout.flush()
 
-# Mutate one variable across its
-# entire range, determining whether
-# it has the best possible energy
-def mutate(c, sn, m, energy):
-  vect = sn
-  e = energy(m, vect)
-  # first set the chromosome to the minimum value
-  vect[c] = m.get_min(c)
-  step = 1.0/10.0
-  max = m.get_max(c)
-  for i in range(1, 10):
-    m.add_epsilon(c, vect, max * step)
-    if m.check_con(vect, c) and energy(m, vect) > e:
-      sn = list(vect)
-      e = energy(m, vect)
-  return sn
-
-def tweak(c, vect, m):
-  tmp = list(vect)
-  m.gen_spec(vect, c)
-  capital = 5
-  while not m.check_con(vect, c):
-   # print('in tweak loop c is ' + str(c))
-   # print "check con returns: " + str(m.check_con(vect, c))
-   # print(vect)
-   m.gen_spec(vect, c)
-   capital -= 1
-   if capital == 0: return tmp
-  return vect
-
-def add_vect(m, vect):
-  resp = m.eval_objs(vect)
-  # This works since the formula is
-  # x = (x - min) / (max - min)
-  # min is zero max is 2
-  norm = lambda x: x / 2
-  return norm(resp[0] + resp[1])
-
-def from_hell(m, vect):
-  resp = m.eval_objs(vect)
-  dist_from_hell = ((1 - resp[0])**2 + (1 - resp[1])**2)**0.5
-  return dist_from_hell / (2**(0.5))
-
-
-# Pass in the model m
-def run(m, e, retries, changes):
-  print "RUN DATA: "
-  print "Model: ", m.get_name()
-  print "Optimizer: Max Walk Sat"
-
-  emax = 1
-  if e == 'from_hell':
-    energy = from_hell
-  else:
-    energy = add_vect
-  s = m.gen_con()
-  print's is ',s
-  e = energy(m, s)
-  print 'starting s ', s
-  print 'starting e ', e
-  sb = s
-  sbo = s
-  eb = e
-  ebo = e
-  sn = sb
-  for i in range(retries):
-    print '\nT:', i
-    for j in range(changes):
-      # print 'S', s
-      if e >= emax:
[…]

### 2015-10-21 hw/code/6/run.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+# Stupid simple script to delete out and rerun the rig
+if [ -f out.txt ]
+	then
+		rm out.txt
+fi
+python test.py

### 2015-10-21 hw/code/6/sa.py

@@ -1,137 +1,122 @@
-import random, math, sys
+# Notes for var names:
+# f = some anonymous function
+# x = some value
+# i = some index
+from Models import *
+from random import *
+from state import *
+import sys
 
-def neighbor(m, id, s, temp):
-  vect = list(s)
-  bound = m.get_bound(id)
-  decay = math.exp(-temp)
-  # temp is decreasing so the possibility
-  # of a completely random position also is
-  # decreasing.  If we miss this then we calculate
-  # some epsilon based on the magnitude of the
-  # difference between the max and min for the dec
-  # and then add or subtract it
-  if( random.random() < decay):
-    # print 'vect id before ', vect[id]
-    vect[id] = random.uniform(*bound)
-    # print 'vect id after ', vect[id]
-    # print 'm.check_con ', m.check_con(vect, id)
-    if m.check_con(vect, id):
-      return vect
+def prob(old, new, t):
+    p = math.exp(((old - new) / t))
+    print 'p: ', p
+    return p
+
+def neighbor(model, id, vector, t):
+    vect = list(vector)
+    bounds = model.bounds.get(id)
+    decay = math.exp(-t)
+    if( random() < decay):
+        vect = model.singleRetry(vect, id)
     else:
-      vect = list(s)
-  mag = bound[1] - bound[0]
-  # print 'bound', bound
-  # print 'mag', mag
-  # print 'temp', temp
-  epsilon = decay * abs(mag)
-  # print 'epsilon', epsilon
+        mag = bounds[1] - bounds[0]
+        epsilon = decay * abs(mag)
+        if bool(getrandbits(1)):
+            vect[id] += epsilon
+        else:
+            vect[id] -= epsilon
+        vect = model.wrap(vect)  # wrap
+    for i in range(0, len(vect)):  # check all constraints for each vector
+        # will change value if constraints aren't met
+        vect = model.singleRetry(vect, i)
+        # could implement this differently
+    return(vect)
 
-  add = bool(random.getrandbits(1))
-  if add:
-    m.add_epsilon(id, vect, epsilon)
-  else:
-    m.add_epsilon(id, vect, epsilon * -1)
-  return vect
-
-def say(x):
-  sys.stdout.write(str(x)); sys.stdout.flush()
-
-def prob(old, new, k):
-  # print 'old is ', old
-  # print 'new is ', new
-  # print 'k is ',k
-  x = math.exp(((new - old) / k))
[…]

### 2015-10-21 hw/code/6/test.py

@@ -1,7 +1,8 @@
 from Models import *
-from SA import *
-from MWS import *
+from sa import *
+from mws import *
 
 for m in [Schaffer, Osyczka2, Kursawe]:
-    for o in [SA, MWS]:
-        o(m)
+    for o in [sa, mws]:
+        #Absolutely do not pass integers for retries or changes
+        o(m, 50.0, 500.0)

### 2015-10-22 hw/read/6/summary.tex
Started Paper 6's summary

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}
\title{Paper Six Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Rahman et al. \cite{Rahman} listed below.

\section*{Important Keywords}
\begin{description}
\item [{Cross-project defect prediction}] Using data from one project to predict defects in another.
\item [{Within-project defect prediction}] Using data from previous releases of a project to predict defects in future releases. For new projects, the lack of historical defect data makes this kind of defect prediction almost impossible.

\end{description}

\section*{Feature Extraction}
\begin{description}
\item[{Motivational Statements}]  While within-project defect prediction can be very effective, new projects don't have the volume of data needed to create these models. Cross-project defect prediction models aim to help with this issue, but so far the results have largely been disappointing. The authors hope to show that cross-project defect prediction can be roughly as effective as traditional defect prediction by using a different set of measures, namely those based on a variety of tradeoffs of time-and-cost vs. quality.

\end{description}

\section*{Possible Improvements}

\section*{Connection to Other Papers}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-10-22 hw/code/6/sa.py
fixed one bug, discovered another

@@ -7,9 +7,9 @@ from random import *
 from state import *
 import sys
 
-def prob(old, new, t):
+def prob(old, new, t, retry):
+    if t == 0: return 0.0
     p = math.exp(((old - new) / t))
-    print 'p: ', p
     return p
 
 def neighbor(model, id, vector, t):
@@ -17,8 +17,12 @@ def neighbor(model, id, vector, t):
     bounds = model.bounds.get(id)
     decay = math.exp(-t)
     if( random() < decay):
+        print 'random '
         vect = model.singleRetry(vect, id)
+        print 's ', vector
+        print 'sn ', vect
     else:
+        print 'epsilon '
         mag = bounds[1] - bounds[0]
         epsilon = decay * abs(mag)
         if bool(getrandbits(1)):
@@ -55,6 +59,7 @@ def sa(model, retries, changes, goal = 0.01, pat = 100, era = 100):
         # prime the maxs and mins with second values, avoids divide by 0
         model.updateObjectiveMaxMin(model.retry())
     st = state(model.name, 'SA', s, model.energy(s), retries, changes, era)
+    print 'model name ', model.name
     #changes is some static value passed by the caller
     #st changes is actually a counter
     while st.t:
@@ -97,9 +102,12 @@ def sa(model, retries, changes, goal = 0.01, pat = 100, era = 100):
                 st.app_out('+')
                 st.s = st.sn
                 st.e = st.en
-            elif(prob(st.e, st.en, st.k / changes) > random()):
+            elif(st.en == st.e):
+                st.app_out('=')
+                # print 's ', st.s
+                # print 'sn ', st.sn
+            elif(prob(st.e, st.en, ((changes - st.k)/changes), st.t) < random()):
                 st.app_out('?')
-                print 'took route'
                 st.s = st.sn
                 st.e = st.en
             else:

### 2015-10-22 hw/read/6/summary.tex

@@
 For new projects, the lack of historical defect data makes this kind of defect prediction almost impossible.
+\item[{F-measure}] The harmonic mean of precision and recall. A unified score used to balance the trade-off between precision and recall.
+\item[{Over-fitting}] When a model has completely learned all the variances of the training data and has lost significant generality leading to significantly worse predictive performance on unseen test data.
+This property usually manifests as very low training error and very high test error.
+Over-fitting becomes more probable as a model gains greater complexity.
 

### 2015-10-22 hw/code/6/sa.py
fixed mutate call

@@ -18,7 +18,7 @@ def neighbor(model, id, vector, t):
     decay = math.exp(-t)
     if( random() < decay):
         print 'random '
-        vect = model.singleRetry(vect, id)
+        vect = model.mutate(vect, id)
         print 's ', vector
         print 'sn ', vect
     else:

### 2015-10-27 hw/read/6/summary.tex
Paper Six: Added a feature extraction, possible improvement, and reference to first paper

@@
 quality.
+\item[{Statistical tests}] The authors used the area under the ROC curve (AUC), AUCCE, precision, recall, and f-measure statistical tests to report their results.
+They varied the cutoffs for precision, recall, and f-measure but used the standard 0.5 cutoff for their sanity checks.
 
@@
 \section*{Possible Improvements}
+\begin{itemize}
+\item In the Results section, some of the graphs are hard to read because they have been scaled down to fit on the page.
+Look at Figures 5 and 7 for example.
+The y-axis label runs into the labels along the y-axis.
+To fix this, the individual graphs should be split so that there is only one per column, or they should be combined and made bigger.
+\end{itemize}
 
 \section*{Connection to Other Papers}
+The authors state that they are examining code at the file level.
+They reference our first paper on ecological inference \cite{Posnett} when stating that they feared that a model on a coarser level of aggregation may not be a good predictor at the file level.
 

### 2015-10-27 hw/read/6/summary.tex
Added hypothesis
Added informative visualizations

@@
 quality.
+\item[{Hypothesis}] The hypothesis of this paper is that performance of cross-project defect prediction models is similar to the performance of within-project defect prediction when assessing performance within reasonable and practical resource limitations.
 \item[{Statistical tests}] The authors used the area under the ROC curve (AUC), AUCCE, precision, recall, and f-measure statistical tests to report their results.
 They varied the cutoffs for precision, recall, and f-measure but used the standard 0.5 cutoff for their sanity checks.
+\item[{Informative Visualization}] Figure 2 gives an informative comparison of cross and within-project model performance assessed by multiple performance metrics.
+It visualizes how well the distribution of results overlap for within and cross-project model performance even though within-project generally has higher performance.
+The addition of p-values shows how the differences lack significance.
+Figure 4 is also very informative, showing how weighting the defects by density affects AUC.
+Both cross-project and within-project have similar results and the addition of random and optimal baselines are useful for comparison.
 

### 2015-10-27 hw/read/6/summary.tex
Added two possible improvements

@@
 To fix this, the individual graphs should be split so that there is only one per column, or they should be combined and made bigger.
+\item The authors could have reported the importance of their features in predicting defects using a measurement such as entropy. This could aid other researchers when selecting features.
+\item The data mining methods used to extract features are summarized generally.
+The process can actual be very complex and depend on many assumptions.
+A specific and more detailed explanation could be more useful for future research.
 \end{itemize}

### 2015-11-13 project/model.py
A number of bugfixes

@@ -91,21 +91,16 @@ class Model(object):
         return [obj(vect) for obj in s.objectives]
 
     def cdom(self, c1, c2, can1=None, can2=None):
-        # From what I understand we could add in epsilon here
-        # to determine a worthwhile difference.
-        # I think we'd prob do something like this:
-        # if loss(model, c1, c2) + epsilon < loss(model, c2, c1)
-        # could also return something like the magnitude of the
-        # difference and use that as a sort of energy value I suppose.
         a = self.loss(c1, c2)
         b = self.loss(c2, c1)
         if math.fabs(a-b) < 0.1:
-            print "ZERO DIFFERENCE"
             if(can2):
-                print can1
-                print can2
+                print "ZERO DIFFERENCE IDS: %d %d, diff: %0.3f" % (can1.uniq, can2.uniq, math.fabs(a-b))
+        #         print 'math.fabs(a-b): ', math.fabs(a-b)
+        #         print can1
+        #         print can2
             # else:
-            #     print can1
+            #     # print "SAME CAN"
         if(self.loss(c1, c2) < self.loss(c2, c1)):
             return True
         else:
@@ -120,6 +115,11 @@ class Model(object):
         n = min(len(c1), len(c2))
         losses = [math.exp((a - b)/n) for (a,b) in zip(c1, c2)]
         return sum(losses) / n
+
+    def checkBounds(s, vector):
+        list_of_truth = [False if vector[k] < v[0] or vector[k] > v[1] else True for k, v in s.bounds.iteritems()]
+        # returns true if all are true false if not
+        return all(list_of_truth)
 
     def checkConstraints(s, vector):
         if(len(s.constraints) > 0):

### 2015-11-13 project/pso.py

@@ -75,7 +75,7 @@ Parameters:
 - phi_1: the social learning rate - how much you learn from other people
 - phi_2: the cognitive learning rate - how much you learn from yourself
 """
-def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=5, phi_1=2.8, phi_2=1.3):
+def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1=2.8, phi_2=1.3):
     emin = 0
     # pulled K from the parameters, because it can be calculated from the
     # values for phi.
@@ -87,9 +87,11 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=5, phi_1=
     print '+++++++++++++++++++++++++++++++++++++++++++++++++++++++++'
     print 'Model Name: ', model.name, '\nOptimizer: PSO'
     # Set an initial value for the global best
+    # The downside to setting pbest equal to the current
+    # particle position is that if there is a high phi_1 value
+    # the particle will stay still until something happens globally
+    # that pushes it away.
     st.sb = st.s[0].pbest
-    #changes is some static value passed by the caller
-    #st changes is actually a counter
     tot_deaths = 0
     while st.t:
         st.k = changes
@@ -104,6 +106,15 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=5, phi_1=
                 can.vel =  [k * (vel + (phi_1 * random.uniform(0,1) * (best - pos)) + (phi_2 * random.uniform(0,1) * (gbest - pos))) \
                     for vel, pos, best, gbest in zip(can.vel, can.pos, can.pbest, st.sb)]
                 can.pos = [pos + vel for pos, vel in zip(can.pos, can.vel)]
+                # Currently doing the same thing for particles that are
+                # out of bounds and out of constraints, simply killing them
+                # definitely some other options with this.  If they get to
+                # bounds can set vector to boundary, and vel ot zero, then
+                # just let them be pulled back into the space.
+                if not model.checkBounds(can.pos):
+                    can.pos = model.retry()
+                    can.vel = [0.0 for x in can.pos]
+                    num_deaths += 1
                 if not model.checkConstraints(can.pos):
                     # print 'can ' + str(can.uniq) + ' died'
                     can.pos = model.retry()
@@ -114,7 +125,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=5, phi_1=
                     # position and our phi_1 is much higher than phi_2
[…]

### 2015-11-13 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Kursawe, Osyczka2]:
+for m in [Kursawe]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
-        o(m, 1.0, 10.0)
+        o(m, 1.0, 200.0)

### 2015-11-13 project/pso.py
Added energy calculations

@@ -92,6 +92,8 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
     # the particle will stay still until something happens globally
     # that pushes it away.
     st.sb = st.s[0].pbest
+    #Initialize objective mins and maxs
+    model.initializeObjectiveMaxMin(st.sb)
     tot_deaths = 0
     while st.t:
         st.k = changes
@@ -130,6 +132,9 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                     # Uncomment this to wipe its memory.
                     # can.pbest = list(can.pos)
                     num_deaths += 1
+
+                #Update objective maxs and mins    	
+                model.updateObjectiveMaxMin(can.pos)
             tot_deaths += num_deaths
             # if num_deaths > 0:
             #     print "num deaths in era " + str(st.k) + " : " + str(num_deaths)
@@ -156,7 +161,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                     elif c.pos == can.pos:
                         print "PARTICLES IN SAME POSITION"
                         continue
-                    if not model.cdom(c.pos, can.pos, c, can):
+                    if model.cdom(can.pos, c.pos, can, c):
                         #If we're here then we've been
                         #bettered by the next can, so we
                         #just set it to be our cursor
@@ -167,6 +172,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 # print '+++++++++++++++++++++++++++'
                 # print 'best pos after dom ', best.pos
             st.sb = best.pos
+            st.eb = model.energy(st.sb)
             print 'final best id ', best.uniq
             # Looking at this just to make sure that
             # we are actually updating pbest.
@@ -175,7 +181,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
             #    print can
             st.k -= 1
         # We need a clean slate here.
-        print 'Global best: ', st.sb
+        print 'Global best: ', st.sb, 'global best energy: ', st.eb
         print 'Num deaths: ', tot_deaths
         print 'Total number of particles ', changes*np
         print "Attrition %0.2f percent" % (100.0 * (tot_deaths/(changes*np)))

### 2015-11-13 project/test.py

@@ -10,4 +10,4 @@ from pso import *
 for m in [Kursawe]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
-        o(m, 1.0, 200.0)
+        o(m, 1.0, 10.0)

### 2015-11-13 project/pso.py
Slight change to domination check

@@ -161,7 +161,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                     elif c.pos == can.pos:
                         print "PARTICLES IN SAME POSITION"
                         continue
-                    if model.cdom(can.pos, c.pos, can, c):
+                    if model.cdom(can.pos, c.pos, can, c) and not model.cdom(c.pos, can.pos, c, can):
                         #If we're here then we've been
                         #bettered by the next can, so we
                         #just set it to be our cursor

### 2015-11-13 project/model.py
More bug fixes

@@ -91,16 +91,15 @@ class Model(object):
         return [obj(vect) for obj in s.objectives]
 
     def cdom(self, c1, c2, can1=None, can2=None):
-        a = self.loss(c1, c2)
-        b = self.loss(c2, c1)
-        if math.fabs(a-b) < 0.1:
-            if(can2):
-                print "ZERO DIFFERENCE IDS: %d %d, diff: %0.3f" % (can1.uniq, can2.uniq, math.fabs(a-b))
-        #         print 'math.fabs(a-b): ', math.fabs(a-b)
-        #         print can1
-        #         print can2
-            # else:
-            #     # print "SAME CAN"
+        # if can2:
+        #     print 'comparison ids: ', can1.uniq, can2.uniq
+        # a = self.loss(c1, c2)
+        # b = self.loss(c2, c1)
+        # diff = math.fabs(a-b)
+        # print 'diff is ', diff
+        # if diff < 0.01:
+        #     if(can2):
+        #         print "ZERO DIFFERENCE IDS: %d %d, diff: %0.3f" % (can1.uniq, can2.uniq, diff)
         if(self.loss(c1, c2) < self.loss(c2, c1)):
             return True
         else:

### 2015-11-13 project/pso.py

@@ -85,7 +85,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
     # Energy here is set to zero since we're not actively using it for now.
     st = state(model.name, 'PSO', s, 0, retries, changes, era)
     print '+++++++++++++++++++++++++++++++++++++++++++++++++++++++++'
-    print 'Model Name: ', model.name, '\nOptimizer: PSO'
+    print 'Model Name: ', model.name, '\nOptimizer: PSO, K: ', changes
     # Set an initial value for the global best
     # The downside to setting pbest equal to the current
     # particle position is that if there is a high phi_1 value
@@ -99,10 +99,6 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
         st.k = changes
         patience = pat
         while st.k:
-            # print "INITIAL CANS: "
-            # for can in st.s:
-            #     print 'can.pos: ', can.pos
-            #     print 'can.pbest ', can.pbest
             num_deaths = 0
             for can in st.s:
                 can.vel =  [k * (vel + (phi_1 * random.uniform(0,1) * (best - pos)) + (phi_2 * random.uniform(0,1) * (gbest - pos))) \
@@ -116,44 +112,33 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 if not model.checkBounds(can.pos):
                     can.pos = model.retry()
                     can.vel = [0.0 for x in can.pos]
+                    # Should a killed candidate maintain it's phantom memory?
+                    # Uncomment this to wipe its memory.
+                    # can.pbest = list(can.pos)
                     num_deaths += 1
                 if not model.checkConstraints(can.pos):
-                    # print 'can ' + str(can.uniq) + ' died'
                     can.pos = model.retry()
-                    # If this is zero something really weird happens
-                    # there tends to be a can that will continue on
-                    # having a zero velocity for a long period of time.
-                    # REASON: If the can has a pbest that is its current
-                    # position and our phi_1 is much higher than phi_2
-                    # the particle will be attracted to its current position
-                    # and may not break free for a long period of time.
                     can.vel = [0.0 for x in can.pos]
                     # Should a killed candidate maintain it's phantom memory?
                     # Uncomment this to wipe its memory.
                     # can.pbest = list(can.pos)
                     num_deaths += 1
-
-                #Update objective maxs and mins    	
+                #Update objective maxs and mins
[…]

### 2015-11-13 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Kursawe]:
+for m in [Osyczka2, Fonseca]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
-        o(m, 1.0, 10.0)
+        o(m, 1.0, 500.0)

### 2015-11-13 project/grapher.py
Added decision graphing

@@ -1,0 +1,24 @@
+import matplotlib.pyplot as plt
+from model import *
+
+class grapher(object):
+
+	def __init__(s, model, numOfCans):
+		s.allCansX = {}
+		s.allCansY = {}
+		for i in xrange(numOfCans):
+			s.allCansX.update({i: []})
+			s.allCansY.update({i: []})
+
+		s.model = model
+
+	def addVector(s, v, i):
+		x, y = v[0], v[1]
+		s.allCansX[i].append(x)
+		s.allCansY[i].append(y)
+
+	def graph(s):
+		for i in s.allCansX:
+			plt.scatter(s.allCansX[i], s.allCansY[i])
+
+		plt.show()

### 2015-11-13 project/pso.py

@@ -5,7 +5,9 @@
 from Models import *
 from random import *
 from state import *
+from grapher import *
 import sys, random, math, copy
+
 
 class can(object):
     # Didn't want to override id so used uniq
@@ -82,6 +84,10 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
     phi_tot = phi_1 + phi_2
     k = (2.0/math.fabs(2.0 - (phi_tot) - math.sqrt(phi_tot**2.0 - 4.0*phi_tot)))
     s = gens(model, np)
+    #initialize grapher
+    g = grapher(model, np)
+    for can in s:
+        g.addVector(can.pos, can.uniq)
     # Energy here is set to zero since we're not actively using it for now.
     st = state(model.name, 'PSO', s, 0, retries, changes, era)
     print '+++++++++++++++++++++++++++++++++++++++++++++++++++++++++'
@@ -104,6 +110,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 can.vel =  [k * (vel + (phi_1 * random.uniform(0,1) * (best - pos)) + (phi_2 * random.uniform(0,1) * (gbest - pos))) \
                     for vel, pos, best, gbest in zip(can.vel, can.pos, can.pbest, st.sb)]
                 can.pos = [pos + vel for pos, vel in zip(can.pos, can.vel)]
+                g.addVector(can.pos, can.uniq)
                 # Currently doing the same thing for particles that are
                 # out of bounds and out of constraints, simply killing them
                 # definitely some other options with this.  If they get to
@@ -177,4 +184,5 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
         st.s = gens(model, np)
         st.sb = st.s[0].pbest
         st.t -= 1
+    g.graph()
     st.term()

### 2015-11-13 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Osyczka2, Fonseca]:
+for m in [Tanaka]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
         o(m, 1.0, 500.0)

### 2015-11-14 project/grapher.py
Added color for each unique

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 from model import *
 
+colors = ["AliceBlue","AntiqueWhite","Aqua","Aquamarine","Azure","Beige","Bisque","Black","BlanchedAlmond","Blue","BlueViolet","Brown","BurlyWood","CadetBlue","Chartreuse","Chocolate","Coral","CornflowerBlue","Cornsilk","Crimson","Cyan","DarkBlue","DarkCyan","DarkGoldenRod","DarkGray","DarkGreen","DarkKhaki","DarkMagenta","DarkOliveGreen","DarkOrange","DarkOrchid","DarkRed","DarkSalmon","DarkSeaGreen","DarkSlateBlue","DarkSlateGray","DarkTurquoise","DarkViolet","DeepPink","DeepSkyBlue","DimGray","DodgerBlue","FireBrick","FloralWhite","ForestGreen","Fuchsia","Gainsboro","GhostWhite","Gold","GoldenRod","Gray","Green","GreenYellow","HoneyDew","HotPink","IndianRed" ,"Indigo" ,"Ivory","Khaki","Lavender","LavenderBlush","LawnGreen","LemonChiffon","LightBlue","LightCoral","LightCyan","LightGoldenRodYellow","LightGray","LightGreen","LightPink","LightSalmon","LightSeaGreen","LightSkyBlue","LightSlateGray","LightSteelBlue","LightYellow","Lime","LimeGreen","Linen","Magenta","Maroon","MediumAquaMarine","MediumBlue","MediumOrchid","MediumPurple","MediumSeaGreen","MediumSlateBlue","MediumSpringGreen","MediumTurquoise","MediumVioletRed","MidnightBlue","MintCream","MistyRose","Moccasin","NavajoWhite","Navy","OldLace","Olive","OliveDrab","Orange","OrangeRed","Orchid","PaleGoldenRod","PaleGreen","PaleTurquoise","PaleVioletRed","PapayaWhip","PeachPuff","Peru","Pink","Plum","PowderBlue","Purple","RebeccaPurple","Red","RosyBrown","RoyalBlue","SaddleBrown","Salmon","SandyBrown","SeaGreen","SeaShell","Sienna","Silver","SkyBlue","SlateBlue","SlateGray","Snow","SpringGreen","SteelBlue","Tan","Teal","Thistle","Tomato","Turquoise","Violet","Wheat","White","WhiteSmoke","Yellow",
[…]

### 2015-11-14 project/pso.py

@@ -133,6 +133,9 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 #Update objective maxs and mins
                 model.updateObjectiveMaxMin(can.pos)
             tot_deaths += num_deaths
+            #if you wanter to see step by step particle movement uncomment below
+            #warning you will end up having to terminate this manually
+            #g.graph()
             # print "======================="
             # print "BEGIN DOM PROC K: ", st.k
             # print "======================="

### 2015-11-14 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Tanaka]:
+for m in [Tanaka, Constr_Ex, Srinivas, Viennet2, Viennet3, Viennet4]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
         o(m, 1.0, 500.0)

### 2015-11-14 hw/read/8/summary.tex
added writeup for paper 8

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}
\title{Paper Eight Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Jiang et al. \cite{Jiang} listed below.

\section*{Important Keywords}
\begin{description}
\item [{Personalized change classification}] A defect prediction modeling approach that works by building a change classification model for each specific developer.  The methodology promoted by the paper.
\item[{Traditional change classification}] A defect prediction modeling approach that works by building a single change classification model for all developers in aggregate.  Used as a baseline, since it is the way that defect prediction is generally carried out.
\item[{Multivariate Regression Splines (MARS)}] A defect prediction modeling approach that works with a global aggregate of developers, but groups data to minimize the fitting error.   Used as a baseline in the study, as a sort of middle way between traditional and personalized change classification.

\end{description}

\section*{Feature Extraction}
\begin{description}
\item[{Motivational Statements}]  The idea is that generally studies for defect prediction aggregate all developers together in one model, but there are many differences between individual developers.  One developer may be stronger in one area than another and will make more errors in a certain area than another.  Given that this is the case, the authors believe that it makes sense to create models for individual developers to predict defects since it had not been done prior to this paper.
\item[{Informative Visualization}]  Figure two on page 281 is a really telling visual for proving the author's point that there are drastic differences in the skill of different developers.  The interesting thing about these developers in particular is the fact that this graph is drawn from Linux kernel developers, where you would expect some of the most skilled developers worldwide, but we find errors on things like for loops and modulo just like any normal developer.  But, in terms of the paper, this visual really shows the value in producing models for specific developers.

\end{description}

\section*{Possible Improvements}
\begin{itemize}
\item Even though the authors have shown that the results in terms of both number of bugs found and F1 are statistically significant, it seems that they are overplaying their hand a bit.  Even though the results are statistically significant they seem only to improve on CC and Mars by a very small margin in terms of F1 and not at all in several cases.  They do not even bother discussing this fact in terms of their Threats to Validity.
\item There is a section on future work, but it is incredibly short, and isn't even broken out into its own section given its brevity.  A bit more thought put towards future work would have been nice.
\item The authors go to the trouble of putting together a second methodology for defect prediction in PCC+, but really do not go to a lot of trouble in proving anything about its efficacy.  It seems like a bit of an afterthought and may well have made up another paper entirely if the results had been more conclusive. 
\end{itemize}

\section*{Connection to Other Papers}
The authors used Cost Effectiveness as their most important metric in the paper as discussed in \cite{Rahman}.  They make the case that at when looking at only 20\% of a particular code base PCC ends up being a better predictor of defects.

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-11-14 project/grapher.py
Added resizing of dots based on energy

@@ -21,8 +21,17 @@ class grapher(object):
 
 	def graph(s):
 		plt.title(s.model.name)
+
 		for i in s.allCansX:
 			color = [colors[i]] * len(s.allCansY[i])
-			plt.scatter(s.allCansX[i], s.allCansY[i], c=color)
+			#this will calculate all the energies and then scale
+			#them to 15 which is accepted by matplotlib 
+			#this will increase the size of the circle for each 
+			#dot on the graph in proportion to it's
+			#betterness as an energy (ie the larger the dot
+			#the better the candidate)
+			energies = [(15 - (s.model.energy([x, y]) * 15)) \
+				for (x, y) in zip(s.allCansX[i], s.allCansY[i])]
+			plt.scatter(s.allCansX[i], s.allCansY[i], s=energies, c=color, alpha=0.5)
 
 		plt.show()

### 2015-11-14 project/grapher.py
Added graph for energies, inverted energy relationship in decision graph

@@ -19,9 +19,10 @@ class grapher(object):
 		s.allCansX[i].append(x)
 		s.allCansY[i].append(y)
 
+	#this will graph the decisions
+	#each color is a unique candidate
 	def graph(s):
-		plt.title(s.model.name)
-
+		plt.title(s.model.name + " Decisions")
 		for i in s.allCansX:
 			color = [colors[i]] * len(s.allCansY[i])
 			#this will calculate all the energies and then scale
@@ -30,8 +31,21 @@ class grapher(object):
 			#dot on the graph in proportion to it's
 			#betterness as an energy (ie the larger the dot
 			#the better the candidate)
-			energies = [(15 - (s.model.energy([x, y]) * 15)) \
+			energies = [(s.model.energy([x, y]) * 15) \
 				for (x, y) in zip(s.allCansX[i], s.allCansY[i])]
+			#note: alpha controls conspiracy
 			plt.scatter(s.allCansX[i], s.allCansY[i], s=energies, c=color, alpha=0.5)
 
 		plt.show()
+
+	#this will graph the energies 
+	#each color is a unique candidate
+	def graphEnergy(s):
+		plt.title(s.model.name + " Energies")
+		for i in s.allCansX:
+			color = [colors[i]] * len(s.allCansX[i])
+			o1 = [s.model.calculateObjective([x,y], 0) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+			o2 = [s.model.calculateObjective([x,y], 1) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+			plt.scatter(o1, o2, c=color, alpha=0.5)
+		plt.show()
+

### 2015-11-14 project/model.py

@@ -35,6 +35,11 @@ class Model(object):
         s.objectives.append(f)
         return s
 
+    #takes vector and objective index argument
+    #returns normalized value for objective
+    def calculateObjective(s, v, i): 
+        return ((s.objectives[i](v) - s.objectiveMins[i])/(s.objectiveMaxs[i] - s.objectiveMins[i]))
+
     def boundy(s, index):  # generates new single random decision within bounds
         return (s.bounds[index][1] - s.bounds[index][0]) * random() + s.bounds[index][0]
 

### 2015-11-14 project/pso.py

@@ -100,6 +100,9 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
     st.sb = st.s[0].pbest
     #Initialize objective mins and maxs
     model.initializeObjectiveMaxMin(st.sb)
+    #we whould do this just in case
+    for c in st.s:
+        model.updateObjectiveMaxMin(c.pos)
     tot_deaths = 0
     while st.t:
         st.k = changes
@@ -133,18 +136,18 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 #Update objective maxs and mins
                 model.updateObjectiveMaxMin(can.pos)
             tot_deaths += num_deaths
-            #if you wanter to see step by step particle movement uncomment below
+            #if you want to see step by step particle movement uncomment below
             #warning you will end up having to terminate this manually
             #g.graph()
-            # print "======================="
-            # print "BEGIN DOM PROC K: ", st.k
-            # print "======================="
-            # best = st.s[0]
+            print "======================="
+            print "BEGIN DOM PROC K: ", st.k
+            print "======================="
+            best = st.s[0]
             best_list = []
             low_diff = []
             for c in st.s:
                 best = c
-                # print 'c is ', c.uniq
+                print 'c is ', c.uniq
                 # We first check the can's personal best
                 # and update it if its current position
                 # dominates.
@@ -172,11 +175,11 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 # global best candidate.
                 if(not best.uniq in best_list):
                     best_list.append(best.uniq)
-                # print 'best id after run ', best.uniq
+                print 'best id after run ', best.uniq
             st.sb = best.pos
             st.eb = model.energy(st.sb)
-            # print 'low diff list ', low_diff
-            # print 'best_list ', best_list
+            print 'low diff list ', low_diff
+            print 'best_list ', best_list
             st.k -= 1
         # We need a clean slate here.
         print '++++++++++++++++++++++++++++++++++++++++++++++++++++'
@@ -188,4 +191,5 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
         st.sb = st.s[0].pbest
         st.t -= 1
     g.graph()
+    g.graphEnergy()
     st.term()

### 2015-11-15 hw/read/8/summary.tex
Added some more to reading 8

@@
 Used as a baseline in the study, as a sort of middle way between traditional and personalized change classification.
+\item[{Characteristic vector}]  One of three classes of features the author used to describe the characteristics of source code.
+Basically a vector of integers, where each integer corresponds to a count of node types, e.g.
+reserved keywords.
+\item[{Bag-of-words}] Another of three classes of features used. Stores words within the code, e.g. function names.
 
@@
 One developer may be stronger in one area than another and will make more errors in a certain area than another.
-Given that this is the case, the authors believe that it makes sense to create models for individual developers to predict defects since it had not been done prior to this paper.
+Given that this is the case, the author believes that it makes sense to create models for individual developers to predict defects since it had not been done prior to this paper.
 \item[{Informative Visualization}]  Figure two on page 281 is a really telling visual for proving the author's point that there are drastic differences in the skill of different developers.
@@
 But, in terms of the paper, this visual really shows the value in producing models for specific developers.
-
+\item[{Sampling Procedures}] The author chose six open source projects: Linux, PostgreSQL, Xorg, Eclipse, Lucene, and Jackrabbit.
+The author states that these projects have enough change history data to build good experimental models, and they are commonly found within the literature, which makes it easier to compare their results with those of other researchers.
+\item[{Future Work}] The author mentioned improving defect prediction models to giving more of an explanation of its reasoning so management can make more informed decisions.
+One of the threats to validity was that only open source projects were used, leaving open the possibility to run these models on closed source systems.
+They mentioned that their bug data contains noise that might have affected their results and suggested reducing the noise levels through advanced techniques.
+Finally, they noted that their selection of developers and changes might bias the model and hope to experiment with different selection techniques in the future.
 \end{description}
@@
 \begin{itemize}
-\item Even though the authors have shown that the results in terms of both number of bugs found and F1 are statistically significant, it seems that they are overplaying their hand a bit.
+\item Even though the author has shown that the results in terms of both number of bugs found and F1 are statistically significant, it seems that they are overplaying their hand a bit.
 Even though the results are statistically significant they seem only to improve on CC and Mars by a very small margin in terms of F1 and not at all in several cases.
@@
 \item There is a section on future work, but it is incredibly short, and isn't even broken out into its own section given its brevity.  A bit more thought put towards future work would have been nice.
-\item The authors go to the trouble of putting together a second methodology for defect prediction in PCC+, but really do not go to a lot of trouble in proving anything about its efficacy.
+\item The author goes to the trouble of putting together a second methodology for defect prediction in PCC+, but really does not go to a lot of trouble in proving anything about its efficacy.
 It seems like a bit of an afterthought and may well have made up another paper entirely if the results had been more conclusive.
@@
 \section*{Connection to Other Papers}
-The authors used Cost Effectiveness as their most important metric in the paper as discussed in \cite{Rahman}.
+The author used Cost Effectiveness as their most important metric in the paper as discussed in \cite{Rahman}.
 They make the case that at when looking at only 20\% of a particular code base PCC ends up being a better predictor of defects.

### 2015-11-15 project/grapher.py
troubleshooting maxmin

@@ -42,10 +42,29 @@ class grapher(object):
 	#each color is a unique candidate
 	def graphEnergy(s):
 		plt.title(s.model.name + " Energies")
+		omaxs = s.model.getObjectiveMaxs()
+		omins = s.model.getObjectiveMins()
+
+		print("MAXS:")
+		print(omaxs)
+		print("MINS")
+		print(omins)
+
 		for i in s.allCansX:
-			color = [colors[i]] * len(s.allCansX[i])
-			o1 = [s.model.calculateObjective([x,y], 0) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
-			o2 = [s.model.calculateObjective([x,y], 1) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
-			plt.scatter(o1, o2, c=color, alpha=0.5)
-		plt.show()
+			allVectors = [[x,y] for x,y in zip(s.allCansX[i], s.allCansY[i])]
+			for k in allVectors:
+				ovalue = s.model.cal_objs(k)
+				for j in xrange(len(ovalue)):
+					if ovalue[j] > omaxs[j]:
+						print(str(ovalue[j]) + " is greater than max for objective " + str(j))
+					if ovalue[j] < omins[j]:
+						print(str(ovalue[j]) + " is less than min for objective " + str(j))
+
+
+		# for i in s.allCansX:
+		# 	color = [colors[i]] * len(s.allCansX[i])
+		# 	o1 = [s.model.calculateObjective([x,y], 0) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+		# 	o2 = [s.model.calculateObjective([x,y], 1) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+		# 	plt.scatter(o1, o2, c=color, alpha=0.5)
+		# plt.show()
 

### 2015-11-15 project/model.py

@@ -40,6 +40,12 @@ class Model(object):
     def calculateObjective(s, v, i): 
         return ((s.objectives[i](v) - s.objectiveMins[i])/(s.objectiveMaxs[i] - s.objectiveMins[i]))
 
+    def getObjectiveMaxs(s):
+        return s.objectiveMaxs
+
+    def getObjectiveMins(s):
+        return s.objectiveMins
+
     def boundy(s, index):  # generates new single random decision within bounds
         return (s.bounds[index][1] - s.bounds[index][0]) * random() + s.bounds[index][0]
 

### 2015-11-15 project/pso.py

@@ -190,6 +190,6 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
         st.s = gens(model, np)
         st.sb = st.s[0].pbest
         st.t -= 1
-    g.graph()
+    #g.graph()
     g.graphEnergy()
     st.term()

### 2015-11-15 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Tanaka, Constr_Ex, Srinivas, Viennet2, Viennet3, Viennet4]:
+for m in [Constr_Ex]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
         o(m, 1.0, 500.0)

### 2015-11-15 project/grapher.py
grapher fix

@@ -41,7 +41,7 @@ class grapher(object):
 	#this will graph the energies 
 	#each color is a unique candidate
 	def graphEnergy(s):
-		plt.title(s.model.name + " Energies")
+		plt.title(s.model.name + " Objectives")
 		omaxs = s.model.getObjectiveMaxs()
 		omins = s.model.getObjectiveMins()
 
@@ -61,10 +61,10 @@ class grapher(object):
 						print(str(ovalue[j]) + " is less than min for objective " + str(j))
 
 
-		# for i in s.allCansX:
-		# 	color = [colors[i]] * len(s.allCansX[i])
-		# 	o1 = [s.model.calculateObjective([x,y], 0) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
-		# 	o2 = [s.model.calculateObjective([x,y], 1) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
-		# 	plt.scatter(o1, o2, c=color, alpha=0.5)
-		# plt.show()
+		for i in s.allCansX:
+			color = [colors[i]] * len(s.allCansX[i])
+			o1 = [s.model.calculateObjective([x,y], 0) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+			o2 = [s.model.calculateObjective([x,y], 1) for (x,y) in zip(s.allCansX[i], s.allCansY[i])]
+			plt.scatter(o1, o2, c=color, alpha=0.5)
+		plt.show()
 

### 2015-11-15 project/pso.py

@@ -113,7 +113,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                 can.vel =  [k * (vel + (phi_1 * random.uniform(0,1) * (best - pos)) + (phi_2 * random.uniform(0,1) * (gbest - pos))) \
                     for vel, pos, best, gbest in zip(can.vel, can.pos, can.pbest, st.sb)]
                 can.pos = [pos + vel for pos, vel in zip(can.pos, can.vel)]
-                g.addVector(can.pos, can.uniq)
+                
                 # Currently doing the same thing for particles that are
                 # out of bounds and out of constraints, simply killing them
                 # definitely some other options with this.  If they get to
@@ -134,6 +134,7 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
                     # can.pbest = list(can.pos)
                     num_deaths += 1
                 #Update objective maxs and mins
+                g.addVector(can.pos, can.uniq)
                 model.updateObjectiveMaxMin(can.pos)
             tot_deaths += num_deaths
             #if you want to see step by step particle movement uncomment below
@@ -190,6 +191,6 @@ def pso(model, retries, changes, goal = 0.01, pat = 100, era = 100, np=30, phi_1
         st.s = gens(model, np)
         st.sb = st.s[0].pbest
         st.t -= 1
-    #g.graph()
+    g.graph()
     g.graphEnergy()
     st.term()

### 2015-11-15 project/test.py

@@ -7,7 +7,7 @@ from pso import *
 
 # full model list
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
-for m in [Constr_Ex]:
+for m in [Srinivas, Tanaka, Viennet2, Viennet3, Viennet4, Constr_Ex]:
     for o in [pso]:
         #Absolutely do not pass integers for retries or changes
         o(m, 1.0, 500.0)

### 2015-11-21 project/Models.py
Pushed fixes to DTLZ and added DTLZ4

@@ -197,41 +197,41 @@ Water = (Model(3)
          )
 
 # 5 is recommended
-m_dtlz1 = 5
+m_dtlz1 = 3
 # g function for DTLZ1
 g_dtlz1 = (lambda x: 100 * (len(x) * reduce(lambda a, b: a + b,
                                 [(x[i] - 0.5)**2 - math.cos(20 * math.pi * (x[i] - 0.5)) for i in xrange(len(x))])))
 
 DTLZ1 = Model(m_dtlz1).addName("DTLZ1")
 
-for i in xrange(m_dtlz1):
-    DTLZ1.addBound([i], 0, 1)
-    DTLZ1.addObjective(lambda x: gen_dtlz1_obj(x, i))
+for i_1 in xrange(m_dtlz1):
+    DTLZ1.addBound([i_1], 0, 1)
+    DTLZ1.addObjective(lambda x: gen_dtlz1_obj(x, i_1))
 
-def gen_dtlz1_obj(x, i):
+def gen_dtlz1_obj(x, index):
     product = 1
 
-    for j in xrange(len(x) - i - 1):
+    for j in xrange(len(x) - index - 1):
         product *= x[j]
 
-    if i > 0:
-        product *= (1 - x[len(x) - i - 1])
+    if index > 0:
+        product *= (1 - x[len(x) - index - 1])
 
     product *= 0.5 * (1 + g_dtlz1(x))
 
     return product
 
 # 10 is recommended
-m_dtlz2 = 10
+m_dtlz2 = 20
 # g function for DTLZ2
 g_dtlz2 = (lambda x: reduce(lambda a, b: a + b,
                                 [(x[i] - 0.5)**2 for i in xrange(len(x))]))
 
 DTLZ2 = Model(m_dtlz2).addName("DTLZ2")
 
-for i in xrange(m_dtlz2):
-    DTLZ2.addBound([i], 0, 1)
-    DTLZ2.addObjective(lambda x: gen_dtlz2_obj(x, i))
+for i_2 in xrange(m_dtlz2):
+    DTLZ2.addBound([i_2], 0, 1)
+    DTLZ2.addObjective(lambda x: gen_dtlz2_obj(x, i_2))
 
 def gen_dtlz2_obj(x, i):
     product = 1
@@ -247,26 +247,53 @@ def gen_dtlz2_obj(x, i):
     return product
 
 # 10 is recommended
-m_dtlz3 = 10
+m_dtlz3 = 50
[…]

### 2015-11-21 project/test.py

@@ -9,7 +9,7 @@ from classicalGlobalPSOV2 import *
 # Osyczka2, Fonseca, ZDT1, ZDT2, ZDT3, ZDT4, ZDT6, Tanaka, Constr_Ex, Srinivas, Golinski, Viennet2, Viennet3, Viennet4, Water
 # Tanaka, Viennet2, Viennet3, Viennet4, Constr_Ex
 
-for m in [Fonseca]:
+for m in [DTLZ4]:
     for o in [adaptiveGlobalPSO]:
         #Absolutely do not pass integers for retries or changes
         o(m, 5.0, 500.0)

### 2015-11-21 hw/read/9/summary.tex
Added some keywords for reading 9

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}
\title{Paper Nine Summary}

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

\maketitle

\section*{Reference}

Nam et al. \cite{Nam} listed below.

\section*{Important Keywords}
\begin{description}
\item[{Transfer defect learning}] Extracting common knowledge from one task domain and transferring it to another. The transferred knowledge is then used to train a prediction model.
\item[{TCA+}] An improvement on Transfer Component Analysis. TCA can map the data of the source and target projects on a latent feature space, but is sensitive to normalization. TCA+ selects a proper normalization to yield better prediction performance.
\item[{Data set Characteristic Vector}] A vector of six elements each relating to the distance between pairs of instances of data. DCVs are used to see how similar two projects are (see below).
\item[{Similarity vector}] Represents the difference between two projects: a source and a target. Examples include "much more", "less", or "same". The values in the DCVs are used to calculate the similarity vectors.
\end{description}

\section*{Feature Extraction}

\section*{Possible Improvements}

\section*{Connection to Other Papers}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2015-11-30 project/Models.py
Fixed issues with gigantic console.txt file

@@ -102,7 +102,7 @@ Tanaka = (Model(2)
           .addConstraint([0, 1], lambda x: -x[0]**2 - x[1]**2 + 1 + 0.1 * math.cos(16 * math.atan(x[0] / x[1])) <= 0)
           .addConstraint([0, 1], lambda x: (x[0] - 0.5)**2 + (x[1] - 0.5)**2 <= 0.5)
           .addObjective(lambda x: x[0])
-          .addObjective(lambda x: x[0])
+          .addObjective(lambda x: x[1])
           .addName("Tanaka")
           )
 
@@ -196,30 +196,57 @@ Water = (Model(3)
          .addName("Water")
          )
 
-# 5 is recommended
+#############################################################
+# START OF DTLZ1
+#############################################################
+
+# Number of objective dimensions
 m_dtlz1 = 3
+# 5 is recommended
+k_dtlz1 = 5
+# n val
+n_dtlz1 = m_dtlz1 + k_dtlz1 - 1
+
 # g function for DTLZ1
-g_dtlz1 = (lambda x: 100 * (len(x) * reduce(lambda a, b: a + b,
-                                [(x[i] - 0.5)**2 - math.cos(20 * math.pi * (x[i] - 0.5)) for i in xrange(len(x))])))
+g_dtlz1 = lambda x: 100 * (n_dtlz1 + sum(\
+    [(x[i] - 0.5)**2 - math.cos(20 * math.pi * (x[i] - 0.5)) for i in xrange(n_dtlz1)]))
 
-DTLZ1 = Model(m_dtlz1).addName("DTLZ1")
 
-for i_1 in xrange(m_dtlz1):
+DTLZ1 = (Model(n_dtlz1)
+        .addName("DTLZ1")
+        .addObjective(lambda x: 0.5 * x[0] * x[1] * (1 + g_dtlz1(x)))
+        .addObjective(lambda x: 0.5 * x[0] * (1 - x[1]) * (1 + g_dtlz1(x)))
+        .addObjective(lambda x: 0.5 * (1 - x[0]) * (1 + g_dtlz1(x)))
+        )
+
+for i_1 in xrange(n_dtlz1):
     DTLZ1.addBound([i_1], 0, 1)
-    DTLZ1.addObjective(lambda x: gen_dtlz1_obj(x, i_1))
 
-def gen_dtlz1_obj(x, index):
-    product = 1
+# def gen_dtlz1_obj(x, index):
[…]

### 2015-11-30 project/adaptiveGlobalPSO.py

@@ -1,14 +1,8 @@
-# Notes for var names:
-# f = some anonymous function
-# x = some value
-# i = some index
 from Models import *
 from random import *
 from state import *
 from grapher import *
 import sys, random, math, copy
-
-
 
 def gens(model, np):
     init_pos = [model.retry() for x in xrange(np)]
@@ -19,7 +13,10 @@ def gens(model, np):
     return cans
 
 def addToFront(model, frontier, pos):
+    if pos in frontier:
+        return
     nondom = True
+    count = 0
     for fpos in frontier:
         ret_val = model.cdom(pos, fpos)
         if ret_val == -1:
@@ -31,105 +28,36 @@ def addToFront(model, frontier, pos):
         else:
             nondom = False
             break
+        count += 1
     if nondom:
         frontier.append(pos)
 
-"""
-Parameters:
-- model: The model you want to run.
-- retries: The number of times to completely restart from scratch with
-  a totally random vector.
-- changes: The number of times to actually run the optimizer for each retry
-- goal: This is an epsilon value.  If the energy value is within this amount
-  of the minimum/maximum energy then we decide its good enough and stop.
-- pat: This is our patience for finding a solution.  If we see the same
-  energy best value 100 times in a row we give up.  If somewhere in our
-  countdown we actually find a new best we reset the patience to its original
-  value again.
-- era: This is basically a pass through to the state of the optimizer. It determines
-  how often we will print an output line giving the best energy and best solution so far.
-- np: The number of candidates
-- w: the influence of the current velocity
-- phi_1: the social learning rate - how much you learn from other people
-- phi_2: the cognitive learning rate - how much you learn from yourself
-"""
 def adaptiveGlobalPSO(model, retries, changes, graph=False, goal = 0.01, pat = 100, \
-    era = 100, np=30, phi_1=2.5, phi_2=1.5):
+    era = 100, np=30, phi_1=1.5, phi_2=2.5):
     emin = 0
-    # pulled K from the parameters, because it can be calculated from the
-    # values for phi.
     phi_tot = phi_1 + phi_2
     k = (2.0/math.fabs(2.0 - (phi_tot) - math.sqrt(phi_tot**2.0 - 4.0*phi_tot)))
     s = gens(model, np)
-    #initialize grapher
-    if graph:
-        g = grapher(model, np)
-        for can in s:
-            g.addVector(can.pos, can.uniq)
-    # Energy here is set to zero since we're not actively using it for now.
[…]

### 2015-11-30 project/front_test.py

@@ -1,7 +1,7 @@
 import math
 
-c1 = [-273.3632, 75.2432]
-c2 = [-273.048, 74.848]
+c1 = [250.90619794930973, 141.88259339345035]
+c2 = [14.144825715501085, 64.55868802601792]
 n = min(len(c1), len(c2))
 losses_a = [math.exp((a - b)/n) for (a,b) in zip(c1, c2)]
 losses_a = sum(losses_a) / n

### 2015-11-30 project/model.py

@@ -107,6 +107,7 @@ class Model(object):
             return False
 
     def cal_objs(s, vect):
+        print "vect: ", vect
         obs = list()
         for i in xrange(len(s.objectives)):
             obs.append(s.calculateObjective(vect, i))
@@ -115,24 +116,22 @@ class Model(object):
     def cal_objs_2(s, vect):
         obs = list()
         obs = [obj(vect) for obj in s.objectives]
-        # print obs
         return obs
 
     def cdom(self, c1, c2, can1=None, can2=None):
         a = self.loss(c1, c2)
         b = self.loss(c2, c1)
         diff = math.fabs(a-b)
-        if diff < 0.1:
+        # 0.6 is a reasonable value here in most cases
+        # DTLZ is proving to need a larger value
+        if diff < 0.06:
             return -1
         elif(a < b):
             return 1
         else:
             return 0
 
-    # Written to assume minimization
-    # Menzies' code added flexibility to
-    # minimize or maximize.  Figured we'd
-    # just peg this for now.
+    # Written to assume minimization.
     def loss(self, c1, c2):
         c1,c2 = self.cal_objs_2(c1), self.cal_objs_2(c2)
         n = min(len(c1), len(c2))

### 2015-11-30 project/run.sh

@@ -17,7 +17,19 @@ cd ..
 cd ..
 # Run rig
 python test.py
-cd metrics/HyperVolume/
-python hypervolume_runner.py
+# Only run hypervolume if -h flag is used.
+# Partially stolen from here http://wiki.bash-hackers.org/howto/getopts_tutorial
+while getopts ":h" opt; do
+  case $opt in
+    h)
+      echo "Calculate Hypervolume" >&2
+      cd metrics/HyperVolume/
+	  python hypervolume_runner.py
+      ;;
+    \?)
+      echo "Invalid option: -$OPTARG" >&2
+      ;;
+  esac
+done
 cd ../Spread/
 python Spread.py

### 2015-11-30 project/state.py

@@ -108,20 +108,28 @@ class state(object):
       (self.name, self.optimizer, self._ebo, self._sbo))
 
   def addFrontier(self, obVals):
+    if obVals not in self.frontier:
       self.frontier.append(obVals)
+
+  def convergence(self):
+    # based on https://github.com/ai-se/storm/blob/master/PerformanceMetrics/IGD/IGD_Calculation.py
+    print "Calculating convergence"
+    path = "./metrics/Spread/True_PF"
+    fn = path + model_name
+
 
   """
   This is a special method specifically for PSO to output text files for
   the frontiers that are in the personal bests for each of the  particles.
   """
   def termPSO(self):
+    print(convergence())
+
+    #Write to spread and hypervolume files
     spread_out = self.spread_path + self.optimizer + "_" + self.name + ".txt"
     hypervolume_out = self.hypervolume_path + self.optimizer + "_" + self.name + ".txt"
     hypervolume_file = open(hypervolume_out, 'w')
     spread_file = open(spread_out, 'w')
-
-
-    # Uncommenting the below will print out all of the frontiers to the console
     outList = list()
     for front in self.frontier:
       for vector in front:
@@ -129,44 +137,15 @@ class state(object):
         if not ln in outList:
           outList.append(ln)
     outString = "\n".join(outList)
-    # print outString
-
-    # outList = ["\n".join([" ".join(map(str,vector)) for vector in front]) for front in self.frontier]
-    # outString = "\n".join(outList)
-    # print outString
-
-    # print "Dominant frontier:"
-    # fin = ""
-    # for tup in zip(*self.frontier):
-    #   tup_string = ""
-    #   best = 0
-    #   for i in xrange(len(tup) - 1):
-    #     if not self.cdom_spec(tup[best], tup[i+1]):
-    #       best = i + 1
-    #   fin += " ".join(map(str, tup[best])) + '\n'
-
-    # print fin
     hypervolume_file.write(outString)
     spread_file.write(outString)
 
+    #Write a closing message with frontier, name of optimizer, and name of model
     if self.outstring != "":
       self.logger.info(self.outstring)
       self.outstring =""
     self.logger.info("%s\nFINAL:\nMODEL:%s\nOPTIMIZER:%s" % ('-'*100, self.name, self.optimizer))
     self.logger.info("FRONTIER:\n%s" % outString)
-
[…]

### 2015-11-30 project/test.py

@@ -12,6 +12,6 @@ from classicalGlobalPSOV2 import *
 for m in [Tanaka]:
     for o in [adaptiveGlobalPSO]:
         #Absolutely do not pass integers for retries or changes
-        o(m, 2.0, 2000.0)
+        o(m, 5.0, 2000.0)
 
 

### 2015-11-30 hw/read/9/summary.tex
Added some features for reading 9

@@
 \usepackage{babel}
+\usepackage{hyperref} 
 \begin{document}
@@
 \section*{Feature Extraction}
+\begin{description}
+\item[{Motivational statements}] Cross-project defect prediction is often necessary for new projects, but doesn't always yield good results.
+Therefore, the authors hope to employ transfer defect learning to improve the performance of these models.
+\item[{Data}] The authors have provided the data used in their experiments at\\
+ \href{https://sites.google.com/site/transferdefect/}{https://sites.google.com/site/transferdefect/}.
+\item[{Future work}] The authors were looking into transferring knowledge across entire domains as an extension of transfer learning.
+They were also interested in seeing which other prediction and recommendation systems might benefit from transfer learning.
+\end{description}
 

### 2015-11-30 project/model.py
changed shell script to allow multiple metric modes

@@ -119,12 +119,13 @@ class Model(object):
         return obs
 
     def cdom(self, c1, c2, can1=None, can2=None):
+        epsilon = 0.06
         a = self.loss(c1, c2)
         b = self.loss(c2, c1)
         diff = math.fabs(a-b)
         # 0.6 is a reasonable value here in most cases
         # DTLZ is proving to need a larger value
-        if diff < 0.06:
+        if diff < epsilon:
             return -1
         elif(a < b):
             return 1

### 2015-11-30 project/run.sh

@@ -19,17 +19,34 @@ cd ..
 python test.py
 # Only run hypervolume if -h flag is used.
 # Partially stolen from here http://wiki.bash-hackers.org/howto/getopts_tutorial
-while getopts ":h" opt; do
+while getopts ":hsx" opt; do
   case $opt in
+    x)
+      echo "Calculate Hypervolume" >&2
+      cd metrics/HyperVolume/
+      python hypervolume_runner.py
+      cd ..
+      cd ..
+      echo "Calculate Spread" >&2
+      cd metrics/Spread/
+      python Spread.py
+      ;;
     h)
       echo "Calculate Hypervolume" >&2
       cd metrics/HyperVolume/
-	  python hypervolume_runner.py
+	    python hypervolume_runner.py
+      cd ..
+      cd ..
+      ;;
+    s)
+      echo "Calculate Spread" >&2
+      cd metrics/Spread/
+      python Spread.py
+      cd ..
+      cd ..
       ;;
     \?)
       echo "Invalid option: -$OPTARG" >&2
       ;;
   esac
 done
-cd ../Spread/
-python Spread.py

### 2015-11-30 project/state.py

@@ -123,7 +123,6 @@ class state(object):
   the frontiers that are in the personal bests for each of the  particles.
   """
   def termPSO(self):
-    print(convergence())
 
     #Write to spread and hypervolume files
     spread_out = self.spread_path + self.optimizer + "_" + self.name + ".txt"

### 2015-11-30 project/test.py

@@ -12,6 +12,4 @@ from classicalGlobalPSOV2 import *
 for m in [Tanaka]:
     for o in [adaptiveGlobalPSO]:
         #Absolutely do not pass integers for retries or changes
-        o(m, 5.0, 2000.0)
-
-
+        o(m, 1.0, 500.0)

### 2015-12-11 paper/paper.tex
Added template for final paper

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Automated Software Engineering Final Paper (Working Title)}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Matthew Neal\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{meneal@ncsu.edu}
% 2nd. author
\alignauthor
Joseph Sankar\\
	   \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{jesankar@ncsu.edu}
% 3rd. author
\alignauthor Alexandar Sobran\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{aisobran@ncsu.edu}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\centering
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\begin{figure*}
\centering
\caption{A sample black and white graphic
that needs to span two columns of text.}
\end{figure*}

\begin{figure}
\centering
\caption{A sample black and white graphic that has
been resized with the \texttt{includegraphics} command.}
\vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{references}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2015-12-12 paper/paper.tex
Added some to intro and related work

@@
 \section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+It is a well-known fact that software bugs are much cheaper and easier to fix before being released.
+But finding these bugs is often difficult and may not be cost effective to fix.
+Researchers have been working on fault detection models to predict which software modules are most likely to contain bugs post-release.
+Management can use these predictions to focus testing and bug-fixing efforts on those modules, resulting in fewer bugs in release which are less costly to fix.
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+In this paper, we focus on the advances made in software fault prediction models in the literature. Section 2 contains an assortment of existing work in the area.
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+\section{Related Work}
+Cagatay Catal and Banu Diri \cite{Catal} gave an overview of software fault prediction studies and advancements up to 2008.
+They found that an increasing number of studies used datasets available to the public.
+They also found that since 2005, machine learning algorithms have become increasingly popular choices to implement the models.
+Finally, they observed that the most dominant metrics in fault prediction were at the method level.
+They recommended that machine learning algorithms and public datasets continue to be used, but caution against using method-level metrics and instead suggested class-level metrics as they can predict faults earlier in the software development cycle.
 
-\section{The {\secit Body} of The Paper}
 Typically, the body of a paper is organized

### 2015-12-12 paper/paper.tex
Added Vandecruys paper to related work

@@
 % in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{30 July 1999}
 % Just remember to make sure that the TOTAL number of authors
@@
 %
-\printccsdesc
+%\printccsdesc
 
@@
 
-\keywords{ACM proceedings; \LaTeX; text tagging}
+\keywords{Fault prediction model; Software mining; Ant Colony Optimization; Classification}
 
@@
 They recommended that machine learning algorithms and public datasets continue to be used, but caution against using method-level metrics and instead suggested class-level metrics as they can predict faults earlier in the software development cycle.
+
+Vandecruys et al \cite{Vandecruys} mined software repositories to create predictive models.
+The authors used AntMiner+, an Ant Colony Optimization (ACO)-based classification technique.
+On public datasets, AntMiner+ was found to be competitive to alternative classification techniques, such as C4.5, logistic regression, and support vector machines.
+The authors suggested that software managers would find the output of rules produced by AntMiner+ easy to understand and accept.
 
@@
 formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
+or the Definition shown above,
 use the \texttt{{\char'134}newtheorem} or the

### 2015-12-12 paper/paper.tex
Added Nagappan paper to related work

@@
 The authors suggested that software managers would find the output of rules produced by AntMiner+ easy to understand and accept.
+
+While there have been plenty of studies about predicting software faults based on the code itself, few studies have looked at organizational structure as a factor.
+Nagappan et al \cite{Nagappan} used organizational metrics, such as number of engineers, edit frequency, and organizational intersection factor to predict fault-proneness.
+The authors compared the effectiveness of the resulting model with alternative models which use traditional software metrics, like code churn and code complexity.
+They found that the model derived from organizational metrics had better precision and recall than others derived from software metrics, meaning they can also be effective indicators of failure-proneness.
 

### 2015-12-12 hw/read/9/summary.tex
complete summary of paper 9

@@
 \documentclass[english]{article}
-\usepackage[T1]{fontenc}
 \usepackage[latin9]{inputenc}
@@
 They were also interested in seeing which other prediction and recommendation systems might benefit from transfer learning.
+\item[{Statistical Tests}] The authors use the F-measure as a metric to determine the performance of TCA vs TCA+ vs within target cross prediction.
+They state that because of the trade off between precision and recall, providing F-measure is a better metric to provide overall.
 \end{description}
@@
 \section*{Possible Improvements}
+\begin{itemize}
+\item The authors make a statement on page five in the section on expirimental design that is unfortunately false.
+They state that 10-fold cross validation essetially uses 90 percent of the training data and 10 percent of the test data as a downside of 10-fold cross validation.
+They neglect to state that it does that 10 times and actually goes through the entireity of the 10 possible permutations of the data and calculates its error based on that.
+It may have been enough to state that random split was used widely in the literature and leave out the statement on 10-fold.
 
+\item There is not a future work section that is actually specifically split out in the paper, and what they do provide is really sparse.  A bit of expansion on that would have been extremely helpful.
+
+\item Tables X and XI could be improved to be a bit simpler to understand.
+The within target $\rightarrow$ target column is a bit confusing, and furthermore the reasoning for only providing (N4) and (N2) normalization techniques in X and XI respectively is a bit confusing as well.
+
+\end{itemize}
 \section*{Connection to Other Papers}
+\begin{itemize}
+\item There is a direct connection with \cite{Rahman} as the author discusses his paper as evidence that cross-project defect prediction works as well as within-project prediction in terms of cost effectiveness.
 
+\end{itemize}
 \bibliographystyle{plain}

### 2015-12-12 hw/read/9/summary.tex
fixed typos

@@
 \begin{itemize}
-\item The authors make a statement on page five in the section on expirimental design that is unfortunately false.
-They state that 10-fold cross validation essetially uses 90 percent of the training data and 10 percent of the test data as a downside of 10-fold cross validation.
-They neglect to state that it does that 10 times and actually goes through the entireity of the 10 possible permutations of the data and calculates its error based on that.
+\item The authors make a statement on page five in the section on experimental design that is unfortunately false.
+They state that 10-fold cross validation essentially uses 90 percent of the training data and 10 percent of the test data as a downside of 10-fold cross validation.
+They neglect to state that it does that 10 times and actually goes through the entirety of the 10 possible permutations of the data and calculates its error based on that.
 It may have been enough to state that random split was used widely in the literature and leave out the statement on 10-fold.

### 2015-12-12 paper/paper.tex
Added Bird paper to related work

@@
 They found that the model derived from organizational metrics had better precision and recall than others derived from software metrics, meaning they can also be effective indicators of failure-proneness.
+
+Bird et al \cite{Bird} examined whether development that is largely distributed produces more failures than development that is mainly collocated.
+The belief at the time was that distributed development was prone to more failures than collocated development.
+They found a negligible difference in both code metrics and failures between the two methods of development.
+The authors examined how the developers working on Windows Vista managed to work well together among teams located in different countries based on the relationships between the development sites, cultural barriers, communication, consistent use of tools, end to end ownership, common schedules, and organizational integration.
+They recommended that companies wishing to distribute development across sites located far apart to employ similar strategies to overcome some of the difficulties associated with such an endeavor.
 

### 2015-12-13 paper/paper.tex
Added Arisholm paper to related work

@@
 Bird et al \cite{Bird} examined whether development that is largely distributed produces more failures than development that is mainly collocated.
-The belief at the time was that distributed development was prone to more failures than collocated development.
+The belief at the time was that global development was prone to more failures than collocated development.
 They found a negligible difference in both code metrics and failures between the two methods of development.
@@
 They recommended that companies wishing to distribute development across sites located far apart to employ similar strategies to overcome some of the difficulties associated with such an endeavor.
+
+Arisholm et al \cite{Arisholm} examined different ways to build and evaluate fault prediction models.
+First, they tested a variety of modeling techniques, such as neural networks, C4.5 with some variants, support vector machines, and logistic regression.
+They then looked at different metrics:  Process measures, OO code measures, and delta measures.
+Finally, they looked at ROC area and cost-effectiveness as evaluation criteria.
+They found that the choice of modeling technique did not have much of an impact when evaluated with both criteria tested.
+Among the metric sets, they found that process measures provide a significant improvement over the others, even though they are typically more costly to collect.
+They also suggested cost-effectiveness as a good evaluation technique instead of traditional techniques like precision and recall as smarter decisions can be made to prioritize which parts of the project are tested and bug-fixed.
 

### 2015-12-13 paper/paper.tex
Added Posnett paper to related work

@@
 They also suggested cost-effectiveness as a good evaluation technique instead of traditional techniques like precision and recall as smarter decisions can be made to prioritize which parts of the project are tested and bug-fixed.
+
+Most software products are structured in a hierarchical format, for example into methods, classes, files, packages, etc.
+What level of analysis should fault prediction models operate on?
+And can analysis on one level of study apply to other levels?
+Posnett et al \cite{Posnett} examines these issues.
+They observed that sometimes relevant phenomena only occur at an aggregated level or data may only be observed at an aggregated level, meaning that studies are often conducted at aggregated levels.
+They also noted that in other fields of study there are ecological fallacies which make findings at aggregated levels not apply at disaggregated levels.
+They found that much of these fallacies also exist in the domain of computer software and that care needs to be taken when employing ecological inference.
+As to how exactly the risks of ecological fallacies can be dealt with, the authors left open for future research.
 

### 2015-12-13 paper/paper.tex
more reasonable title
Added remainder of previous papers to related work

@@
 
-\title{Automated Software Engineering Final Paper (Working Title)}
+\title{Software Defect Prediction: Review, Commentary, and Future Work}
 %
@@
 
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
+Traditional software fault prediction models are trained on historical project data.
+Since new projects do not have such a volume of historical data, these fault prediction models are not as effective at within-project defect prediction.
+A possible solution to this issue is cross-project prediction which uses data from one project to predict defects in another.
+Still, models using this technique exhibit poor performance.
+Rahman et al \cite{Rahman} argued that one reason for such behavior is that standard evaluation measures such as precision, recall, and F-measure are taken at specific threshold settings, while they really should be taken in a range of time/cost vs.
+quality tradeoffs.
+They took the standard measures at a variety of tradeoffs and found that cross-project defect prediction is at least as good as within-project defect prediction, and sometimes substantially better.
 
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
+Also within the area of cross-project defect prediction, Nam et al \cite{Nam} found that when the source and target projects have a different feature distributions, the resulting model gives poor performance.
+The authors use Transfer Component Analysis (TCA) to find a common feature set for both projects and then map the data of both projects to it.
+They found that TCA is sensitive to normalization, so they developed an improvement, TCA+ to select appropriate normalization options.
+After using TCA+ to create cross-project defect prediction models for eight open-source projects, they found a significant improvement in prediction performance compared to traditional algorithms and techniques.
+The authors proposed applying knowledge in one domain to another to further improve performance.
+
+As another approach to improving fault prediction, Tian Jiang \cite{Jiang} introduced \emph{personalized defect prediction}.
+He argued that developers have different coding styles and techniques and that if each developer had their own defect prediction model, performance would improve.
+He was careful to note that the developer was not a feature of the model, but that there was a model for each developer.
+He ran experiments on six large open-source projects using PCC+, a model which chooses the highest confidence prediction among CC (traditional change classification), PCC (personalized change classification), and weighted PCC (PCC with changes from other developers added to a developer's model).
+Compared to CC and MARS (another predictor which also creates different models for different groups of data), PCC+ outperformed CC, MARS, and PCC as long as there is enough training data for each developer.
+Jiang recommended that PCC+ be applied to other recommendation systems and types of predictions.
 

### 2015-12-14 paper/paper.tex
start on abstract

@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
+This paper provides a comprehensive review and commentary on software defect prediction research. Review and criticism of previous work is presented. Future steps in the domain are given.
 \end{abstract}
@@
 
-\keywords{Fault prediction model; Software mining; Ant Colony Optimization; Classification}
+\keywords{Fault prediction model, Software mining, Ant Colony Optimization, Classification, Defect Prediction}
 

### 2015-12-14 paper/paper.tex
Added categories, and started cross project

@@
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
+\section{Machine Learning Algorithms}
 
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
+\section{Metrics}
+
+\section{Features}
+
+\section{Data Sources}
+
+\section{Data Preprocessing}
+
+\section{Cross-Project Defect Prediction}
+
+\subsection{Context Factors}
+Context factors for projects were assessed by Fend at el (2014 cite here).
+Used as a measurement of project similarity.
+The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
+
+\textbf{Programming Languages} Projects can be divided into groups depending on the programming language they are written in.
+Projects written in multiple languages could be problematic unless multiple language categories are included.
+
+\textbf{Issue Tracking} Whether or not a project uses an issue tracking system.
+
+\textbf{Total Lines Of Code} Project size based on the total number of lines of code split by quartiles.
+
+\textbf{Total Number of Commits}Project size as a function of the number of commits. Split into quartiles.
+
+\textbf{Total Number of Developers} Project size as a determined by the number of developer. Split into quartiles.
+
+\subsection{Ranking}
+
+\subsection{Clustering}
 

### 2015-12-14 paper/paper.tex
Started on data sources section

@@
 
+Jun Zheng \cite{zheng2010} argued that the mistakenly predicting a module as non-defective is more dangerous and costly than mistakenly predicting a module as defective.
+He presented three algorithms which boost neural networks to predict software defects with cost in mind.
+When evaluated on four NASA datasets, he found that threshold moving algorithm gave the best results in the sole Normalized Expected Cost of Misclassification (NECM) measure.
+He especially recommended threshold-moving algorithms on projects written in object oriented languages.
+
 Most software products are structured in a hierarchical format, for example into methods, classes, files, packages, etc.
@@
 \section{Data Sources}
+The choice of dataset is extremely important, especially when doing software defect prediction research.
+Datasets should be representative of actual software projects and should ideally be accessible to the public so the results can be re-tested and verified by others.
+Within the referenced papers, we found a variety of data sources which we feel need to be discussed.
+Primarily, we found open-source datasets, NASA datasets, and Windows Vista datasets.
+We will discuss each along with some reasons why they may have been chosen.
+\subsection{Open-source}
+\subsection{NASA}
+A few papers (Zheng \cite{zheng2010}...) used datasets from NASA.
+Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1, used for flight software.
+
+One major possibility for using NASA datasets is that most of their software is critical.
+A malfunction or crash due to a software defect is not only costly, but can also be deadly.
+NASA's software needs to be thoroughly tested and bug-fixed before it is ready for use.
+NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.
+
+NASA datasets are also publicly available.
+Researchers can more easily verify the results obtained in a study.
+Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
+\subsection{Windows Vista}
 

### 2015-12-14 paper/paper.tex
Some minor additions and typo fixes

@@
 % 3rd. author
-\alignauthor Alexandar Sobran\\
+\alignauthor Alexander Sobran\\
        \affaddr{Department of Computer Science}\\
@@
 First, they tested a variety of modeling techniques, such as neural networks, C4.5 with some variants, support vector machines, and logistic regression.
-They then looked at different metrics:  Process measures, OO code measures, and delta measures.
+They then looked at different metrics:  Process measures, object oriented code measures, and delta measures.
 Finally, they looked at ROC area and cost-effectiveness as evaluation criteria.
@@
 Rahman et al \cite{Rahman} argued that one reason for such behavior is that standard evaluation measures such as precision, recall, and F-measure are taken at specific threshold settings, while they really should be taken in a range of time/cost vs.
-quality tradeoffs.
+quality trade offs.
 They took the standard measures at a variety of tradeoffs and found that cross-project defect prediction is at least as good as within-project defect prediction, and sometimes substantially better.
@@
 
-One major possibility for using NASA datasets is that most of their software is critical.
+One major reason for using NASA datasets is that most of their software is critical.
 A malfunction or crash due to a software defect is not only costly, but can also be deadly.
 NASA's software needs to be thoroughly tested and bug-fixed before it is ready for use.
-NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.
+Software defect models which work well on these datasets can be claimed to be more reliable and trustworthy.
+Additionally, NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.
 
-NASA datasets are also publicly available.
+NASA datasets are publicly available.
 Researchers can more easily verify the results obtained in a study.

### 2015-12-14 paper/paper.tex
Added content to Windows Vista under data sources

@@
 \subsection{Open-source}
+
 \subsection{NASA}
@@
 \subsection{Windows Vista}
+Two of the referenced papers (Bird et al \cite{Bird} and Nagappan et al \cite{Nagappan}) use data from Windows Vista.
+Neither paper tests a fault prediction model using Vista test data.
+Instead, the first paper examined how different development teams worked together within Microsoft and the second paper examined Microsoft's organizational structure.
+Two of the three authors of the second paper are associated with Microsoft Research.
+
+But why was Windows Vista chosen?
+Windows in general is a widely used operating system which contains many lines of code.
+Windows is also known for being vulnerable without frequent patching and antivirus software.
+Windows Vista may have been the latest version of Windows at the time of both papers, but Vista is also known as a slow and buggy release.
+Maybe the authors intended to show that Vista did not contain an unusually high number of bugs compared to other releases, or maybe they just wanted to choose a Microsoft product that was well-known, whether for good or bad.
 

### 2015-12-14 paper/paper.tex
Added some stuff to open source data source section

@@
 \subsection{Open-source}
+The majority of papers we reviewed used open-source data, with most of those being Apache projects.
+Open-source projects are accessible to everyone, so researchers can verify the results they read, making every author accountable for the results they publish.
+Many of the Apache projects are tracked using JIRA which contains a plethora of data, including defect information.
+
+Apache libraries are also commonly used in a variety of products, so defects that are in released code can manifest themselves in projects that use them, creating a sort of ripple effect.
 

### 2015-12-14 paper/paper.tex
added a good bit of material to the metrics section as well as some additional references

--- 2015-12-14 paper/paper.tex
@@
 
-\section{Metrics}
+\section{Evaluation Metrics}
+
+There are three major approaches to evaluating the performance of models in the area of fault prediction:  Confusion matrix approaches, ROC curve based approaches, and finally cost effectiveness approaches.
+
+\subsection{Confusion Matrix Approaches}
+
+The use of confusion matrices, and the metrics (precision, recall, and F-measure) that revolve around them are very common in the fault prediction area.
+As will likely be known by the reader, a confusion matrix is a summary of predicted values compared with actual values.
+A confusion matrix in most cases will have been created based on test data where the actual values are known.
+Precision, recall, and F-Measure are all statistics that can be used to assess how close a model has come in predicting the actual on the test data.
+This methodology is used in nearly all of the papers we read \cite{Posnett} \cite{Nam} \cite{Bird} \cite{Vandecruys} \cite{Nagappan} \cite{Arisholm} \cite{Rahman} \cite{Jiang}.
+
+Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.
+One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).
+The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.
+
+\subsection{ROC curves}
+
+The ROC curve is another fairly standard metric for performance used in the literature.
+ROC, or Receiver Operating Characteristic analysis is an elaboration of the confusion matrix approach.
+The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.
+The rate for a particular model can be plotted as point on the ROC curve and the area under the curve be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.
+
+These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.
+The ROC curve has somewhat diminished usage because of a number of downsides that have been discussed in several papers \cite{Hall}.
 

### 2015-12-14 paper/paper.tex

@@
 \subsection{Open-source}
+The majority of papers we reviewed used open-source data, with most of those being Apache projects.
+Open-source projects are accessible to everyone, so researchers can verify the results they read, making every author accountable for the results they publish.
+Many of the Apache projects are tracked using JIRA which contains a plethora of data, including defect information.
+
+Apache libraries are also commonly used in a variety of products, so defects that are in released code can manifest themselves in projects that use them, creating a sort of ripple effect.
+
 \subsection{NASA}

### 2015-12-14 paper/paper.tex
Finished but still raw evaluation metrics section

@@
 The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.
-The rate for a particular model can be plotted as point on the ROC curve and the area under the curve be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.
+The rate for a particular model can be plotted as point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.
 
 These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.
-The ROC curve has somewhat diminished usage because of a number of downsides that have been discussed in several papers \cite{Hall}.
+Some negatives have been pointed out about the ROC approach and it's usefulness in certain circumstances.
+One such negative is the fact that ROC curve approaches have "an overly optimistic view of an algorithm's performance if there is a large skew in the class distribution".
+\cite{Davis}  Other papers mention the fact that both ROC/AUC approaches and confusion matrix based approaches in general do not address the whether a particular fault prediction methodology can pinpoint the source of the faults or not.
+Since knowing where to find errors is just as important or more important than knowing whether errors exist or not several papers find ROC/AUC insufficient as an evaluation metric \cite{Posnett} \cite{Arisholm} \cite{Rahman}.
+
+\subsection{Cost Effectiveness}
+
+Arisholm et al \cite{Arisholm} contributed Cost Effectiveness as a metric to software defect prediction.
+The high level idea behind Cost Effectiveness is the idea that it is impossible in most cases to inspect the entire code base of a large project for bugs.
+Defect prediction models that can guide inspection of code to find the largest number of bugs by inspecting the smallest percentage of the code base are viewed as models with high cost effectiveness.
+
+The basic idea of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of the lines of code included in classes selected to focus verification as the x-axis.
+Classes are ranked according to their likelihood of having defects, first by the model, and next by the size of the class in case of ties.
+The graph has a baseline of $y=x$ which is essentially the assumption that the percentage of faults will be equivalent to the percentage of lines of code inspected, this is done using a random ranking of the classes.
+On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of class selected to focus verification according to the ranking determined by the model.
+
+ Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.
+To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.
+The actual calculation is $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/ (CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.
+The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.
+
+Those same papers that find ROC to be inefficient all suggest that Cost Effectiveness is an important and to some degree a superior metric to use in determining the performance of an algorithm \cite{Posnett} \cite{Arisholm} \cite{Rahman}.
+The Arisholm paper was in fact one of the most influential papers that we worked with throughout the semester.
+Cross-project defect prediction has been validated to some degree by the existence of Cost Effectiveness as an evaluation metric \cite{Rahman}.
+The technique was used in Jiang et al as a metric as well \cite{Jiang}.
 

### 2015-12-15 paper/paper.tex
Added unfinished ML section

@@
 \section{Machine Learning Algorithms}
+
+Every fault prediction study used some sort of machine learning algorithm as the heart of the model.
+There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.
+
+\subsection{Regression}
+Regression is a ML algorithm for data that can be fitted to a curve.
+A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...).
+Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.
+
+\subsection{Neural Networks}
+Neural networks are designed to model the learning pattern of the human brain.
+Essentially, neural networks consist of nodes connected by links.
+The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.
+
+Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers.
+Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature.
+AdaBoost was chosen because it is a popular way to improve the performance of the model.
+
+\subsection{Other ML Algorithms}
+Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.
+
+Tian Jiang's algorithm \cite{Jiang} was based on a classification scheme known as Personalized Change Classification+ (PCC+).
+
+Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.
+
+\subsection{Discussion}
+Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems.
+We see that research has followed the advice of the authors.
+Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.
+
+Not only have authors used well-known ML algorithms, but they have even implemented new ones. This shows that ML algorithms were the primary choice of recent studies and still are today.
 

### 2015-12-15 paper/paper.tex
fixed citation

@@
 \subsection{Context Factors}
-Context factors for projects were assessed by Fend at el (2014 cite here).
-Used as a measurement of project similarity.
+Context factors for projects were assessed by Feng et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
 The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

### 2015-12-15 paper/paper.tex
Added statistical tests and context aware cross-prroject ranking

--- 2015-12-15 paper/paper.tex
@@
 
+\section{Statistical Tests}
+\subsection{Mann-Whitney U test}
+The Mann-Whitney U test, a non-parametric test that determines if two independent distributions have equally large value,  was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to pair-wise compare the distribution of metrics of projects in the domain of cross-project defect prediction.
+
 \section{Cross-Project Defect Prediction}
@@
 \subsection{Context Factors}
-Context factors for projects were assessed by Fend at el (2014 cite here).
-Used as a measurement of project similarity.
+Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
 The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
@@
 
-\subsection{Ranking}
+\subsection{Context-Aware Rank Tranformation}
+Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} propose a context-aware rank transformation approach.
+First, split the project up into non-overlapped groups based on the previous context factors.
+Then cluster the groups with similar context factor distributions.
+Obtain a ranking function based using the 10th quantiles of predictors.
+Apply this ranking function to bin the predictor values into the 10 levels.
 

### 2015-12-15 paper/paper.tex
Mostly complete Features section

--- 2015-12-15 paper/paper.tex
@@
 
-Every fault prediction study used some sort of machine learning algorithm as the heart of the model.
-There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.
-
-\subsection{Regression}
-Regression is a ML algorithm for data that can be fitted to a curve.
-A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...).
-Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.
-
-\subsection{Neural Networks}
-Neural networks are designed to model the learning pattern of the human brain.
-Essentially, neural networks consist of nodes connected by links.
-The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.
-
-Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers.
-Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature.
-AdaBoost was chosen because it is a popular way to improve the performance of the model.
-
-\subsection{Other ML Algorithms}
-Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.
-
-Tian Jiang's algorithm \cite{Jiang} was based on a classification scheme known as Personalized Change Classification+ (PCC+).
-
-Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.
-
-\subsection{Discussion}
-Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems.
-We see that research has followed the advice of the authors.
-Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.
-
-Not only have authors used well-known ML algorithms, but they have even implemented new ones. This shows that ML algorithms were the primary choice of recent studies and still are today.
-
 \section{Evaluation Metrics}
@@
 Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.
+The Vandecruys paper \cite{Vandecruys} even uses terminology that is separate from many other publications in using sensitivity for recall and specificity for the true negative rate, which is a seldom reported statistic.
 One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).
@@
 To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.
-The actual calculation is $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/ (CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.
+The actual calculation is\\ $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/$\\ $(CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.
 The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.
@@
 \section{Features}
+
+This section could also be labeled metrics, as it is in many places throughout the literature on this topic, but to not confuse it and the previous section on evaluation metrics we have chosen to label it features.
+The main reasoning for this is the fact that metrics are actually used as features in this area and not actually as metrics for comparison of one method versus another.
+The Radjenovic paper \cite{Radjenovic} is a fairly exhaustive paper with relation to metrics/features in fault prediction.
+Radjenovic came up with three categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.
+The categories are: Traditional, Object-Oriented, and Process.
+Some of the papers we reviewed defy this categorization and use metrics that are either one offs or are hybridized to such a degree that they should be explained on their own.
+
+\subsection{Traditional}
+
+These are metrics that relate to complexity (ie McCabe or Halstead calculations) and lines of code.
+A good number of papers we reviewed used these metrics as feature \cite{Posnett} \cite{Vandecruys} \cite{Bird}.
+There is considerable discussion in terms of whether these sorts of metrics provide good quality models or not.
+Hall et al indicate that in their review that models using only static code metrics that are complexity based have poor performance, but that Lines of Code based models tend to be useful \cite{Hall}.
+Radjenovic et al indicate that LOC has no strong evidence behind it in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.
+On complexity metrics Radjenovic states that these metrics are reasonable, but that "others are better"\cite{Radjenovic}.
+
+\subsection{Object Oriented Metrics}
+
+Object oriented metrics seem to have been dominated by the metrics presented by Chidamber and Kemerer \cite{Chidamber} \cite{DAmbros}.
+These metrics include things like number of children(NOC), coupling between classes (CBO), or lack of cohesion of methods (LCOM).
+Object oriented metrics were used in only one of our papers, Arisholm et al, and used there really only as a comparison metric\cite{Arisholm}.
+In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size are correlated and that further work is needed in that area  \cite{Radjenovic}.
+Hall et al state that OO and LOC are actually on pretty equal footing and that OO provides better performance than source code metrics \cite{Hall}.
+
+\subsection{Process Metrics}
+
+Process metrics relate to things like number of developers, code churn, number of commits, features, etc.
+Process metrics are mostly mined from source code management systems like Git, and also bug tracking and issue tracking systems like Jira.
+These metrics have a strong following in the fault prediction community and are well represented in our papers \cite{Posnett} \cite{Bird} \cite{Arisholm} \cite{Rahman}.
+Rahman et al particularly only used a set of process metrics while the other papers mentioned used some sort of combination of process and other metrics.
+There is some dispute between Radjenovic and Hall with regards to process metrics, with Hall suggesting that their performance was the worst out of everything they had examined where Radjenovic considers process metrics to be promising and that they are deserving of further study and validation while additionally stating that they provide superior post-release fault prediction \cite{Hall} \cite{Radjenovic}.
+
+\subsection{Organizational Structure}
+This is an approach that was proposed by Nagappan et al at Microsoft Research \cite{Nagappan}.
+The metrics included a set of 8 measures of organizational complexity: Number of engineers, Edit Frequency, Depth of Master Ownership, Percentage of Org contributing to development, Overall Organization Ownership, and Organization Intersection Factor.
+They used these metrics to create a fault prediction model and compared its performance in Precision and recall against a set of OO, Traditional, and Process metrics.
+For Windows Vista they show that Organizational metrics are superior to the other types of metrics available.
+As mentioned in the paper there are questions about whether this approach would work outside Microsoft or with a smaller project.
+
+Naggapan and Bird produced another paper in the next year using organizational metrics again with a bit of a twist in looking at whether distributed development had an effect on software quality \cite{Bird}.
+This paper added an additional metric of the actual location of the members of teams working on Windows Vista with levels starting at the same building and growing to the point of developers working at locations across the globe from one another.
+Organizaitonal metrics as well as a set of process and traditional metrics were used in conjunction with the distribution metric seemingly out of surprise that there was little difference between distributed projects and more local projects.
+The idea was to try to prove that there was not in fact some correlation between the other metrics they looked at and the performance of teams across long distances.
+They found that in fact there was no difference and that distributed development within one company was possible without sacrificing quality.
 

### 2015-12-15 paper/paper.tex

@@
 
+Every fault prediction study used some sort of machine learning algorithm as the heart of the model.
+There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.
+
+\subsection{Regression}
+Regression is a ML algorithm for data that can be fitted to a curve.
+A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...).
+Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.
+
+\subsection{Neural Networks}
+Neural networks are designed to model the learning pattern of the human brain.
+Essentially, neural networks consist of nodes connected by links.
+The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.
+
+Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers.
+Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature.
+AdaBoost was chosen because it is a popular way to improve the performance of the model.
+
+\subsection{Other ML Algorithms}
+Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.
+
+Tian Jiang's algorithm \cite{Jiang} was based on a classification scheme known as Personalized Change Classification+ (PCC+).
+
+Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.
+
+\subsection{Discussion}
+Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems.
+We see that research has followed the advice of the authors.
+Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.
+
+Not only have authors used well-known ML algorithms, but they have even implemented new ones. This shows that ML algorithms were the primary choice of recent studies and still are today.
+
 \section{Evaluation Metrics}

### 2015-12-15 paper/paper.tex
Added discussion for data sources

@@
 Maybe the authors intended to show that Vista did not contain an unusually high number of bugs compared to other releases, or maybe they just wanted to choose a Microsoft product that was well-known, whether for good or bad.
-
+\subsection{Discussion}
+Most of the studies we examined used open-source datasets which is in line with previous recommendations (\cite{Catal}, \cite{Vandecruys}).
+The two papers which used Windows Vista were not proposing a new or improved fault prediction model but were instead analyzing Microsoft's organizational structure to see how it may have affected bug levels.
+Although the NASA software isn't open source, we think that its datasets are acceptable because of their domain and the fact that NASA has made the datasets public for research purposes.
+Research has heeded the recommendations of earlier researchers and now primarily use open-source datasets
 \section{Data Preprocessing}

### 2015-12-15 paper/paper.tex
Cliff's d

@@
 
+\subsection{Cliff's $\delta$}
+Cliffs $\delta$ measures the effect size of the importance of the difference between two distributions.
+It is a nonparametric statistical test which represents the overlap two distributions.
+If two distributions are identical then the measurement is 0.
+It was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to determine the difference in the distributions of two project's metrics.
+If the difference of the effect size was large then the projects were not clustered together.
+This was done as second step in clustering similar projects and only on project's whose Mann-Whitney U test determined a statistically significant difference.
+
 \section{Cross-Project Defect Prediction}
@@
 \subsection{Context Factors}
-Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
+Context factors for projects were assessed by Zhang et et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
 The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

### 2015-12-15 paper/paper.tex
complete feature and metric sections

--- 2015-12-15 paper/paper.tex
@@
 \documentclass{sig-alternate-05-2015}
+\usepackage{hyperref}
 
@@
 
+\subsection{Discussion}
+It seems that Arisholm's contribution to the community with Cost Effectiveness back in  2010 has provided a better metric to evaluate fault prediciton models going forward.
+Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects injecting the realism that CE brings to the table seems to be totally appropriate in going forward.
+Even though that is viewed as the case by some in the community confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.
+These approaches will continue to be important in evaluating models until something better comes along.
+
+Our recommendation in this area would be to work with a hybrid approach of using both confusion matrix approaches and the ROC curve as well as CE based metrics.
+The suggestion of Hall as listed above to simply report confusion matrices seems like a great recommendation when possible going forward.
+At that point researchers could simply report cost effectiveness data along with confusion matrices and leave any further analysis to those that are interested.
+If reporting confusion matrices were not to become popular, settling on one confusion matrix based approach such as the F-Measure would be preferable to the random mixture of reporting approaches viewed throughout our papers.
+
 \section{Features}
@@
 They found that in fact there was no difference and that distributed development within one company was possible without sacrificing quality.
+
+\subsection{Text Classification}
+The paper on Personalized Defect Prediction by Jiang et al uses a methodology based on change classification \cite{Jiang}.
+To understand the metrics involved it was necessary to go back to a paper by Kim et al and get an idea of exactly what was done for feature extraction \cite{Kim}.
+The basic methodology uses process metrics such as changed LOC between commits, and when commits take place, but also uses traditional techniques like LOC, and complexity analysis.
+
+The more interesting and complex aspect of both of these papers is text classification.
+They both use a tool called BOW (Bag Of Words) to pull features out of log messages (called metadata in Jiang et all) and source code.
+The metadata aspect of this approach is also used in the Arisholm paper under the name Deltas where it is stated as simply the change between releases and also calls it Code Churn \cite{Arisholm}.
+Code churn in later papers is simply subsumed into process metrics, where later survey papers like Radjenovic simply categorize them together \cite{Radjenovic}.
+
+The source code inspection can be incredibly low level as in the Kim paper where they "This (text classification) means that every variable, method name, function name, keyword, comment word, and operator, that is everything  in the source code separated by whitespace or a semicolon is used as a feature"\cite{Kim}.
+The Jiang paper pulled out features like incorrect calls of individual language level functions like malloc and calloc on a per developer basis and then used those to predict faults for individual developers.
+It is an intriguing approach and one that was successful based on Jiang's results, It is an approach that has been cited, but not repeated.
+Partially that may be because the paper is fairly recent having been published in 2013, but it may also owe something to the fact that this is a seemingly intensive effort that few would use in industry.
+
+\subsection{Benchmark Data Sets}
+
+In one of our most recent papers (the Nam paper 2013 \cite{Nam}) we found researchers using benchmark data sets that had sets of metrics that could be chosen from in order to build models.
+The two sets discussed in the paper are ReLink and AEEEM \cite{Wu} \cite{DAmbros}.
+
+D'Ambros' AEEEM seemingly took everything he could find that he could rationalize and some new ideas and then just threw all of it into a metric set.
+\href{http://bug.inf.usi.ch/}{AEEEM} includes: change metrics, CK metrics, Object Oriented metrics, number of previous defects, complexity of code change, churn of CK and OO metrics, entropy of CK and OO metrics.
+ReLink unfortunately was not as helpful in listing out what is available in terms of metrics.
+Based on the Nam paper it contains 26 complexity metrics \cite{Nam}.
+
+\subsection{Discussion}
+As can be seen by the length and complexity of this section, the metrics area is still a very open area in fault defect prediction.
+The simple fact that there are major differences in terms of what metric set is being used across different projects creates some difficulty when comparing them.
+Also since many of these projects also use a hybrid approach, it makes it even less likely that another project will use exactly the same set of metrics.
+
+There is simply no consensus on what a good metric set really is, and that makes research going forward a difficult proposition.
+Our recommendation would be for the community to continue to codify what they believe to be the best metric sets and then to build benchmark data sets like AEEEM and ReLink that can be used across projects so that the approaches of researchers can be appropriately compared.
 

### 2015-12-15 paper/paper.tex
merged back in some missing stuff

@@
 
+\subsection{Discussion}
+Most of the studies we examined used open-source datasets which is in line with previous recommendations (\cite{Catal}, \cite{Vandecruys}).
+The two papers which used Windows Vista were not proposing a new or improved fault prediction model but were instead analyzing Microsoft's organizational structure to see how it may have affected bug levels.
+Although the NASA software isn't open source, we think that its datasets are acceptable because of their domain and the fact that NASA has made the datasets public for research purposes.
+Research has heeded the recommendations of earlier researchers and now primarily use open-source datasets
+
 \section{Data Preprocessing}
@@
 \subsection{Context Factors}
-Context factors for projects were assessed by Zhang et et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
+Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
 The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

### 2015-12-16 paper/paper.tex
Push paper from sharelatex edited by all members

@@
 % DOI
-\doi{10.475/123_4}
+%\doi{10.475/123_4}
 
 % ISBN
-\isbn{123-4567-24-567/08/06}
+%\isbn{123-4567-24-567/08/06}
 
 %Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
 
-\acmPrice{\$15.00}
+%\acmPrice{\$15.00}
 
@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\title{Software Defect Prediction: Review, Commentary, and Future Work}
+\title{Software Defect Prediction: Review, Commentary, and Recommendations}
 %
@@
        \email{aisobran@ncsu.edu}
-\and  % use '\and' if you need 'another row' of author names
+%\and  % use '\and' if you need 'another row' of author names
 }
@@
 \begin{abstract}
-This paper provides a comprehensive review and commentary on software defect prediction research. Review and criticism of previous work is presented. Future steps in the domain are given.
+This paper provides a comprehensive review and commentary on software defect prediction research.
+Review and criticism of previous work is presented.
+Recommendations and future steps in the domain are given.
 \end{abstract}
@@
 It is a well-known fact that software bugs are much cheaper and easier to fix before being released.
-But finding these bugs is often difficult and may not be cost effective to fix.
+But finding these bugs is often difficult and some bugs may be cheaper to fix than others.
 Researchers have been working on fault detection models to predict which software modules are most likely to contain bugs post-release.
@@
 
-In this paper, we focus on the advances made in software fault prediction models in the literature. Section 2 contains an assortment of existing work in the area.
+In this paper, we focus on the progress of software fault prediction models in the literature within the last few years.
+Section 2 contains an assortment of existing work in the area.
+We analyze the literature through different perspectives in Sections 3 through 10.
+Finally, in section 11, we give our overall observations and suggestions for future research in this area.
 
@@
 They recommended that machine learning algorithms and public datasets continue to be used, but caution against using method-level metrics and instead suggested class-level metrics as they can predict faults earlier in the software development cycle.
+
+A couple of years later, Hall et al \cite{Hall} performed another comprehensive literature review on fault prediction performance from January 2000 to December 2010.
+They hoped to see how the context, independent variables, and modeling techniques affected the performance of fault prediction models.
+They found that simpler modeling techniques seemed to perform better, along with feature selection on sets of independent variables.
+They encouraged future studies to better report their context, methodology, and performance.
+
+A couple of years after the Hall paper was published, Radjenovic et al \cite{Radjenovic} performed a literature review of metrics used in fault prediction models.
+The date range of papers was about double that for the Hall paper, from 1991 to 2011.
+The authors found that there are major differences between the metrics used, and that object-oriented and process metrics seemed to be better at predicting faults than static code metrics.
 
@@
 
-Also within the area of cross-project defect prediction, Nam et al \cite{Nam} found that when the source and target projects have a different feature distributions, the resulting model gives poor performance.
+Also within the area of cross-project defect prediction, Nam et al \cite{Nam} found that when the source and target projects have different feature distributions, the resulting model gives poor performance.
 The authors use Transfer Component Analysis (TCA) to find a common feature set for both projects and then map the data of both projects to it.
@@
 
+Two common approaches to evaluating defect prediction models are precision-recall and ROC curves.
+Davis et al \cite{Davis} showed that there exists a deep connection between the two.
+Additionally, they claimed that ROC curves are overly optimistic with highly skewed data, and that PR curves are better suited for that type of data.
+While there exists a connection between the two types of curves, the authors showed that an algorithm that optimizes the area under the ROC curve does not necessarily optimize the area under the PR curve.
+Essentially, they were trying to show that although both evaluation methods are related, just one does not show the complete picture.
+Both are needed to gain a better understanding of the performance of an optimization algorithm.
+
+Given that managers are trying to improve the process of software development, how do we best manage such a process? Chidamber and Kemerer \cite{Chidamber}
+developed and evaluated six such metrics.
+They were then tested at two different sites via automated tools.
+The authors concluded by suggesting how these metrics can be adapted in a software development environment and correlated with managerial performance indicators.
+
+D'Ambros et al \cite{DAmbros} presented a benchmark for fault prediction.
+Their motivation was the observation that such a benchmark did not exist, making it difficult to compare the models and approaches found in the literature.
+Their benchmark consisted of a publicly available data set consisting of five software systems.
+They also compared and evaluated well-known fault prediction methods and developed some new ones.
+They then ran their new methods on their benchmark, finding that they actually performed the best out of all.
+They conclude by stating that techniques based off of only one metric do not work well against every software project, meaning that the more useful metrics included, the better.
+
+Kim et al \cite{Kim} introduced a new technique called \textit{Change Classification}, which looks at individual changes to source code and predicts whether those changes are similar to previous buggy or clean changes.
+When testing on twelve open-source systems, change classification was found to be as accurate as other leading bug prediction techniques.
+Since this was a new technique, there were a number of open issues for future research.
+
+Wu et al \cite{Wu} implemented an algorithm which recovers links between bugs and committed changes called \textit{ReLink}.
+The authors tested this new algorithm on three open-source projects, finding that it was roughly as accurate as traditional heuristics.
+
+Zhang et al \cite{Zhang2014} attempted to implement a universal defect prediction model, which would work on both new projects and projects with historical data.
+In order to account for variations in the distributions of predictors, the authors clustered projects based on the similarities of the predictors.
+Their dataset included almost 1,400 open-source projects.
+They found their universal model performs well on both within-project and cross-project models.
+They have hope that such a universal model is achievable.
+
+\section{Ecological Inference}
+Ecological inference or EI was presented in the first paper we reviewed, the Posnett paper \cite{Posnett}.
+Posnett et al explain ecological inference as the idea that an observation or finding at an aggregated level can apply at a disaggregated level.
+For example, the idea that a model of defects at the package level also applies at the file level.
+
+The suggestion is that in the fault prediction area there is in fact an Ecological Fallacy, where findings at the aggregated level are expected to be valid at a disaggregated level.
+As in the example above a defect model that is created at a package level is applied to predict defects at a file level.
+Based on this concept Posnett wanted to prove whether or not the Ecological Fallacy applied to fault prediction.
+
+Posnett et al posit two main overarching conclusions in their paper:  That aggregated models when evaluated only at the aggregated level may have deceivingly strong performance, and furthermore inferences from aggregated models may not apply to their disaggregated parts \cite{Posnett}.
+Posnett cites another of our papers, Bird et al, as a potential rebuttal of his results because of the fact that geographical distribution did not have an effect in Bird's study \cite{Bird}.
+
+Moving beyond the Posnett paper, Rahman et al in 2012 made considerations regarding the aggregation level of their models, in that they decided to examine code at the file level.
+Rahman et al went that direction because they were worried that evaluation of a model on a coarser level of aggregation may not be a good predictor at the file level \cite{Rahman}.
+Rahman again cites Ecological Inference in a 2013 paper on Process Metrics as a threat for validity \cite{Rahman13}.
+
+\subsection{Discussion}
+The main question is whether EI and EF represent important concepts to researchers going forward in the fault prediction area.
+It seems that only a subset of papers are actually being written currently where EF is recognized as a concern.
+Our recommendation would be further study to validate Posnett's 2011 work, and if the work is further validated the community should consider EI/EF when conducting studies.
+
 \section{Machine Learning Algorithms}
 
-Every fault prediction study used some sort of machine learning algorithm as the heart of the model.
+Every fault prediction study leverages a machine learning algorithm as the heart of the model.
+Machine learning algorithms are a way to "learn" from data and create a model that can make predictions.
+Typically, there is a set of training data which the algorithm uses to generate the model.
+Then, it is evaluated with test data to see if it generates accurate and reliable predictions.
 There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.
@@
 Regression is a ML algorithm for data that can be fitted to a curve.
-A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...).
-Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.
+Regression algorithms are considered to be the simplest type, but can perform well if the data is a well-fit to some sort of well-behaved mathematical function.
+Most of the referenced papers used some form of regression as their main algorithm (\cite{Posnett}, \cite{Bird}, \cite{Nagappan}, \cite{Rahman}).
+
+\subsection{MARS}
+MARS is short for Multivariate Adaptive Regression Splines.
+The concept goes back to a 1991 paper by Friedman the technique is a non-parametric method used to model complex multivariate non-linear scenarios.
+It is suited modeling non-linear data because of the fact that models have a series of hinge and basis functions.
+Each hinge function per Bettenburg et al "partitions the data into disjoint regions that can be described separately"\cite{Bettenburg}.
+Bettenburg et al used MARS in building models to look at the difference between global and local trained model.
+The Jiang paper used MARS models based on Bettenburg's work as a baseline to compare PCC and PCC+ models against \cite{Jiang}.
 
 \subsection{Neural Networks}
-Neural networks are designed to model the learning pattern of the human brain.
-Essentially, neural networks consist of nodes connected by links.
-The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.
+Neural networks are a family of machine learning algorithms based initially on the perceptron.
+The basic structure of neural network consist of an input layer, layers of activation functions, and an output layer.
+Each layer is connected to other layers but no connections exist within the layer.
+The result of each activation function is delivered to the next connected layer until it finally reaches an output layer.
 
-Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers.
-Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature.
+Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, as a way to achieve better classification results by producing diverse base classifiers.
+Zheng states that he used neural networks based on their popularity in pattern recognition, and BPNNs because they were the most frequent neural network used in the literature.
 AdaBoost was chosen because it is a popular way to improve the performance of the model.
 
+\subsection{Naive Bayes}
+Zhang et al \cite{Zhang2014} use Naive Bayes classifier as a modeling technique in their approach to build a universal defect prediction model for cross-project defect prediction.
+They decided on this classifier because previous research determined that Bayes learners outperform other learners when predicting defects in noisy data.
+The Naive Bayes classifier is based on Bayes' theorem with independence assumptions.
+
+\subsection{Probabilistic Graphical Models}
+Probabilistic graphical models are considered powerful machine learning tools.
+They consist of a graphical structure where nodes are events and edges are conditional dependencies.
+Some examples include bayesian networks and hidden markov models.
+They have many strength including informative visualization from structures, insights from model inference, and lower complexities.
+Inferring insights from model structure could be leveraged in software defect prediction.
+Certain conditional relationships can be reported verbally to all concerned parties.
+It has also been posited every machine learning algorithm is an instance of a probabilistic graphical model.\cite{Bishop:2006:PRM:1162264}
+
 \subsection{Other ML Algorithms}
-Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.
+Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization(ACO) which models the foraging behavior of ant colonies.
+In AntMiner+, ACO is used to optimize a rule based classification algorithm.
+Rule based classification algorithms usually have greater comprehensibility than other machine learning algorithms as the association rules can be reported.
+Vandecruys also presented good accuracy using AntMiner+.
 
 Tian Jiang's algorithm \cite{Jiang} was based on a classification scheme known as Personalized Change Classification+ (PCC+).
-
-Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.
 
@@
 We see that research has followed the advice of the authors.
-Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.
+Among them, Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.
 
@@
 
-The use of confusion matrices, and the metrics (precision, recall, and F-measure) that revolve around them are very common in the fault prediction area.
-As will likely be known by the reader, a confusion matrix is a summary of predicted values compared with actual values.
+The use of confusion matrices, and the metrics (precision, recall, and F-measure) derived from them are very common in the fault prediction area.
+As will likely be known by the reader, a confusion matrix is a contingency table summarizing the predicted values compared with actual values.
 A confusion matrix in most cases will have been created based on test data where the actual values are known.
-Precision, recall, and F-Measure are all statistics that can be used to assess how close a model has come in predicting the actual on the test data.
-This methodology is used in nearly all of the papers we read \cite{Posnett} \cite{Nam} \cite{Bird} \cite{Vandecruys} \cite{Nagappan} \cite{Arisholm} \cite{Rahman} \cite{Jiang}.
+Precision, recall, type I errors, type II errors, and F-Measure are all statistics that can be used to assess how close a model has come in predicting the actual on the test data.
+This methodology is used in nearly all of the papers we read \cite{Posnett} \cite{Nam} \cite{Bird} \cite{Vandecruys} \cite{Nagappan} \cite{Arisholm} \cite{Rahman} \cite{Jiang} \cite{Zhang2014}
 
-Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.
+Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, type I errors, type II errors, and F-Measure has considerable variance between papers.
 The Vandecruys paper \cite{Vandecruys} even uses terminology that is separate from many other publications in using sensitivity for recall and specificity for the true negative rate, which is a seldom reported statistic.
@@
 The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.
+
+Another measurement we encountered is the g-measure.
+It is used by Zhang et al \cite{Zhang2014} in their cross-project defect prediction study.
+They use it to combat the the instability of precision in datasets with low percentages of defects.
 
@@
 The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.
-The rate for a particular model can be plotted as point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.
+The rate for a particular model can be plotted as a point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.
 
 These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.
-Some negatives have been pointed out about the ROC approach and it's usefulness in certain circumstances.
+Some negatives have been pointed out about the ROC approach and its usefulness in certain circumstances.
 One such negative is the fact that ROC curve approaches have "an overly optimistic view of an algorithm's performance if there is a large skew in the class distribution".
@@
 
-The basic idea of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of the lines of code included in classes selected to focus verification as the x-axis.
+The basic implementation of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of LOC included in classes selected to focus verification as the x-axis.
 Classes are ranked according to their likelihood of having defects, first by the model, and next by the size of the class in case of ties.
 The graph has a baseline of $y=x$ which is essentially the assumption that the percentage of faults will be equivalent to the percentage of lines of code inspected, this is done using a random ranking of the classes.
-On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of class selected to focus verification according to the ranking determined by the model.
+On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of classes selected to focus verification according to the ranking determined by the model.
 
  Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.
-To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.
+To find an approximation of the optimal cost effectiveness they use a ranking that ranks the most error filled classes highly and then create a cost effectiveness line according to that ranking.
 The actual calculation is\\ $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/$\\ $(CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.
@@
 It seems that Arisholm's contribution to the community with Cost Effectiveness back in 2010 has provided a better metric to evaluate fault prediciton models going forward.
-Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects injecting the realism that CE brings to the table seems to be totally appropriate in going forward.
-Even though that is viewed as the case by some in the community confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.
+Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects, injecting the realism that CE brings to the table seems to be totally appropriate in going forward.
+Even though that is viewed as the case by some in the community, confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.
 These approaches will continue to be important in evaluating models until something better comes along.
@@
 This section could also be labeled metrics, as it is in many places throughout the literature on this topic, but to not confuse it and the previous section on evaluation metrics we have chosen to label it features.
-The main reasoning for this is the fact that metrics are actually used as features in this area and not actually as metrics for comparison of one method versus another.
+The main reasoning for this is the fact that metrics are actually used as features in Machine Learning algorithms and not actually as metrics for comparison of one method versus another.
 The Radjenovic paper \cite{Radjenovic} is a fairly exhaustive paper with relation to metrics/features in fault prediction.
-Radjenovic came up with three categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.
+Radjenovic came up with three metric categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.
 The categories are: Traditional, Object-Oriented, and Process.
@@
 These are metrics that relate to complexity (ie McCabe or Halstead calculations) and lines of code.
-A good number of papers we reviewed used these metrics as feature \cite{Posnett} \cite{Vandecruys} \cite{Bird}.
+A good number of papers we reviewed used these metrics as features \cite{Posnett} \cite{Vandecruys} \cite{Bird}.
 There is considerable discussion in terms of whether these sorts of metrics provide good quality models or not.
 Hall et al indicate that in their review that models using only static code metrics that are complexity based have poor performance, but that Lines of Code based models tend to be useful \cite{Hall}.
-Radjenovic et al indicate that LOC has no strong evidence behind it in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.
+Radjenovic et al indicate that LOC based methods have no strong evidence behind them in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.
 On complexity metrics Radjenovic states that these metrics are reasonable, but that "others are better"\cite{Radjenovic}.
@@
 Object oriented metrics were used in only one of our papers, Arisholm et al, and used there really only as a comparison metric\cite{Arisholm}.
-In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size are correlated and that further work is needed in that area  \cite{Radjenovic}.
+In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size metrics are correlated and that further work is needed in that area  \cite{Radjenovic}.
 Hall et al state that OO and LOC are actually on pretty equal footing and that OO provides better performance than source code metrics \cite{Hall}.
@@
 Rahman et al particularly only used a set of process metrics while the other papers mentioned used some sort of combination of process and other metrics.
+
 There is some dispute between Radjenovic and Hall with regards to process metrics, with Hall suggesting that their performance was the worst out of everything they had examined where Radjenovic considers process metrics to be promising and that they are deserving of further study and validation while additionally stating that they provide superior post-release fault prediction \cite{Hall} \cite{Radjenovic}.
+
+Another discussion of the strength of process metrics can be found in a 2013 paper by Rahman where he and Devanbu examine "How, and Why, Process Metrics are better"\cite{Rahman13}.
+Based on the title it is fairly clear where Rahman and Devanbu come out on this, but the main thrust of their argument is that process metrics do not suffer from the stasis that code metrics do suffer from.
+The idea is that between releases code metric based models lose relevancy as the distribution of defects in the project changes.
+Further Rahman indicates that this assessment is geared towards situations in which AUC and Cost-Sensitive evaluation methods are being used.
+
+Process metrics were also used by Zhang et al \cite{Zhang2014} to build a successful universal defect prediction model.
+This reaffirms the feature set as generalizable to other projects when performing cross-project defect prediction.
 
@@
 As mentioned in the paper there are questions about whether this approach would work outside Microsoft or with a smaller project.
-
 Naggapan and Bird produced another paper in the next year using organizational metrics again with a bit of a twist in looking at whether distributed development had an effect on software quality \cite{Bird}.
@@
 
+Rahman et al also use a benchmark set of metrics for their 2013 paper.
+The metric set is called \href{https://scitools.com/feature/metrics/}{UNDERSTAND} from Scitools.
+It uses a set of complexity, LOC, and OO metrics \cite{Rahman13}.
+
 \subsection{Discussion}
@@
 
+Sourceforge and GoogleCode projects were used by Zhang et al \cite{Zhang2014} for cross-project defect prediction.
+Although open source projects are a viable data source they also contain many useless projects where defects are not properly tracked.
+
 \subsection{NASA}
-A few papers (Zheng \cite{zheng2010}...) used datasets from NASA.
-Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1, used for flight software.
+A couple of papers (\cite{zheng2010}, \cite{Vandecruys}) used datasets from NASA.
+Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1 and PS4, used for flight software.
 
@@
 \section{Data Preprocessing}
+\subsection{Filtering}
+Zhang et al \cite{Zhang2014} filtered for projects to meet specific programming language criteria.
+To perform this they specifically filter for file types associated to those languages.
+They also apply a second filtering to remove small projects by filtering out projects with a small number of commits.
+The decide on the 25\% quantile which is 32 commits.
+This is to confirm projects have enough information for extracting viable features.
+Next they filter projects with a lifespan of less than one year and project with limited defects for the same reasoning.
+Finally, they filter out projects without fix-inducing commits as they are marked abnormal.
+
+Vandecruys et al also utilize a filtering based approach to rank variables according to their predictive power.
+They used a $\chi^{2}$ based filter.
+The idea was to decrease the number of metrics to the point that only the metrics that were useful would be actually added to the model \cite{Vandecruys}.
+
+\subsection{Discretization}
+Generally a method to turn continuous variables into discrete variables.  Vandecruys et al used this technique because AntMiner plus could not deal with continuous variables \cite{Vandecruys}.
+
+\subsection{Oversampling}
+The data in many fault prediction data sets has many more clean files than faulty files the data is considered to be heavily skewed.
+One method for dealing with skewed data is oversampling, as discussed in \cite{Vandecruys}.
+The idea is when sampling for training data to repeat observations that correspond to faults in the data.
+Vandecruys et al found in their study that oversampling had different effects at different levels of oversampling (the number of times faulty observations were repeated).
+
+The true positive rate, sensitivity or recall, and the true negative rate, specificity are affected by the levels of oversampling.
+In Vandercruy's case an increase in oversampling increased specificity, but decreased sensitivity.
+This change also coincides with a decrease in accuracy.
+Their perspective was that it was important to reach a break even point in terms of oversampling where they could live with the level of accuracy and sensitivity on one hand but specificity on the other.
+They found that oversampling to the level where there were equal numbers of faulty and non-faulty observations was optimal\cite{Vandecruys}.
+
+\subsection{Normalization}
+Normalization was a key part of Nam et al's paper on TCA.
+TCA requires normalization to function correctly, this is fairly common throughout that statistical/machine learning/ASE world, and is essentially scaling all features in a data set to the same scale.
+This is often necessary because features may well be from completely different scales such as liters of oil and pounds sterling.
+
+Nam et al use 4 different schemes for normalization: The first is a simple Min-Max scheme where $norm_x = \frac{x - min}{max - min}$.
+The other methods are z score normalizations with slight changes, such as $norm_x = \frac{x-mean}{std_dev}$.
+The difference comes in where the mean is either the mean of all of the features, or the mean of a particular feature vector.
+As follows in the section on TCA+ Nam et al used this as an optimization for TCA since it had such a high sensitivity to normalization\cite{Nam}
+
+\subsection{PCA}
+PCA or principal component analysis does not completely fit into data preprocessing, but is not significant enough to be its own section.
+The technique is used to take a large number of features and flatten them into a smaller number of features through a transformation using Eigenvectors and Eigenvalues \cite{James}.
+
+This technique is used by Nagappan et al, they actually use PCA in a somewhat odd manner.
+They first state that there is a concern with multicollinerity between the organizational metrics that the propose, so they decide to use PCA to deal with the multicollinerity in the data.
+They find that PCA returns 8 principal components and then determine on that basis as well as step-wise regression that all of the measures are valuable and should be retained \cite{Nagappan}.
+It is possible that this is a legitimate use for PCA, but it is not a use that we are familiar with.
 
 \section{Statistical Tests}
+
 \subsection{Mann-Whitney U test}
-The Mann-Whitney U test, a non-parametric test that determines if two independent distributions have equally large value,  was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to pair-wise compare the distribution of metrics of projects in the domain of cross-project defect prediction.
+The Mann-Whitney U test, a non-parametric test that determines if two independent distributions have equally large value,  was used by Zhang et al \cite{Zhang2014} to pair-wise compare the distribution of metrics of projects in the domain of cross-project defect prediction.
+
+The Mann-Whitney test is also used in Bird et al to test the differences in mean number of failures between projects that were distributed and non-distributed projects.
+\cite{Bird}  Bird et al indicate that the usage of the Mann-Whitney test is more appropriate to their circumstances because of the fact that the number of failures that they were looking at were not normally distributed.
 
@@
 If two distributions are identical then the measurement is 0.
-It was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to determine the difference in the distributions of two project's metrics.
+It was used by Zhang et al \cite{Zhang2014} to determine the difference in the distributions of two project's metrics.
 If the difference of the effect size was large then the projects were not clustered together.
@@
 
+\subsection{Wilcoxon signed-rank test}
+
+This is a hypothesis testing technique that is used in the comparison of two samples.
+It is a non-parametric method so, does not assume any particular distribution which increases its usefulness in certain circumstances.
+The Rahman paper uses the WSR test for hypothesis testing to try to prove that cross-project\%SLOC AUCEC (Area under the cost effectiveness curve) is "resilient to parameter selection for a reasonable cutoff choice"\cite{Rahman}.
+This is in the context of determining the size of model in terms of number of parameters to use.
+
+Wilcoxon Signed rank was also used in the Arisholm paper to determine whether there is a significant difference between all pairs of techniques and metric sets that they studied in their project\cite{Arisholm}.
+Arisholm et al only report p-values, but also report what level of significance they used in determining the p-values.
+For whatever reason Rahman neglects to do so, from our perspective this is at least somewhat of a failure on the part of Rahman et al.
+Without the significance level it is difficult to interpret the p-values quoted.
+
+WSR was also used in Nam et al to determine whether there was a statistically significant difference in performance between TCA and TCA+ \cite{Nam}.
+Jiang et al used WSR to examine the difference between CC and PCC within their paper \cite{Jiang}.
+
+\subsection{Wilcoxon rank-sum test}
+The Wilcoxon rank-sum test is a non-parametric statistical test.
+It compares the ranks of two independent population based on their whole ordered rank.
+Zhang et al \cite{Zhang2014} used the test to compare their technique of rank transformation of features with log transformation of features.
+With this measure they were able to differentiate between the two transformations.
+
+\subsection{Cohen's d}
+
+Cohen's d is a measure of effect size, per \href{https://en.wikipedia.org/wiki/Effect_size#cite_note-CohenJ1988Statistical-7}{Wikipedia} it is defined as the difference between two means divided by a standard deviation for the data.
+Arisholm et al use Cohen's D to report the effect size of the differences generated by the Wilcoxon Signed Rank test commented on above \cite{Arisholm}.
+Between the two measures Arisholm creates a fantastic table presented in their paper that shows both the p-values generated and the effect sizes.
+Zhang et al \cite{Zhang2014} map Cliff's $\delta$ to Cohen's d standards to determine effect size of project metric distribution difference.
+
+\subsection{Spearman's Rank Correlation}
+This technique was used in the Nagappan paper to determine the correlation between organizational metrics.
+The paper suggests that Spearman's rank correlation is superior to the Pearson correlation because it does not require a linear relationship between elements under consideration \cite{Nagappan}.
+Nagappan et al use the rank correlation in terms of a hypothesis test between the organization metrics that are discussed in the metrics section above.
+They report p-values along with the associated significance level.
+
+Bird et al used the Spearman Rank Correlation in their paper as well, perhaps because Nagappan was the second writer on this paper as well \cite{Bird}.
+In this circumstance they wanted to determine whether there was a correlation between the distribution level of projects and process metrics.
+The reasoning was that they wanted to prove that the results they had found in terms of distributed projects being no more fault prone than non-distributed projects.
+If they could show that there was no real correlation between other factors and the fact that distribution was not a cause for faults.
+
+\subsection{AIC}
+The AIC is the Akaike Information Criterion.
+It is generally used as a methodology to reduce the number of features in a machine learning model.
+In a feature selection scenario, features are removed/added and the AIC value is checked to determine whether removing/adding a feature leads to a better model \cite{James}.
+Rahman et al use AIC for the same purpose of reducing the number of variables in their models \cite{Rahman}.
+
+\subsection{VIF}
+The Variance Inflation Factor is a metric used to determine whether multicollinearity exists within a particular model \cite{James}.
+It was used alongside the AIC score in the Posnett paper we reviewed.
+As Posnett et al indicate AIC should not be used without using VIF because of the potential for high Multicollinearity.
+In their feature selection process they used VIF as another factor to determine which models were best.
+They ranked by AIC and then additionally removed any models with high VIF from consideration.
+
+\subsection{F Statistic}
+The F statistic is generally used to test the relationship between the independent and dependent variables in regression scenarios \cite{James}.
+The Bird paper makes extensive use of the F-Statistic to determine whether the distribution level of developers has an effect on the response variable, the number of faults.
+The paper presents p-values with significance levels as should be standard.
+The p-values test the hypothesis that there is no effect of the independent variable on the dependent variables discussed above \cite{Bird}.
+
+Bird et al use this setup to prove that a majority of the difference in defects is in fact the number of developers working on a binary.
+He attempts to prove that using the F statistic and its concurrent adjusted $R^{2}$ statistic when adding in the number of developers to the project.
+Since Adjusted $R^{2}$ is meant to show the amount of variance in the response variable explained by the predictor variable adding the number of developers to the model should increase the $R^{2}$ value which it does.
+
+\subsection{Discussion}
+Our main recommendation with regards to statical testing is that there should be at least basic significance testing in general in the defect prediction community.
+Surprisingly there were no statistical significance tests of any sort in one of the papers we reviewed \cite{Vandecruys}.
+Furthermore the reporting of p-values without reporting the statistical significance level that they were evaluated should not happen at this level.
+
 \section{Cross-Project Defect Prediction}
+One of the main limitations of defect prediction models is the within-project requirement for model fitting.
+Cross-project defect prediction can be used to predict defects in projects with models trained on other projects.
+This allows the application of defect predictors to new projects without enough history for within-project model fitting.
+It also allows the development of a universal model for defect prediction on any project.
 
 \subsection{Context Factors}
-Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity.
-The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
+Context factors for projects were assessed by Zhang et al \cite{Zhang2014} and used as a measurement of project similarity.
+These context factors showed an overall increase in the confusion matrix measure when compared to just code and process metrics.
+Context factors provide a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
 
@@
 
-\subsection{Context-Aware Rank Tranformation}
-Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} propose a context-aware rank transformation approach.
+\subsection{Context-Aware Rank Transformation}
+Zhang et al \cite{Zhang2014} propose a context-aware rank transformation approach.
 First, split the project up into non-overlapped groups based on the previous context factors.
@@
 Apply this ranking function to bin the predictor values into the 10 levels.
+The ranking function achieves the purpose of making projects with different scales of metrics comparable.
+This is crucial to a cross project defect prediction algorithm.
 
 \subsection{Clustering}
+Zhang et al \cite{Zhang2014} use a clustering method to group similar projects together for cross-project defect prediction.
+Projects in the same group are used to predict each others' defects and form a universal defect prediction model.
+The clustering is a two step process of comparing the distribution of the project metrics and then quantifying the difference between the distributions.
+The first step leverages the Mann-Whitney U test.
+The second step leverages the Cliff's $\delta$ measure.
 
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
+\subsection{TCA}
+Transfer component analysis(TCA) finds the latent feature space for two different projects by minimizing the distance between their distribution while preserving the original data.
+Features for both projects are then mapped to this latent space.
+Training and prediction is done on the transformed space.
+TCA is sensitive the normalization which decreases its performance in transfer defect prediction.
+Nam et al \cite{Nam} extended TCA to TCA+ to deal with this sensitivity to normalization.
 
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+\subsection{TCA+}
+TCA+ is an extension of TCA proposed by Nam et al \cite{Nam}.
+By optimizing the normalization stage of data processing they are able to mitigate the sensitivities of TCA to normalization and demonstrate improved software defect prediction performance.
 
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps} files to be
-displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
-\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
-\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
-each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\caption{A sample black and white graphic.}
-\end{figure}
-
-\begin{figure}
-\centering
-\caption{A sample black and white graphic
-that has been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-\begin{figure*}
-\centering
-\caption{A sample black and white graphic
-that needs to span two columns of text.}
-\end{figure*}
-
-\begin{figure}
-\centering
-\caption{A sample black and white graphic that has
-been resized with the \texttt{includegraphics} command.}
-\vskip -6pt
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
+\subsection{Discussion}
+Our recommendation for future work includes extending the universal model used by Zhang et al \cite{Zhang2014} with the TCA+ approach of Nam et al \cite{Nam}.
+They both offer different approaches to linking projects with one relying on statistical similarities while the other relies on component analysis, respectively.
+A method leveraging these two approaches could first cluster based on the rank transformation and then preprocess data using TCA+ before applying a machine learning algorithm for defect prediction.
 
 \section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
+Software defect prediction has made significant progress within the last few years.
+Recommendations from earlier papers, such as more machine learning algorithms \cite{Catal}, better metrics \cite{Arisholm} and publicly available datasets (\cite{Catal}, \cite{Vandecruys}) have largely been followed by the papers we reviewed.
 
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+However, there remains room for improvement for future studies, namely with ecological inference concerns \cite{Posnett}, feature metrics \cite{Hall}, and statistical tests.
+Recent research into cross-project fault defect prediction has proved to be an area with potential since the application of cost effectiveness as a metric, we hope to see additional effort in this area.
+We suggest that researchers focus on these areas to continue the progress that has been occurring recently.
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+We recommend usage of a greater diversity of machine learning algorithms including probabilistic graphical models.
+A specific use case could include hidden Markov models.
+It could be theorized changes to a software component can be viewed as a series of changes with a hidden state of defective or not defective.
+This sets up a feasible implementation of software defect prediction in a hidden Markov chain where the software metrics are observable and the software defect truth is hidden \cite{Bishop:2006:PRM:1162264}.
+
 \bibliographystyle{abbrv}
-\bibliography{references}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-%\balancecolumns % GM June 2007
-% That's all folks!
+\bibliography{references}  
 \end{document}
